---
title: "Example of RRI infographics"
author: "JSM"
date: "9/29/2022"
output:
  html_document
---
  
# {.tabset .tabset-fade .tabset-pills}
  
```{r echo=FALSE, message=FALSE, warning=FALSE}  
library(png)
library(cowplot)
library(ggplot2)
library(reshape2)
library(tidyverse)

###############
#plotting setup
blankitout <-   theme(axis.line        = element_blank(),
                      axis.text.x      = element_blank(),
                      axis.text.y      = element_blank(),
                      axis.ticks       = element_blank(),
                      axis.title.x     = element_blank(),
                      axis.title.y     = element_blank(),
                      legend.position  = "none",
                      panel.background = element_blank(),
                      panel.border     = element_blank(),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      plot.background  = element_blank())



###########################
################human setup
# Load png file with human
img <- readPNG("C:/Users/jmallett/OneDrive - The Council of State Governments/GitProjects/MCLCShiny/prep/infographics/human2.png")
#make all values binary (0/1)
img <- ifelse(img>0 & img<1,1,
              ifelse(img==0,0,
                     ifelse(img==1,1,1)))

source("create_infograph_function.R")
```

## Example: RRI > 1 (with creepy zombies)

The first argument is the RRI, the second argument is the number of infographics to plot (default is 9)

```{r echo=TRUE, message=FALSE, warning=TRUE,fig.height=4} 
create_infograph(11.35)
```

## Example: RRI < 1 (with creepy zombies)

The first argument is the RRI, the second argument is the number of infographics to plot (default is 9)

```{r echo=TRUE, message=FALSE, warning=TRUE,fig.height=2} 
create_infograph(.9,7)
```

## Example: RRI > 1 (no zombies)

The first argument is the RRI, the second argument removes empty infographics from the plot 

```{r echo=TRUE, message=FALSE, warning=TRUE,fig.height=2} 
create_infograph(6.35,emptyhumans=FALSE)
```

## Example: RRI < 1 (no zombies)

The first argument is the RRI, the second argument removes empty infographics from the plot

```{r echo=TRUE, message=FALSE, warning=TRUE,fig.width=1,fig.height=2} 
create_infograph(0.35,emptyhumans=FALSE)
```

## Example: RRI > 1 (no zombies), testing all arguments

The first argument is the RRI, the second argument is the number of infographics to plot (default is 9), the third argument removes empty infographics from the plot, the fourth argument changes the fill color of the infographics, and the fifth argument changes the direction of the fill color (horizontal v. vertical)

```{r echo=TRUE, message=FALSE, warning=TRUE, fig.width=4, fig.height=2} 
create_infograph(setrri=3.5, infog=3, emptyhumans=FALSE, fillcolor="orange", fillHoriz=FALSE)
```



