---
title: "General Documentation: MCLC NCRP Revocations 2015-2019" 
subtitle: "Last updated/ran: `r Sys.time()`"
format: 
  html:
    page-layout: full
editor: source
self-contained: true
---

```{r, include=FALSE}
box::use(
    box/admin
  , box/calc
  , box/clean_SC
)
```




::: panel-tabset

## Data Source 

### [NCRP: National Corrections Reporting Program 1991-2019 ICPSR 38048](https://www.icpsr.umich.edu/web/ICPSR/studies/38048) 

### [SC - Census State Population by Characteristics](https://www.census.gov/programs-surveys/popest/technical-documentation/research/evaluation-estimates/2020-evaluation-estimates/2010s-state-detail.html) 


#### SC --> NCRP 

-   filter data to be 18+, combine sex, and combine ORIGIN
-   re-code RACE/ORIGIN categories to match RACE NCRP categories
-   sum across categories
-   add state ids

#### RACE/ORIGIN --\> RACE

SC has `ORIGIN`(Ethnicity) and `RACE` that need to be fit into the NCRP `RACE` categories.

| SC `ORIGIN`      | SC `RACE`                                            | NCRP `RACE`                       | Label                 |
|:--------------|:-----------------------|:-----------------|:--------------|
| 1 (Not Hispanic) | 1 (White Alone)                                      | \(1\) White, non-Hispanic         | `r admin$lev_RACE[1]` |
| 1 (Not Hispanic) | 2 (Black or African American Alone)                  | \(2\) Black, non-Hispanic         | `r admin$lev_RACE[2]` |
| 1 (Not Hispanic) | 3 (American Indian or Alaska Native Alone)           | \(4\) Other race(s), non-Hispanic | `r admin$lev_RACE[4]` |
| 1 (Not Hispanic) | 4 (Asian Alone)                                      | \(4\) Other race(s), non-Hispanic | `r admin$lev_RACE[4]` |
| 1 (Not Hispanic) | 5 (Native Hawaiian and Other Pacific Islander Alone) | \(4\) Other race(s), non-Hispanic | `r admin$lev_RACE[4]` |
| 1 (Not Hispanic) | 6 (Two or more races)                                | \(4\) Other race(s), non-Hispanic | `r admin$lev_RACE[4]` |
| 2 (Hispanic)     | 1 (White Alone)                                      | \(3\) Hispanic, any race          | `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 2 (Black or African American Alone)                  | \(3\) Hispanic, any race          | `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 3 (American Indian or Alaska Native Alone)           | \(3\) Hispanic, any race          | `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 4 (Asian Alone)                                      | \(3\) Hispanic, any race          | `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 5 (Native Hawaiian and Other Pacific Islander Alone) | \(3\) Hispanic, any race          | `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 6 (Two or more races)                                | \(3\) Hispanic, any race          | `r admin$lev_RACE[3]` |



## Code 

Imports data, cleans, combines and calculates metrics.  Output is a list of 4 data frames: 

| DF | Meaning | 
|:---|:----------------------|
| `cs_OR`        | Cross Section by STATE, RPTYEAR, OFFGENERAL, RACE (offense and race) |
| `cs_O`         | Cross Section by STATE, RPTYEAR, OFFGENERAL (offense) |
| `cs_R`         | Cross Section by STATE, RPTYEAR, RACE (race) |
| `cs_t`         | Cross Section by STATE, RPTYEAR (total)  |

```{r}
calc$combine_and_calcrates()
```



## Metrics

::: grid
::: g-col-6
Values:\
$n$ revocation count\
$N$ population estimate\
$R$ rate\
$I$ Relative rate index
:::

<!--end {.g-col-6} -->

::: g-col-6
Sub-text:\
$s$ State\
$o$ offense general category\
$r$ race/ethnicity\
$y$ year
:::

<!--end {.g-col-6} -->
:::

<!-- end {.grid}-->

::: panel-tabset
### Revocation Counts, $n$

Count the individual level data from NCRP by specific metrics.

| DF      | Equation      | Meaning                                                                 |
|:---------------|:-----------------|:-------------------------------------|
| `cs_OR` | $n^{sy}_{or}$ | Revocation count by STATE, RPTYEAR, OFFGENERAL, RACE (offense and race) |
| `cs_O`  | $n^{sy}_{o}$  | Revocation count by STATE, RPTYEAR, OFFGENERAL (offense)                |
| `cs_R`  | $n^{sy}_{r}$  | Revocation count by STATE, RPTYEAR, RACE (race)                         |
| `cs_t`  | $n^{sy}$      | Revocation count by STATE, RPTYEAR (total)                              |

### Rate, $R$

Revocation counts for a specific cross section divided by the population estimate for that specific cross section. Population is available by state, year, and race/ethnicity.

| DF      | Equation                                                       | Meaning                                                     |
|:---------------|:-----------------|:-------------------------------------|
| `cs_OR` | $R^{sy}_{or} = \frac{n^{sy}_{or} }{N^{sy}_{r} }$ | Rate by STATE, RPTYEAR, OFFGENERAL, RACE (offense and race) |
| `cs_O`  | $R^{sy}_{o} = \frac{n^{sy}_{o} }{N^{sy} }$       | Rate by STATE, RPTYEAR, OFFGENERAL (offense)                |
| `cs_R`  | $R^{sy}_{r} = \frac{n^{sy}_{r} }{N^{sy}_{r} }$   | Rate by STATE, RPTYEAR, RACE (race)                         |
| `cs_t`  | $R^{sy} = \frac{n^{sy} }{N^{sy} }$               | Rate by STATE, RPTYEAR (total)                              |


#### Rate per 

| Variable | Equation | Meaning | 
|:----|:------|:---------------|
|`RATE` | $R$ | plain rate | 
|`RATE_1K` | $R \cdot 1,000$ | Rate per 1,000 | 
|`RATE_100K` | $R \cdot 100,000$ | Rate per 100,000 | 
|`RATE_1MIL` | $R \cdot 1,000,000$ | Rate per 1,000,000 | 



### Relative Rate Index (RRI), $I$

Relative Rate Index is compare the $r = 1$ (White) to the other race/ethnicity groups.

*Note:* The RRI is calculated for all four race groups but will only be shown for $r = 2$ (Black) and $r = 3$ (Hispanic). When $r = 1$ (White) $\implies I = 1$. The last category, $r = 4$ (Other) is removed due to small counts and difficultly gather meaning from 'Other' category.

| DF      | Equation                                          | Meaning                                                    |
|:---------------|:-----------------|:-------------------------------------|
| `cs_OR` | $I^{sy}_{or} = \frac{R^{sy}_{or} }{R^{sy}_{o1} }$ | RRI by STATE, RPTYEAR, OFFGENERAL, RACE (offense and race) |
| `cs_O`  | N/A                                               | N/A                                                        |
| `cs_R`  | $I^{sy}_{r} = \frac{R^{sy}_{r} }{R^{sy}_{1} }$    | RRI by STATE, RPTYEAR, RACE (race)                         |
| `cs_t`  | N/A                                               | N/A                                                        |
:::

<!-- end {.panel-tabset} -->



:::
<!-- end {.panel-tabset} -->
