---
title: "NCRP Data Exploration: Revocations 2015-2019" 
date: "Last updated/ran: `r Sys.time()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 10)

library(tidyverse)
library(csgjcr)
library(janitor)
library(kableExtra)
library(plotly)
library(geofacet)
library(scales)

box::use(
  scales[percent, comma]
  , ./STCNVRT
)

logger::log_layout(logger::layout_glue_colors)
#logger::log_threshold("TRACE")

CC_path <- csg_sp_path("CC/DATA/Raw/NCRP/ICPSR_38048-V1/ICPSR_38048")

SPLINK_codebook38047 <- "https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2FNCRP%5Finfo%2F38047%2DCodebook%2F38047%2DCodebook%2Epdf&parent=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2FNCRP%5Finfo%2F38047%2DCodebook"

SPLINK_codebook38048 <- "https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2FNCRP%5Finfo%2F38048%2DCodebook%2F38048%2DCodebook%2Epdf&parent=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2FNCRP%5Finfo%2F38048%2DCodebook"

```

```{r import-and-rename-files}
#load(file.path(CC_path,"DS0001","38048-0001-Data.rda"))
load(file.path(CC_path,"DS0002","38048-0002-Data.rda"))
```

```{r}
# want to look at ADMTYPE = (2) Parole return/revocation 
## last 5 years - 2015, 2016, 2017, 2018, 2019
ADM_38048 <- da38048.0002 %>% 
  filter(RPTYEAR >= 2015)
rm(da38048.0002)

revocations <- ADM_38048 %>% 
  filter(as.integer(ADMTYPE) == 2) 


# check 
check <- revocations %>% count(ADMTYPE)
if (nrow(check) != 1){
  logger::log_error("There are more than one ADMTYPE in filtered data")
}  else {
  logger::log_trace("Only one type of value for ADMTYPE")
}

if (check[1,1] == "Revocations"){ #"(2) Parole return/revocation"
  logger::log_fatal("ADMTYPE filtered is not equal to revocations")
} else {
  logger::log_trace("Type of ADMTYPE == (2) Parole return/revocation")
}
rm(check)



addprop <- function(DF){
  DF %>%
    mutate(prop = n/sum(n)) %>% 
    adorn_totals()
}


maketable <- function(DF, title = NULL, allprop = FALSE, totallastrow = FALSE){
  
  if (allprop == FALSE){
    num_cols <- which(sapply(DF, is.numeric) == TRUE & colnames(DF) != "prop") 
    prop_col <- which(colnames(DF) == "prop")
  } else {
    num_cols <- NULL
    prop_col <- which(sapply(DF, is.numeric) == TRUE)
  }
  
  
  main <- DF %>% 
    mutate_at(.vars = num_cols, scales::comma) %>% 
    mutate_at(.vars = prop_col, scales::percent) %>% 
    kable(align = paste(c("l", rep("r", ncol(DF)-1)), collapse = ""), caption = title, escape = F) %>% 
    kable_styling() 
  
  if (totallastrow == TRUE){
    OUT <- main %>% 
      row_spec(nrow(DF), bold = TRUE, extra_css = "border-top: 1px solid;")
  } else {
    OUT <- main
  }
  
  return(OUT)

}
```

# {.tabset}

## Quick Overview

```{r}
revocations %>% skimr::skim_without_charts() %>% print(., n=0)
```

```{r}
revocations %>% count(RACE) %>% 
  addprop() %>% maketable(totallastrow = TRUE) %>% 
  column_spec(2:3, width = "15%")

revocations %>% count(SEX) %>% 
  addprop() %>% maketable(totallastrow = TRUE) %>% 
  column_spec(2:3, width = "15%")

revocations %>% count(RPTYEAR) %>% 
  addprop() %>% maketable(totallastrow = TRUE) %>% 
  column_spec(2:3, width = "15%")

revocations %>% count(OFFGENERAL) %>% 
  addprop() %>% maketable(totallastrow = TRUE) %>% 
  column_spec(2:3, width = "15%")
```


## OFFGENERAL by RPTYEAR by RACE 

### OFFGENERAL by RPTYEAR 

```{r}
wide_table <- revocations %>% count(RPTYEAR, OFFGENERAL)  %>% 
  pivot_wider(names_from = RPTYEAR, values_from = n) %>% 
  adorn_totals() 

long_table <- wide_table %>% 
  pivot_longer(cols = -1, names_to = "RPTYEAR", values_to = "n") 

# revocations %>% count(RPTYEAR, OFFGENERAL) %>% 
#   ggplot(aes(x = RPTYEAR, y = n)) + 
#   geom_point() + 
#   geom_line() + 
#   facet_grid(~OFFGENERAL) +
#   scale_y_continuous(name = NULL) + 
#   theme_bw() 

```


```{r, warning = FALSE}
wide_table %>%   
  mutate(line = "") %>% 
  maketable(totallastrow = TRUE) %>% 
  column_spec(7, image = spec_plot(split(long_table$n, long_table$OFFGENERAL), same_lim = FALSE))
```


### OFFGENERAL by RACE  {.tabset}

```{r}
revocations %>% count(OFFGENERAL, RACE) %>% 
  pivot_wider(names_from = OFFGENERAL, values_from = n) %>% 
  adorn_totals() %>% maketable(totallastrow = TRUE)

YOR_df <- revocations %>% count(RPTYEAR, OFFGENERAL, RACE) %>% 
  group_by(RPTYEAR, OFFGENERAL) %>%
  mutate(
      prop = n/sum(n)
    , perc = round(prop*100, digits = 2)
  )   #prop: % of specific race within off category by year
```


The main general offense categories (Violent, Property, Drugs, Public order) all saw a decrease in 2019.  Within the race categories there is also a decrease in the last year, though at varying degrees.  

One interesting notes is that in 2018, the number of NA race categories increased while other categories of White, Black, Hispanic, all decreased.  

#### By Year (Percent) 

```{r}
p_YOR <- YOR_df %>% 
  ggplot(aes(x = RPTYEAR, y = perc, color = RACE, text = n)) + 
  geom_line() + geom_point() + 
  facet_grid(~OFFGENERAL) +
  scale_y_continuous(name = NULL) + 
  theme_bw() + 
  theme(legend.position = "top")

p_YOR %>% ggplotly() %>% 
  layout(legend = list(orientation = 'h', x = 0, y = 1.15))
```

#### By Year (Count) 

```{r}
p_YOR <- YOR_df %>% 
  ggplot(aes(x = RPTYEAR, y = n, color = RACE, text = perc)) + 
  geom_line() + geom_point() + 
  facet_grid(~OFFGENERAL) +
  scale_y_continuous(name = NULL) + 
  theme_bw() + 
  theme(legend.position = "top")

p_YOR %>% ggplotly() %>% 
  layout(legend = list(orientation = 'h', x = 0, y = 1.15))
```

```{r}
state_YOR <- function(STATENAME){
  plotdf <- revocations %>% 
    filter(STATE == STATENAME) %>% 
    count(RPTYEAR, OFFGENERAL, RACE) %>% 
    group_by(RPTYEAR, OFFGENERAL) %>%
    mutate(
        prop = n/sum(n)
      , perc = round(prop*100, digits = 2)
    ) 
  
  ggcnt <- plotdf %>% 
    ggplot(aes(x = RPTYEAR, y = n, color = RACE, text = perc)) + 
    geom_line() + geom_point() + 
    facet_grid(~OFFGENERAL) +
    scale_y_continuous(name = NULL) + 
    scale_x_continuous(labels = c("'15", "'16", "'17", "'18", "'19")) + 
    labs(title = STATENAME) + 
    theme_bw() + 
    theme(legend.position = "top")
  
    
  ggperc <- plotdf %>% 
    ggplot(aes(x = RPTYEAR, y = perc, color = RACE, text = n)) + 
    geom_line() + geom_point() + 
    facet_grid(~OFFGENERAL) +
    scale_y_continuous(name = NULL) + 
    scale_x_continuous(labels = c("'15", "'16", "'17", "'18", "'19")) + 
    labs(title = STATENAME) + 
    theme_bw() + 
    theme(legend.position = "top")
  
  list(
      "COUNT" = ggcnt
    , "PERC" = ggperc
  )
  
}


display <- function(gg){
  gg %>% ggplotly() %>% 
  layout(legend = list(orientation = 'h', x = 0, y = 1.3))
}
```


### Select States {.tabset .tabset-dropdown}

#### Texas

```{r}
gg <- state_YOR("(48) Texas")
display(gg$COUNT)
display(gg$PERC)
```


#### Pennsylvania

```{r}
gg <- state_YOR("(42) Pennsylvania")
display(gg$COUNT)
display(gg$PERC)
```

#### New York

```{r}
gg <- state_YOR("(36) New York")
display(gg$COUNT)
display(gg$PERC)
```

#### Missouri

```{r}
gg <- state_YOR("(29) Missouri")
display(gg$COUNT)
display(gg$PERC)
```
 


## Questions 

### `RPTYEAR` Time Period 

"Universe: All persons admitted to state prison, released from state prison, or in state prison at **year-end** from 1991-2019"  
- [38048-Codebook, pg 5: Summary Data Description](`r SPLINK_codebook38048`)

"Calendar Year Reporting: NCRP collected data on admissions to prisons, releases from prison and releases from parole **for the dates January 1 through December 31**. **Data were not collected on a fiscal year basis.** Records were rejected on individual's records were rejected if the year of prison admission, prison release or parole release was not reported."  
- [NACJD Resource Guide for NCRP, NCRP Concepts and Definitions](https://www.icpsr.umich.edu/web/pages/NACJD/guides/ncrp.html#Concepts )

### `OFFGENERAL` Meaning 

"OFFGENERAL: 5-level categorization of **most serious sentenced offense**"  
- [38048-Codebook, pg 28: Prison Admissions](`r SPLINK_codebook38048`)

**QUESTION:** what does `OFFGENERAL` mean for revocations?
"The OFFGENERAL is the most serious sentenced offense, so it does refers back to the original most serious offense they were **convicted of** – not the reason someone was revoked.  The clue here is that it says “SENTENCED OFFENSE” – and parole revocations do not include a new sentenced offense." - Jess Saunders 


### Overall Downward Trend in Admissions 

```{r}
wide_table <-ADM_38048 %>% 
  count(RPTYEAR, ADMTYPE) %>% 
  pivot_wider(names_from = RPTYEAR, values_from = n) %>% 
  adorn_totals() 

long_table <- wide_table %>% 
  pivot_longer(cols = -1, names_to = "RPTYEAR", values_to = "n") 
```

```{r, warning = FALSE}
wide_table %>%   
  mutate(line = "") %>% 
  maketable(totallastrow = TRUE) %>% 
  column_spec(7, image = spec_plot(split(long_table$n, long_table$ADMTYPE), same_lim = FALSE))
```


### States submit data 

```{r}
ustate <- sort(unique(ADM_38048$STATE))
```

Total unique states in ADM_38048 data set: `r length(ustate)`


```{r}
state_data <- bind_rows(
    ADM_38048 %>% 
      distinct(RPTYEAR, STATE) %>% 
      group_by(RPTYEAR) %>% 
      summarize(state_list = list(sort(STATE))) %>% 
      mutate(type = "All Admissions (ADM_38048)")
  , revocations %>% 
      distinct(RPTYEAR, STATE) %>% 
      group_by(RPTYEAR) %>% 
      summarize(state_list = list(sort(STATE))) %>% 
      mutate(type = "ADMTYPE == Revocations Only")
  ) %>% 
  rowwise() %>% 
  mutate(
      n_states = length(state_list)
    , missing_state = list(setdiff(ustate, state_list))
  ) %>% 
  ungroup() %>% 
  mutate(missing_state_char = sapply(missing_state, paste, collapse = "<br>")) 

state_data %>% 
  select(RPTYEAR, type, n_states) %>% 
  pivot_wider(names_from = RPTYEAR, values_from = n_states) %>% 
  kable(escape = F, caption = "Count of States with data") %>% 
  kable_styling()
  

state_data %>%
  select(RPTYEAR, type, missing_state_char) %>% 
  mutate(missing_state_char = str_replace_all(missing_state_char, c("\\("="", "\\)"=""))) %>% 
  pivot_wider(names_from = RPTYEAR, values_from = missing_state_char) %>% 
  kable(escape = F, caption = "States WITHOUT data") %>% 
  kable_styling()
```

### Revocation Data by RACE {.tabset}

```{r, fig.height = 8}
state_race <- revocations %>% 
  count(RPTYEAR, STATE, RACE) %>% 
  group_by(RPTYEAR, STATE) %>% 
  mutate(total_yrstate = sum(n)) %>% 
  ungroup() %>% 
  mutate(prop = n/total_yrstate) %>% 
  rowwise() %>% 
  mutate(
      fips = str_sub(STATE, 2, 3)
    , name = str_sub(STATE, 6, -1)
    , abb  = STCNVRT$cnvrt(fips, "fips", "abb_usps")
  ) %>% 
  ungroup()

```


#### NA 

```{r, fig.height = 8, warning = FALSE}
state_race %>% 
  filter(is.na(RACE)) %>% 
  ggplot(aes(x = RPTYEAR, y = prop, group = abb)) + 
  geom_area() + 
  geom_point() + 
  geom_point(data = filter(state_race, is.na(RACE) & prop < 0.01), color = "grey30", fill = "white", shape = 21) + 
  facet_geo(~abb, grid = "us_state_grid2") +  
  labs(
    title = "Percent of NA (Missing) RACE in Revocations for years 2015-2019"
    , subtitle = "If prop < 1% shown with empty circle"
  ) + 
  scale_y_continuous(
      name = NULL
    , breaks = c(0, 0.5, 1)
    , labels = scales::percent
    , expand = expansion(mult=0.10, add=0)
  ) + 
  scale_x_continuous(
      name = NULL
    , labels = ~paste0("'", substr(., 3, 4))
  ) + 
  theme_minimal() + 
  theme(
      legend.position = "top"
    , panel.grid.minor = element_blank()
    , axis.text = element_text(size = 6)
    , strip.background = element_rect(fill = "grey90", color = NA)
   , strip.text = element_text(margin = margin(t=2, r=0, b=3, l=0, unit = "pt"))
  )
```

```{r}
obs_by_state <- full_join(
    revocations %>% distinct(RPTYEAR, STATE) %>% count(STATE) %>% rename(n_yrsofdata = n)
  , revocations %>% count(STATE) %>% rename(n_totalobs = n)
  , by = "STATE"
) %>% 
  mutate(avgobsperyear = n_totalobs/n_yrsofdata)

```


```{r}

# state_race %>% 
#   full_join(., tibble(STATE = ustate), by = "STATE")


na_df <- state_race %>% 
  full_join(., tibble(STATE = ustate), by = "STATE") %>% 
  group_by(RPTYEAR, STATE) %>% 
  mutate(prop_NA = ifelse(NA %in% RACE, prop[which(is.na(RACE))], 0)) %>% 
  ungroup() %>% 
  distinct(RPTYEAR, STATE, abb, prop_NA) %>% 
  pivot_wider(names_from = RPTYEAR, values_from = prop_NA) %>% 
  arrange(STATE) %>% 
  select(-`NA`) %>% 
  left_join(., obs_by_state, by = "STATE") 


add_perc_fmt <- function(val){
  case_when(
      val == 0                        ~ "0%"
    , val == 1                        ~ "100%"
    , round(val*100, digits = 1) <  1 ~"<1%"
    , round(val*100, digits = 1) > 99 ~ ">99%"
    , TRUE                            ~ percent(val, accuracy = 1)
  )
}


na_df %>% 
  select(-abb) %>% 
  DT::datatable(rownames = FALSE) %>% 
  DT::formatPercentage(columns = c("2015", "2016", "2017", "2018", "2019"), digits = 2) %>% 
  DT::formatRound(columns = c("n_totalobs", "avgobsperyear"), digits = 0)
  # mutate_at(vars(as.character(2015:2019)), add_perc_fmt) %>% 
  # mutate_if(is.numeric, comma_format(accuracy = 1)) %>% 
  # kable(align = "lrrrrrrrr") %>% 
  # kable_styling() %>% 
  # column_spec(2, background = spec_color(na_df$`2015`, alpha = 0.2)) %>% 
  # column_spec(3, background = spec_color(na_df$`2016`, alpha = 0.2)) %>% 
  # column_spec(4, background = spec_color(na_df$`2017`, alpha = 0.2)) %>% 
  # column_spec(5, background = spec_color(na_df$`2018`, alpha = 0.2)) %>% 
  # column_spec(6, background = spec_color(na_df$`2019`, alpha = 0.2)) %>% 
  # column_spec(8, background = spec_color(na_df$n_totalobs   , alpha = 0.25, option = "E")) %>% 
  # column_spec(9, background = spec_color(na_df$avgobsperyear, alpha = 0.25, option = "E"))
```



#### Percent 

```{r, fig.height = 8}
state_race %>% 
  ggplot(aes(x = RPTYEAR, y = prop, color = RACE)) + 
  geom_line() + 
  geom_point() + 
  facet_geo(~abb, grid = "us_state_grid2") +  
  labs(title = "Percent of RACE in Revocations for years 2015-2019") + 
  scale_y_continuous(
      name = NULL
    , breaks = c(0, 0.5, 1)
    , labels = scales::percent
    , expand = expansion(mult=0.10, add=0)
  ) + 
  scale_x_continuous(
      name = NULL
    , labels = ~paste0("'", substr(., 3, 4))
  ) + 
  theme_minimal() + 
  theme(
      legend.position = "top"
    , panel.grid.minor = element_blank()
    , axis.text = element_text(size = 6)
    , strip.background = element_rect(fill = "grey90", color = NA)
   , strip.text = element_text(margin = margin(t=2, r=0, b=3, l=0, unit = "pt"))
  )
```

#### Counts

```{r,  fig.height = 8}
state_race %>% 
  ggplot(aes(x = RPTYEAR, y = n, color = RACE)) + 
  geom_line() + 
  geom_point() + 
  facet_geo(~abb, grid = "us_state_grid2") +  
  labs(title = "Percent of RACE in Revocations for years 2015-2019") + 
  scale_y_continuous(
      name = NULL
    , breaks = c(0, 5000, 10000)
    , labels = scales::comma_format(suffix = "k", scale=0.001)
  #  , expand = expansion(mult=0.10, add=0)
  ) + 
  scale_x_continuous(
      name = NULL
    , labels = ~paste0("'", substr(., 3, 4))
  ) + 
  theme_minimal() + 
  theme(
      legend.position = "top"
    , panel.grid.minor = element_blank()
    , axis.text = element_text(size = 6)
    , strip.background = element_rect(fill = "grey90", color = NA)
   , strip.text = element_text(margin = margin(t=2, r=0, b=3, l=0, unit = "pt"))
  )
```

