---
title: "NCRP Mock-Up: Revocations 2015-2019" 
date: "Last updated/ran: `r Sys.time()`"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r, include = FALSE}
box::use(
  box/calc
  , box/admin
)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.height = 8, fig.width = 10)

library(tidyverse)
library(highcharter)
```



```{r}
CNTRTDF <- calc$combine_and_calcrates()
```
```{r}
#copy over from Mari's code 

###app/dataframes.R
default_fonts <- c("Graphik")

gcolors <- c("#D25E2D", "#EDB799", "#C7E8F5", "#236ca7", "#D6C246", "#dcdcdc")

### app/functions.R
# custom highcharts theme for plots
hc_theme_jc2 <- hc_theme(
    #colors = c("#D25E2D", "#EDB799", "#C7E8F5", "#236ca7", "#D6C246", "#dcdcdc")
    chart = list(style = list(fontFamily = default_fonts, color = "#666666"))
  , title = list(align = "left", style = list(fontFamily = default_fonts, fontSize = "24px")) 
  , subtitle = list(align = "left", style = list(fontFamily = default_fonts, fontSize = "16px"))
  , legend = list(align = "left", verticalAlign = "top")
  , xAxis = list(
        gridLineColor = "transparent"
      , lineColor = "transparent"
      , minorGridLineColor = "transparent"
      , tickColor = "transparent"
    )
  # , yAxis = list(
  #       labels = list(enabled = FALSE)
  #     , gridLineColor = "transparent"
  #     , lineColor = "transparent"
  #     , minorGridLineColor = "transparent"
  #     , tickColor = "transparent"
  #     )
  , plotOptions = list(
      #   line = list(marker = list(enabled = FALSE))
      # , spline = list(marker = list(enabled = FALSE))
      # , area = list(marker = list(enabled = FALSE))
      # , areaspline = list(marker = list(enabled = FALSE))
      # , arearange = list(marker = list(enabled = FALSE))
       bubble = list(maxSize = "10%")
      )
)


rri_wline <-  list(list(
      value  = 1
    , color  = "#666666"
    , width  = 2
    , zIndex = 4
    , dashStyle = "Dash" #https://api.highcharts.com/class-reference/Highcharts#.DashStyleValue
    , label = list(
        text = "White (reference group)"
      , rotation = 0
      , style = list(
          color = "#666666"
        , fontWeight = "bold"
        ) #end style list
    ) #end label list
  )) #end doublelist


```

# {.tabset} 

All examples are shown with CA.  

## Line Charts {.tabset} 

```{r}
ABB <- "CA"
VAR <- "REVCNT"

fnc_highchart_ROline <- function(ABB, VAR){
  
  ptfmt <- case_when(
      VAR == "REVCNT"  ~ "{point.VAR:,.0f}" #0 decimal places 
    , VAR == "RATE_1K" ~ "{point.VAR:,.2f}" #2 decimal places 
    , VAR == "RRI"     ~ "{point.VAR:,.1f}" #1 decimal place
    )
  
  plotdata <-  CNTRTDF$OR %>% 
    filter(ABB == !!ABB) %>% 
    rename("VAR" = !!VAR) %>% 
    filter(!RACE %in% admin$lev_RACE[5]) %>% #REMOVE MISSING RACE 
    filter(!OFFGENERAL %in% admin$lev_OFFGENERAL[-c(1:4)])#REMOVE OTHER/MISSING OFFGENERAL 
    
  map(admin$lev_OFFGENERAL[1:4], function(OG){
    
    plotdata %>% 
      filter(OFFGENERAL == OG) %>% 
      hchart("line"
        , hcaes(x = RPTYEAR, y = VAR, group = RACE)
        , color = gcolors[1:4] 
        , tooltip = list(pointFormat = ptfmt)
      ) %>% 
      hc_title(text = OG) %>% 
      hc_yAxis(min = 0, max = max(plotdata$VAR, na.rm = TRUE), title = list(text = "")) %>% 
      hc_xAxis(title = list(text = "")) %>% 
      hc_add_theme(hc_theme_jc2)
  }) %>% 
  hw_grid(rowheight = 350, ncol = 4) %>% 
    htmltools::browsable()
  
}
```
### Revocation Counts 

```{r}
fnc_highchart_ROline("CA", "REVCNT")
```

### Rate Per 1,000

```{r}
fnc_highchart_ROline("CA", "RATE_1K")
```

### Relative Rate Index 

```{r}
fnc_highchart_ROline("CA", "RRI")
```


## Other RRI Options {.tabset}

### Column 

```{r}
## COLUMN CHART
ABB <- "CA"
VAR <- "RRI"

#fnc_highchart_RO <- function(ABB, VAR){

  ptfmt <- case_when(
      VAR == "REVCNT"  ~ "{point.VAR:,.0f}" #0 decimal places 
    , VAR == "RATE_1K" ~ "{point.VAR:,.2f}" #2 decimal places 
    , VAR == "RRI"     ~ "{point.VAR:,.1f}" #1 decimal place
    )
  
  plotdata <-  CNTRTDF$OR %>% 
    filter(ABB == !!ABB) %>% 
    rename("VAR" = !!VAR) %>% 
    filter(!RACE %in% admin$lev_RACE[-c(2:3)]) %>% #REMOVE MISSING/OTHER RACE 
    filter(!OFFGENERAL %in% admin$lev_OFFGENERAL[-c(1:4)])#REMOVE OTHER/MISSING OFFGENERAL 

    
  map(admin$lev_OFFGENERAL[1:4], function(OG){
    
    plotdata %>% 
      filter(OFFGENERAL == OG) %>% 
      hchart("column"
        , hcaes(x = RPTYEAR, y = VAR, group = RACE)
        , color = gcolors[2:3]
        , tooltip = list(pointFormat = ptfmt) 
      ) %>% 
      hc_title(text = OG) %>% 
      hc_yAxis(min = min(plotdata$VAR, na.rm = TRUE), max = max(plotdata$VAR, na.rm = TRUE), title = list(text = ""), plotLines = rri_wline) %>% 
      hc_xAxis(title = list(text = "")) %>% 
      hc_add_theme(hc_theme_jc2)
  }) %>% 
  hw_grid(rowheight = 350, ncol = 4) %>% 
    htmltools::browsable()
#}
  
```
### Bar {.tabset} 

#### Year by Rate by OFFGENEARL 

```{r}
##  BAR CHART
ABB <- "CA"
VAR <- "RRI"

#fnc_highchart_RO <- function(ABB, VAR){
  ptfmt <- case_when(
      VAR == "REVCNT"  ~ "{point.VAR:,.0f}" #0 decimal places 
    , VAR == "RATE_1K" ~ "{point.VAR:,.2f}" #2 decimal places 
    , VAR == "RRI"     ~ "{point.VAR:,.1f}" #1 decimal place
    )
  
  plotdata <-  CNTRTDF$OR %>% 
    filter(ABB == !!ABB) %>% 
    rename("VAR" = !!VAR) %>% 
    filter(!RACE %in% admin$lev_RACE[-c(2:3)]) %>% #REMOVE MISSING RACE 
    filter(!OFFGENERAL %in% admin$lev_OFFGENERAL[-c(1:4)])#REMOVE OTHER/MISSING OFFGENERAL 

    
  map(admin$lev_OFFGENERAL[1:4], function(OG){
    
    plotdata %>% 
      filter(OFFGENERAL == OG) %>% 
      hchart("bar"
        , hcaes(x = RPTYEAR, y = VAR, group = RACE)
        , color = gcolors[2:3]
        , tooltip = list(pointFormat = ptfmt) 
      ) %>% 
      hc_title(text = OG) %>% 
      hc_yAxis(min = min(plotdata$VAR, na.rm = TRUE), max = max(plotdata$VAR, na.rm = TRUE), title = list(text = ""), plotLines = rri_wline) %>% 
      hc_xAxis(title = list(text = "")) %>% 
      hc_add_theme(hc_theme_jc2)
  }) %>% 
  hw_grid(rowheight = 350, ncol = 4) %>% 
    htmltools::browsable()
#}
  
```


#### OFFGENERAL by Rate by Year 

```{r}
##  BAR CHART
ABB <- "CA"
VAR <- "RRI"

#fnc_highchart_RO <- function(ABB, VAR){
  
  ptfmt <- case_when(
      VAR == "REVCNT"  ~ "{point.VAR:,.0f}" #0 decimal places 
    , VAR == "RATE_1K" ~ "{point.VAR:,.2f}" #2 decimal places 
    , VAR == "RRI"     ~ "{point.VAR:,.1f}" #1 decimal place
    )
  
  plotdata <-  CNTRTDF$OR %>% 
    filter(ABB == !!ABB) %>% 
    rename("VAR" = !!VAR) %>% 
    filter(!RACE %in% admin$lev_RACE[-c(2:3)]) %>% #REMOVE MISSING RACE 
    filter(!OFFGENERAL %in% admin$lev_OFFGENERAL[-c(1:4)])#REMOVE OTHER/MISSING OFFGENERAL 

    
  map(sort(unique(plotdata$RPTYEAR)), function(YR){
    
    plotdata %>% 
      filter(RPTYEAR == YR) %>% 
      hchart("bar"
        , hcaes(x = OFFGENERAL, y = VAR, group = RACE)
        , color = gcolors[2:3]
        , tooltip = list(pointFormat = ptfmt) 
      ) %>% 
      hc_title(text = YR) %>% 
      hc_yAxis(min = 0, max = max(plotdata$VAR, na.rm = TRUE), title = list(text = ""), plotLines = rri_wline) %>% 
      hc_xAxis(title = list(text = "")) %>% 
      hc_add_theme(hc_theme_jc2)
  }) %>%
  hw_grid(rowheight = 350, ncol = 5) %>%
    htmltools::browsable()
#}
  
```

### Diverging Bar(X)

- recalculate RRI when group is less likely than White baseline 
- i.e. 'Other' = 0.5 --> -1/0.5 = -2; otherwise won't diverge 
- left side is White is #x more likely than ___
- right side is ___ is #x more likely than white 

```{r}
## DIVERGING BAR CHART
ABB <- "CA"
VAR <- "RRI"

#fnc_highchart_RO <- function(ABB, VAR){
  
  ptfmt <- case_when(
      VAR == "REVCNT"  ~ "{point.VAR:,.0f}" #0 decimal places 
    , VAR == "RATE_1K" ~ "{point.VAR:,.2f}" #2 decimal places 
    , VAR == "RRI"     ~ "{point.VAR:,.1f}" #1 decimal place
    )
  
  plotdata <-  CNTRTDF$OR %>% 
    mutate(RRI = ifelse(RRI < 1, -1/RRI, RRI)) %>% 
    filter(ABB == !!ABB) %>% 
    rename("VAR" = !!VAR) %>% 
    filter(!RACE %in% admin$lev_RACE[-c(2:4)]) %>% #REMOVE MISSING RACE 
    filter(!OFFGENERAL %in% admin$lev_OFFGENERAL[-c(1:4)])#REMOVE OTHER/MISSING OFFGENERAL 

    
  map(admin$lev_OFFGENERAL[1:4], function(OG){
    
    plotdata %>% 
      filter(OFFGENERAL == OG) %>% 
      hchart("bar"
        , hcaes(x = RPTYEAR, y = VAR, group = RACE)
        , color = gcolors[2:4]
        , tooltip = list(pointFormat = ptfmt) 
      ) %>% 
      hc_title(text = OG) %>% 
      hc_yAxis(min = min(plotdata$VAR, na.rm = TRUE), max = max(plotdata$VAR, na.rm = TRUE), title = list(text = "")) %>% 
      hc_xAxis(title = list(text = "")) %>% 
      hc_add_theme(hc_theme_jc2)
  }) %>% 
  hw_grid(rowheight = 350, ncol = 4) %>% 
    htmltools::browsable()
#}
  
```


### DrillDown(X) 

- can't get drilldown plot to separate RACE into side by side plots 
- drilldown seems to only work well with single column charts (i.e. plain counts)

```{r}
  df_dd <- 
  CNTRTDF$OR %>% 
    filter(ABB == !!ABB, RACE != "White", OFFGENERAL %in% admin$lev_OFFGENERAL[1:4]) %>% 
    mutate(RPTYEAR = as.character(RPTYEAR)) %>% 
    select(RPTYEAR, RACE, OFFGENERAL, RRI) %>% 
    group_nest(RPTYEAR) %>% 
    mutate(
        id = RPTYEAR
      , type = "column"
      , data = map(data, mutate, name = OFFGENERAL, y = RRI, group = RACE)
      , data = map(data, list_parse)
    )

  
  df <- CNTRTDF$R %>% 
    mutate(RPTYEAR = as.character(RPTYEAR)) %>% 
    filter(ABB == !!ABB, RACE != "White") 
  
  
  hchart(
    df, "column", 
    hcaes(x = RPTYEAR, y = RRI, group = RACE,  drilldown = RPTYEAR), 
    color = gcolors[2:4]
  ) %>% 
  hc_drilldown(
    allowPointDrilldown = TRUE,
    series = list_parse(df_dd)
  ) 
```

