---
title: "NCRP Data Exploration: Revocations 2015-2019" 
date: "Last updated/ran: `r Sys.time()`"
output: html_document
editor_options: 
  chunk_output_type: console
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 10)


library(tidyverse)
library(csgjcr)
library(janitor)
library(kableExtra)
library(plotly)


box::use(
  scales[percent, comma]
)

logger::log_layout(logger::layout_glue_colors)
#logger::log_threshold("TRACE")

CC_path <- csg_sp_path("CC/DATA/Raw/NCRP/ICPSR_38048-V1/ICPSR_38048")

```



```{r import-and-rename-files}

#load(file.path(CC_path,"DS0001","38048-0001-Data.rda"))
load(file.path(CC_path,"DS0002","38048-0002-Data.rda"))

## RECODE 
levels_ADMTYPE <- c(
    New        = "(1) New court commitment"
  , Revocation = "(2) Parole return/revocation"
  , Other      = "(3) Other admission (including unsentenced, transfer, AWOL/escapee return)"
)

levels_RACE <- c(
    White    = "(1) White, non-Hispanic"
  , Black    = "(2) Black, non-Hispanic"
  , Hispanic = "(3) Hispanic, any race"
  , Other    = "(4) Other race(s), non-Hispanic"
)

levels_OFFGENERAL <- c(
    Violent = "(1) Violent"
  , Property = "(2) Property"
  , Drugs = "(3) Drugs"
  , `Public order` = "(4) Public order"
  , `Other/unspecified` = "(5) Other/unspecified"
)

levels_SEX <- c(
    `M` = "(1) Male"
  , `F` = "(2) Female"
)



```



```{r}
# want to look at ADMTYPE = (2) Parole return/revocation 
## last 5 years - 2015, 2016, 2017, 2018, 2019
revocations <- da38048.0002 %>% 
  filter(as.integer(ADMTYPE) == 2, RPTYEAR >= 2015) 
#%>% 
  # mutate(
  #     ADMTYPE    = fct_recode(ADMTYPE   , !!!levels_ADMTYPE)
  #   , RACE       = fct_recode(RACE      , !!!levels_RACE)
  #   , OFFGENERAL = fct_recode(OFFGENERAL, !!!levels_OFFGENERAL)
  # )

# check 
check <- revocations %>% count(ADMTYPE)
if (nrow(check) != 1){
  logger::log_error("There are more than one ADMTYPE in filtered data")
}  else {
  logger::log_trace("Only one type of value for ADMTYPE")
}

if (check[1,1] == "Revocations"){ #"(2) Parole return/revocation"
  logger::log_fatal("ADMTYPE filtered is not equal to revocations")
} else {
  logger::log_trace("Type of ADMTYPE == (2) Parole return/revocation")
}
rm(check)



addprop <- function(DF){
  DF %>%
    mutate(prop = n/sum(n)) %>% 
    adorn_totals()
}


maketable <- function(DF, title = NULL, allprop = FALSE, totallastrow = FALSE){
  
  if (allprop == FALSE){
    num_cols <- which(sapply(DF, is.numeric) == TRUE & colnames(DF) != "prop") 
    prop_col <- which(colnames(DF) == "prop")
  } else {
    num_cols <- NULL
    prop_col <- which(sapply(DF, is.numeric) == TRUE)
  }
  
  
  main <- DF %>% 
    mutate_at(.vars = num_cols, scales::comma) %>% 
    mutate_at(.vars = prop_col, scales::percent) %>% 
    kable(align = paste(c("l", rep("r", ncol(DF)-1)), collapse = ""), caption = title) %>% 
    kable_styling() 
  
  if (totallastrow == TRUE){
    OUT <- main %>% 
      row_spec(nrow(DF), bold = TRUE, extra_css = "border-top: 1px solid;")
  } else {
    OUT <- main
  }
  
  return(OUT)

}

```


# Quick Overview


```{r}
revocations %>% skimr::skim_without_charts() %>% print(., n=0)
```



```{r}
revocations %>% count(RACE) %>% 
  addprop() %>% maketable(totallastrow = TRUE) %>% 
  column_spec(2:3, width = "15%")

revocations %>% count(SEX) %>% 
  addprop() %>% maketable(totallastrow = TRUE) %>% 
  column_spec(2:3, width = "15%")

revocations %>% count(RPTYEAR) %>% 
  addprop() %>% maketable(totallastrow = TRUE) %>% 
  column_spec(2:3, width = "15%")

revocations %>% count(OFFGENERAL) %>% 
  addprop() %>% maketable(totallastrow = TRUE) %>% 
  column_spec(2:3, width = "15%")
```



## OFFGENERAL by RPTYEAR by RACE 

### OFFGENERAL by RPTYEAR 

```{r}
wide_table <- revocations %>% count(RPTYEAR, OFFGENERAL)  %>% 
  pivot_wider(names_from = RPTYEAR, values_from = n) %>% 
  adorn_totals() 

long_table <- wide_table %>% 
  pivot_longer(cols = -1, names_to = "RPTYEAR", values_to = "n") 

# revocations %>% count(RPTYEAR, OFFGENERAL) %>% 
#   ggplot(aes(x = RPTYEAR, y = n)) + 
#   geom_point() + 
#   geom_line() + 
#   facet_grid(~OFFGENERAL) +
#   scale_y_continuous(name = NULL) + 
#   theme_bw() 

```


```{r, warning = FALSE}
wide_table %>%   
  mutate(line = "") %>% 
  maketable(totallastrow = TRUE) %>% 
  column_spec(7, image = spec_plot(split(long_table$n, long_table$OFFGENERAL), same_lim = FALSE))
```


### OFFGENERAL by RACE  {.tabset}

```{r}
revocations %>% count(OFFGENERAL, RACE) %>% 
  pivot_wider(names_from = OFFGENERAL, values_from = n) %>% 
  adorn_totals() %>% maketable(totallastrow = TRUE)

YOR_df <- revocations %>% count(RPTYEAR, OFFGENERAL, RACE) %>% 
  group_by(RPTYEAR, OFFGENERAL) %>%
  mutate(
      prop = n/sum(n)
    , perc = round(prop*100, digits = 2)
  )   #prop: % of specific race within off category by year
```


The main general offense categories (Violent, Property, Drugs, Public order) all saw a decrease in 2019.  Within the race categories there is also a decrease in the last year, though at varying degrees.  

One interesting notes is that in 2018, the number of NA race categories increased while other categories of White, Black, Hispanic, all decreased.  

#### By Year (Percent) 

```{r}
p_YOR <- YOR_df %>% 
  ggplot(aes(x = RPTYEAR, y = perc, color = RACE, text = n)) + 
  geom_line() + geom_point() + 
  facet_grid(~OFFGENERAL) +
  scale_y_continuous(name = NULL) + 
  theme_bw() + 
  theme(legend.position = "top")

p_YOR %>% ggplotly() %>% 
  layout(legend = list(orientation = 'h', x = 0, y = 1.15))
```

#### By Year (Count) 

```{r}
p_YOR <- YOR_df %>% 
  ggplot(aes(x = RPTYEAR, y = n, color = RACE, text = perc)) + 
  geom_line() + geom_point() + 
  facet_grid(~OFFGENERAL) +
  scale_y_continuous(name = NULL) + 
  theme_bw() + 
  theme(legend.position = "top")

p_YOR %>% ggplotly() %>% 
  layout(legend = list(orientation = 'h', x = 0, y = 1.15))
```