---
title: "NCRP Mock-Up: Revocations 2015-2019" 
date: "Last updated/ran: `r Sys.time()`"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r}
box::use(
    box/admin
  , box/clean_SC
)
```


### SC --> NCRP


```{r}
clean_SC$prep
```


#### Race Crosswalk 


SC has `ORIGIN`(Ethnicity) and `RACE` that need to be fit into the NCRP `RACE` categories.  


| SC `ORIGIN` | SC `RACE` | NCRP `RACE` | Label | 
|:------  |:------------|:---------  |:---|
| 1 (Not Hispanic) | 1 (White Alone) | (1) White, non-Hispanic | `r admin$lev_RACE[1]` | 
| 1 (Not Hispanic) | 2 (Black or African American Alone) | (2) Black, non-Hispanic | `r admin$lev_RACE[2]` | 
| 1 (Not Hispanic) | 3 (American Indian or Alaska Native Alone) | (4) Other race(s), non-Hispanic | `r admin$lev_RACE[4]` | 
| 1 (Not Hispanic) | 4 (Asian Alone) | (4) Other race(s), non-Hispanic | `r admin$lev_RACE[4]` | 
| 1 (Not Hispanic) | 5 (Native Hawaiian and Other Pacific Islander Alone) | (4) Other race(s), non-Hispanic | `r admin$lev_RACE[4]` | 
| 1 (Not Hispanic) | 6 (Two or more races) | (4) Other race(s), non-Hispanic | `r admin$lev_RACE[4]` | 
| 2 (Hispanic) | 1 (White Alone)                                      | (3) Hispanic, any race | `r admin$lev_RACE[3]` | 
| 2 (Hispanic) | 2 (Black or African American Alone)                  | (3) Hispanic, any race | `r admin$lev_RACE[3]` | 
| 2 (Hispanic) | 3 (American Indian or Alaska Native Alone)           | (3) Hispanic, any race | `r admin$lev_RACE[3]` | 
| 2 (Hispanic) | 4 (Asian Alone)                                      | (3) Hispanic, any race | `r admin$lev_RACE[3]` | 
| 2 (Hispanic) | 5 (Native Hawaiian and Other Pacific Islander Alone) | (3) Hispanic, any race | `r admin$lev_RACE[3]` | 
| 2 (Hispanic) | 6 (Two or more races)                                | (3) Hispanic, any race | `r admin$lev_RACE[3]` | 


```{r}
admin$lev_RACE
admin$SC_RE
```


