---
title: "NCRP Revocations Rate Comparison" 
description: "Last User: `r stringr::str_sub(getwd(), 10, stringr::str_locate(stringr::str_sub(getwd(), 10, -1), '/')[1]+10-2)`"
date: last-modified
date-format: "YYYY-MM-DD HH:mm:ss"
published-title: Last Modified
doi: "`r Sys.time()`"
doi-title: Last Ran
format: 
  html:
    page-layout: full
    fontsize: 1em
execute: 
  echo: false
editor: source
self-contained: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| message: FALSE
box::use(
    box/admin
  , box/calc
  , glue[glue]
)


library(tidyverse)
library(geofacet)
library(scales)
library(knitr)

denom_SC <- calc$combine_and_calcrates(pop_denom = "SC")
denom_APS<- calc$combine_and_calcrates(pop_denom = "AParS")
gcolors <- c("#666666", "#D25E2D", "#236ca7", "#D6C246", "#EDB799", "#C7E8F5", "#DCDCDC")
```

All data are shown at the `OFFGENERAL`/`RACE` cross section level. 

<!-- start {.panel tabset} ALLLLLL --> 
::: {.panel-tabset} 

## State Charactersitics

```{r}
#| label: SC
rm(list = setdiff(ls(), c("denom_SC", "denom_APS", "gcolors", "admin", "calc")))
dfOR <- denom_SC$OR %>% 
  select(ABB, RPTYEAR, OFFGENERAL, RACE, REVCNT, POPEST, RATE_100K, RRI) %>% 
  left_join(., select(denom_SC$t, ABB, RPTYEAR, TOTAL_REVCNT = REVCNT), by = c("ABB", "RPTYEAR")) %>% 
  mutate(PROP_OF_TOT_REVCNT = REVCNT/TOTAL_REVCNT)

dfR <- denom_SC$R %>% 
  select(ABB, RPTYEAR, RACE, REVCNT, POPEST, RATE_100K, RRI) %>% 
  left_join(., select(denom_SC$t, ABB, RPTYEAR, TOTAL_REVCNT = REVCNT), by = c("ABB", "RPTYEAR")) %>% 
  mutate(PROP_OF_TOT_REVCNT = REVCNT/TOTAL_REVCNT)
```

<!-- start {.panel tabset} SC --> 
::: {.panel-tabset} 

### Rate per 100k

```{r}
#| label: SC-RATE
dfOR_rate <- dfOR %>% filter(RACE %in% admin$lev_RACE[1:4], OFFGENERAL %in% admin$lev_OFFGENERAL[1:4])
dfR_rate  <- dfR  %>% filter(RACE %in% admin$lev_RACE[1:4])
```

Filtered data used:  

- `RACE` equal to `r paste(admin$lev_RACE[1:4], collapse = ", ")`  
- `OFFGENERAL` equal to `r paste(admin$lev_OFFGENERAL[1:4], collapse = ", ")` 

<!-- start {.panel tabset} SC-RATE --> 
::: {.panel-tabset} 

#### Overview 


```{r}
#| label: SC-RATE-OVERVIEW-table
dfOR_rate %>% 
  select(RATE_100K, OFFGENERAL, RACE) %>% 
  group_by(OFFGENERAL, RACE) %>% 
  skimr::skim_without_charts()
```

```{r}
#| label: SC-RATE-OVERVIEW-boxplot
#| fig.width: 12
#| fig.height: 8
dfOR_rate %>% 
  filter(!is.na(RATE_100K)) %>% 
  ggplot(aes(y = OFFGENERAL, x = RATE_100K)) + 
  geom_boxplot(alpha = 0.8, fill = "grey35", color = "grey35") + 
  facet_wrap(~RACE, ncol = 1) + 
  scale_x_continuous(limits = c(0, NA), expand = c(0.01, 0)) + 
  scale_y_discrete(limits = rev) + 
  theme_bw()
```


#### State Facet


```{r}
#| label: SC-RATE-STATEFACET
#| fig.width: 12
#| fig.height: 7.5
#| warning: FALSE
RATE_statefacet <- function(OFFGEN){
  
  if (OFFGEN %in% c(1:4)){
    
    plotdf <- dfOR_rate %>% 
        filter(OFFGENERAL == admin$lev_OFFGENERAL[OFFGEN], !is.na(RATE_100K))
    title <- glue("Rate per 100,000 by Report Year (2015-2019) and RACE where OFFGENERAL = {admin$lev_OFFGENERAL[OFFGEN]}")
    
  } else if (toupper(OFFGEN) == "ALL"){
    
    plotdf <- dfR_rate %>% 
      filter(RACE %in% admin$lev_RACE[1:4], !is.na(RATE_100K))
    title <- glue("Rate per 100,000 by Report Year (2015-2019) and RACE for any OFFGENERAL")
    
  }
  
  
plotdf %>% 
  ggplot(aes(x = RPTYEAR, y = RATE_100K, color = RACE)) + 
  geom_line(size = 0.65) + 
  facet_geo(~ABB, grid = "us_state_grid2", scales = "free") + 
  scale_color_manual(values = gcolors[c(1, 2, 3, 4)])+ 
  scale_x_continuous(breaks = NULL, labels = ~substr(., 3, 4)) +
  labs(
      title = title
    , x = NULL
    , y = NULL
  ) + 
  theme_minimal() + 
  theme(
    legend.position = "top"
    , panel.grid.major.x = element_blank()
    , panel.grid.minor.x = element_blank()
    , panel.grid.minor.y = element_blank()
  )
  
}

RATE_statefacet("all")
RATE_statefacet(1)
RATE_statefacet(2)
RATE_statefacet(3)
RATE_statefacet(4)

```

:::
<!-- end {.panel tabset} SC-RATE --> 


### RRI

Filtered data used:  

- `RACE` equal to `r paste(admin$lev_RACE[2:3], collapse = ", ")`  
- `OFFGENERAL` equal to `r paste(admin$lev_OFFGENERAL[1:4], collapse = ", ")`

<!-- start {.panel tabset} SC-RRI --> 
::: {.panel-tabset} 

```{r}
#| label: SC-RRI
dfOR_rri    <- dfOR     %>% filter(RACE %in% admin$lev_RACE[2:3], OFFGENERAL %in% admin$lev_OFFGENERAL[1:4])
dfR_rri     <- dfR      %>% filter(RACE %in% admin$lev_RACE[2:3])
dfOR_rri_1l <- dfOR_rri %>% filter(RRI < 1)
dfOR_l1     <- dfOR     %>% filter(RRI < 1)
```


#### Overview 

```{r}
#| label: SC-RRI-OVERVIEW-table
dfOR_rri %>% 
  select(RRI, OFFGENERAL, RACE) %>% 
  group_by(OFFGENERAL, RACE) %>% 
  skimr::skim_without_charts()
```

```{r}
#| label: SC-RRI-OVERVIEW-boxplot
#| fig.width: 12
#| fig.height: 4
dfOR_rri %>% 
  filter(!is.na(RRI)) %>% 
  ggplot(aes(y = OFFGENERAL, x = RRI)) + 
  geom_vline(xintercept = 1, alpha = 0.5, color = "red") + 
  geom_boxplot(alpha = 0.8, fill = "grey35", color = "grey35") + 
  facet_wrap(~RACE, ncol = 1) + 
  scale_x_continuous(limits = c(0, NA), expand = c(0.01, 0)) + 
  scale_y_discrete(limits = rev) + 
  labs(subtitle = "Vertical line in red is when RRI = 1") + 
  theme_bw() + 
  theme(plot.subtitle = element_text(color = "red"))
```


#### State Facet


```{r}
#| label: SC-RRI-STATEFACET 
#| fig.width: 12
#| fig.height: 8
RRI_statefacet <- function(OFFGEN){
  
  if (OFFGEN %in% c(1:4)){
    
    plotdf <- dfOR_rri %>% 
        filter(OFFGENERAL == admin$lev_OFFGENERAL[OFFGEN], !is.na(RRI))
    wrg_o <- expand.grid(ABB = unique(plotdf$ABB), RPTYEAR = c(2015:2019)) %>% 
      mutate(RACE = "White", RRI = 1)
    title <- glue("RRI by Report Year (2015-2019) and RACE where OFFGENERAL = {admin$lev_OFFGENERAL[OFFGEN]}")
    
    
  } else if (toupper(OFFGEN) == "ALL"){
    
    plotdf <- dfR_rri %>% 
      filter(RACE %in% admin$lev_RACE[2:3], !is.na(RRI))
    wrg_o <- expand.grid(ABB = unique(plotdf$ABB), RPTYEAR = c(2015:2019)) %>% 
      mutate(RACE = "White", RRI = 1)
    title <- glue("RRI by Report Year (2015-2019) and RACE for any OFFGENERAL")
    
  }


plotdf %>% 
  full_join(., wrg_o, by = c("ABB", "RPTYEAR", "RACE", "RRI")) %>% 
  ggplot(aes(x = RPTYEAR, y = RRI, fill = RACE, alpha = RACE)) + 
  #geom_col(width = 1, alpha = 0.8, color = "white", position = "identity") + 
  geom_area(color = "white", position = "identity", size = 0.25) + 
  facet_geo(~ABB, grid = "us_state_grid2", scales = "free") + 
  scale_fill_manual(values = gcolors[c(2, 3, 7)])+ 
  scale_alpha_manual(values = c(0.8, 0.9, 0.5)) + 
  scale_x_continuous(breaks = NULL, labels = ~substr(., 3, 4)) +
  labs(
      title = title
    , x = NULL
    , y = NULL
  ) + 
  theme_minimal() + 
  theme(
    legend.position = "top"
    , panel.grid.major.x = element_blank()
    , panel.grid.minor.x = element_blank()
    , panel.grid.minor.y = element_blank()
  )
  
}

RRI_statefacet("all")
RRI_statefacet(1)
RRI_statefacet(2)
RRI_statefacet(3)
RRI_statefacet(4)

```



#### `RRI < 1`

All includes all rows (includes `RACE` of `r paste(admin$lev_RACE[-c(2:3)])` and `OFFGENERAL` of `r paste(admin$lev_OFFGENERAL[-c(1:4)])`)

```{r}
#| label: SC-RRI-RRILESS1
n    <- nrow(dfOR)
n_NA <- nrow(filter(dfOR, is.na(RRI)))
n_l1 <- nrow(dfOR_l1)
n_l1_cl10  <- dfOR_l1 %>% filter(REVCNT <  10) %>% nrow()
n_l1_cl25  <- dfOR_l1 %>% filter(REVCNT <  25) %>% nrow()
n_l1_cl50  <- dfOR_l1 %>% filter(REVCNT <  50) %>% nrow()
n_l1_cl100 <- dfOR_l1 %>% filter(REVCNT < 100) %>% nrow()
n_l1_pl.05 <- dfOR_l1 %>% filter(PROP_OF_TOT_REVCNT <  0.05) %>% nrow()
n_l1_pl.01 <- dfOR_l1 %>% filter(PROP_OF_TOT_REVCNT <  0.01) %>% nrow()
n_l1_r2    <- dfOR_l1 %>% filter(RACE == admin$lev_RACE[2]) %>% nrow()
n_l1_r3    <- dfOR_l1 %>% filter(RACE == admin$lev_RACE[3]) %>% nrow()
n_l1_r4    <- dfOR_l1 %>% filter(RACE == admin$lev_RACE[4]) %>% nrow()
n_l1_o1    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[1]) %>% nrow()
n_l1_o2    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[2]) %>% nrow()
n_l1_o3    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[3]) %>% nrow()
n_l1_o4    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[4]) %>% nrow()
n_l1_o5    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[5]) %>% nrow()
n_l1_o6    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[6]) %>% nrow()


fn    <- nrow(dfOR_rri)
fn_NA <- nrow(filter(dfOR_rri, is.na(RRI)))
fn_l1 <- nrow(dfOR_rri_1l)
fn_l1_cl10  <- dfOR_rri_1l %>% filter(REVCNT <  10) %>% nrow()
fn_l1_cl25  <- dfOR_rri_1l %>% filter(REVCNT <  25) %>% nrow()
fn_l1_cl50  <- dfOR_rri_1l %>% filter(REVCNT <  50) %>% nrow()
fn_l1_cl100 <- dfOR_rri_1l %>% filter(REVCNT < 100) %>% nrow()
fn_l1_pl.05 <- dfOR_rri_1l %>% filter(PROP_OF_TOT_REVCNT <  0.05) %>% nrow()
fn_l1_pl.01 <- dfOR_rri_1l %>% filter(PROP_OF_TOT_REVCNT <  0.01) %>% nrow()
fn_l1_r2    <- dfOR_rri_1l %>% filter(RACE == admin$lev_RACE[2]) %>% nrow()
fn_l1_r3    <- dfOR_rri_1l %>% filter(RACE == admin$lev_RACE[3]) %>% nrow()
fn_l1_o1    <- dfOR_rri_1l %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[1]) %>% nrow()
fn_l1_o2    <- dfOR_rri_1l %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[2]) %>% nrow()
fn_l1_o3    <- dfOR_rri_1l %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[3]) %>% nrow()
fn_l1_o4    <- dfOR_rri_1l %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[4]) %>% nrow()

```


::: {style="line-height: 1em;"}

| Description                       | All<br>Count| <br>Percent       | Filtered<br>Count | <br> Percent      |
|:-----------------------              |-------:     |:----              |-------:           |:----              |
| **Overall:**                       |             |                   |                   |                   |
| &emsp;Count              | `r n`       |                   | `r fn`            |                   |
| &emsp;Count where RRI = NA  | `r n_NA`    |`r percent(n_NA/n)`| `r fn_NA`         |`r percent(fn_NA/fn)`|
| &emsp;Count where RRI < 1| `r n_l1`    |`r percent(n_l1/n)`| `r fn_l1`         |`r percent(fn_l1/fn)`|
|
| **When RRI < 1:**         |             |                   |                   |                   |
| &emsp;Count where REVCNT < 10|`r n_l1_cl10`|`r percent(n_l1_cl10/n_l1)`|`r fn_l1_cl10`|`r percent(fn_l1_cl10/fn_l1)`|
| &emsp;Count where REVCNT < 25|`r n_l1_cl25`|`r percent(n_l1_cl25/n_l1)`|`r fn_l1_cl25`|`r percent(fn_l1_cl25/fn_l1)`|
| &emsp;Count where REVCNT < 50|`r n_l1_cl50`|`r percent(n_l1_cl50/n_l1)`|`r fn_l1_cl50`|`r percent(fn_l1_cl50/fn_l1)`|
| &emsp;Count where REVCNT < 100|`r n_l1_cl100`|`r percent(n_l1_cl100/n_l1)`|`r fn_l1_cl100`|`r percent(fn_l1_cl100/fn_l1)`|
| &emsp;Count where REVCNT/TOTAL_REVCNT[^fttotrevcnt] < 1%  |`r n_l1_pl.01`|`r percent(n_l1_pl.01/n_l1)`|`r fn_l1_pl.01`|`r percent(fn_l1_pl.01/fn_l1)`|
| &emsp;Count where REVCNT/TOTAL_REVCNT < 5% |`r n_l1_pl.05`|`r percent(n_l1_pl.05/n_l1)`|`r fn_l1_pl.05`|`r percent(fn_l1_pl.05/fn_l1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[2]` |`r n_l1_r2`|`r percent(n_l1_r2/n_l1)`|`r fn_l1_r2`|`r percent(fn_l1_r2/fn_l1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[3]` |`r n_l1_r3`|`r percent(n_l1_r3/n_l1)`|`r fn_l1_r3`|`r percent(fn_l1_r3/fn_l1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[4]` |`r n_l1_r4`|`r percent(n_l1_r4/n_l1)`| | |
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[1]` |`r n_l1_o1`|`r percent(n_l1_o1/n_l1)`|`r fn_l1_o1`|`r percent(fn_l1_o1/fn_l1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[2]` |`r n_l1_o2`|`r percent(n_l1_o2/n_l1)`|`r fn_l1_o2`|`r percent(fn_l1_o2/fn_l1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[3]` |`r n_l1_o3`|`r percent(n_l1_o3/n_l1)`|`r fn_l1_o3`|`r percent(fn_l1_o3/fn_l1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[4]` |`r n_l1_o4`|`r percent(n_l1_o4/n_l1)`|`r fn_l1_o4`|`r percent(fn_l1_o4/fn_l1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[5]` |`r n_l1_o5`|`r percent(n_l1_o5/n_l1)`| | |
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[6]` |`r n_l1_o6`|`r percent(n_l1_o6/n_l1)`| | |

:::
<!-- end STYLE FOR TABLE -->

[^fttotrevcnt]: `TOTAL_REVCNT` is the total revocation count for a specific state and year, this sums the revocations across the `RACE` and `OFFGENERAL` categories

```{r}
#| label: SC-RRI-RRILESS1-rmtableitems
rm(n, fn)
rm(list = ls(pattern = "^fn_"))
rm(list = ls(pattern = "^n_"))
```

```{r}
#| label: SC--RRI-RRILESS1-histogramall
#| fig.height: 3
#| fig.width: 12
dfOR_rri %>% 
  drop_na(RRI) %>% 
  ggplot(aes(x = RRI)) + 
  geom_histogram(bins = 100, fill = "grey80", color = "grey35") + 
  geom_vline(xintercept = 1, color = "red", alpha = 0.5) + 
  labs(
      title = "Histogram of RRI values for Filtered Data"
    , subtitle = "Vertical red line indicates RRI = 1"
  ) + 
  theme_bw() + 
  theme(plot.subtitle = element_text(color = "red"))
```

```{r}
#| label: SC-RRI-RRILESS1-histogramcrosssection
#| fig.height: 6
#| fig.width: 12
dfOR_rri %>% 
  drop_na(RRI) %>% 
  ggplot(aes(x = RRI)) + 
  geom_histogram(bins = 50, fill = "grey80", color = "grey35") + 
  geom_vline(xintercept = 1, color = "red", alpha = 0.5) + 
  facet_wrap(RACE~OFFGENERAL, scales = "free", nrow = 2) + 
  labs(
      title = "Histogram of RRI values by RACE/OFFGENERAL for Filtered Data"
    , subtitle = "Vertical red line indicates RRI = 1"
  ) + 
  theme_bw() + 
  theme(plot.subtitle = element_text(color = "red"))
```

```{r}
#| label: SC-RRI-RRILESS1-scatterplota
#| fig.height: 7
#| fig.width: 12
dfOR_rri %>% 
  drop_na(RRI) %>% 
  mutate(REVCNT_less_10 = ifelse(REVCNT < 10, TRUE, FALSE)) %>% 
  ggplot(aes(x = RRI, y = PROP_OF_TOT_REVCNT, color = REVCNT_less_10)) + 
  geom_vline(xintercept = 1, linetype = "dashed") + 
  scale_y_continuous(name = "REVCNT/TOTAL_REVCNT\n(Cross-Section Count / Total Count for State/Year)", labels = scales::percent) + 
  geom_point(alpha = 0.5) + 
  facet_wrap(RACE~OFFGENERAL, scales = "free", nrow = 2) + 
  labs(
    title = "Scatter Plot of PROP_OF_TOT_REVCNT by RRI, by cross-section for Filtered Data"
    , subtitle = "Vertical dashed line indicates RRI = 1"
  ) + 
  theme_bw() + 
  theme(legend.position = "top")
```

```{r}
#| label: SC-RRI-RRILESS1-scatterplotb
#| fig.height: 7
#| fig.width: 12
dfOR_rri %>% 
  filter(RRI < 1) %>% 
  mutate(REVCNT_less_10 = ifelse(REVCNT < 10, TRUE, FALSE)) %>% 
  ggplot(aes(x = RRI, y = PROP_OF_TOT_REVCNT, color = REVCNT_less_10)) + 
  geom_vline(xintercept = 1, linetype = "dashed") + 
  scale_y_continuous(name = "REVCNT/TOTAL_REVCNT\n(Cross-Section Count / Total Count for State/Year)", labels = scales::percent) + 
  geom_point(alpha = 0.5) + 
  facet_wrap(RACE~OFFGENERAL, scales = "free", nrow = 2) + 
  labs(
    title = "Scatter Plot of PROP_OF_TOT_REVCNT by RRI, by cross-section for Filtered Data where RRI < 1"
    , subtitle = "Vertical dashed line indicates RRI = 1"
  ) + 
  theme_bw() + 
  theme(legend.position = "top")
```

#### Tables where `RRI < 1` 

##### All: `RRI < 1` & `REVCNT > 100`: 

- four states (Hawaii, Illinois, New York, and Texas) 
- `RACE` = Hispanic and  `RACE` = Other (which will not be shown in dashboard) 

```{r}
#| label: SC-RRI-TABLES-one
dfOR_l1 %>%
  filter(REVCNT > 100) %>%
  kable(caption = "Instances where RRI < 1 AND REVCNT > 100")
```


##### All: `RRI < 1` & `REVCNT/TOTAL_REVCNT > 5%`: 

- three states (Hawaii, Nevada, and Texas) 
- Nevada and Texas instances are all for `RACE` = Hispanic 
- Hawaii instances are all for `RACE` = Other,  which will not be shown in dashboard 

```{r}
#| label: SC-RRI-TABLES-two
dfOR_l1 %>%
  filter(PROP_OF_TOT_REVCNT > 0.05) %>%
  kable(caption = "Instances where RRI < 1 AND REVCNT/TOTAL_REVCNT > 5%")
```


##### Filtered: `RRI < 1` & `RACE == Black`

- only 5 instances 
- REVCNT = 1 or 2 in all instances 

```{r}
#| label: SC-RRI-TABLES-three
dfOR_rri_1l %>% 
  filter(RACE == admin$lev_RACE[2], OFFGENERAL %in% admin$lev_OFFGENERAL[1:4]) %>% 
  kable(caption = "Instances where RRI < 1 AND RACE = Black AND OFFGENERAL != Other/missing")
```

:::
<!-- end {.panel tabset} SC-RRI --> 


:::
<!-- end {.panel-tabset} SC-->


## Annual Parole Survey

APS data is only available through 2018, so 2019 year is removed.  

```{r}
#| label: APS
rm(list = setdiff(ls(), c("denom_SC", "denom_APS", "gcolors", "admin", "calc")))
dfOR <- denom_APS$OR %>% 
  select(ABB, RPTYEAR, OFFGENERAL, RACE, REVCNT, POPEST, RATE, RATE_1K, RRI) %>% 
  left_join(., select(denom_SC$t, ABB, RPTYEAR, TOTAL_REVCNT = REVCNT), by = c("ABB", "RPTYEAR")) %>% 
  mutate(PROP_OF_TOT_REVCNT = REVCNT/TOTAL_REVCNT) %>% 
  filter(RPTYEAR < 2019)

dfR <- denom_APS$R %>% 
  select(ABB, RPTYEAR, RACE, REVCNT, POPEST, RATE, RATE_1K, RRI) %>% 
  left_join(., select(denom_SC$t, ABB, RPTYEAR, TOTAL_REVCNT = REVCNT), by = c("ABB", "RPTYEAR")) %>% 
  mutate(PROP_OF_TOT_REVCNT = REVCNT/TOTAL_REVCNT) %>% 
  filter(RPTYEAR < 2019)
```

<!-- start {.panel-tabset} APS-->
::: {.panel-tabset}


### Rate per 100

```{r}
#| label: APS-RATE
dfOR_rate <- dfOR %>% filter(RACE %in% admin$lev_RACE[1:4], OFFGENERAL %in% admin$lev_OFFGENERAL[1:4])
dfR_rate  <- dfR  %>% filter(RACE %in% admin$lev_RACE[1:4])
```

Filtered data used:  

- `RACE` equal to `r paste(admin$lev_RACE[1:4], collapse = ", ")`  
- `OFFGENERAL` equal to `r paste(admin$lev_OFFGENERAL[1:4], collapse = ", ")`


<!-- start {.panel-tabset} APS-RATE-->
::: {.panel-tabset}

#### Overview 

```{r}
#| label: APS-RATE-OVERVIEW-tabl3
dfOR_rate %>% 
  mutate(RATE_100 = RATE*100) %>% 
  select(RATE_100, OFFGENERAL, RACE) %>% 
  group_by(OFFGENERAL, RACE) %>% 
  skimr::skim_without_charts()
```


```{r}
#| label: APS-RATE-OVERVIEW-boxplot 
#| fig.width: 12
#| fig.height: 7
dfOR_rate %>% 
  filter(!(ABB == "DE" & OFFGENERAL == admin$lev_OFFGENERAL[4]) ) %>% 
  filter(!is.na(RATE)) %>% 
  ggplot(aes(y = OFFGENERAL, x = RATE*100)) + 
  geom_boxplot(alpha = 0.5, fill = "grey35", color = "grey35") + 
  facet_wrap(~RACE, ncol = 1) + 
  scale_x_continuous(limits = c(0, NA), expand = c(0.01, 0)) + 
  scale_y_discrete(limits = rev) + 
  labs(caption = glue("Rows with ABB = DE and OFFGENERAL = {admin$lev_OFFGENERAL[4]} are removed from chart because of skew")) + 
  theme_bw()
```

#### State Facet


```{r}
#| label: APS-RATE-STATEFACET
#| fig.width: 12
#| fig.height: 8
#| warning: FALSE
RATE_statefacet <- function(OFFGEN){
  
  if (OFFGEN %in% c(1:4)){
    
    plotdf <- dfOR_rate %>% 
        filter(OFFGENERAL == admin$lev_OFFGENERAL[OFFGEN], !is.na(RATE))
    title <- glue("Rate per 100 by Report Year (2015-2019) and RACE where OFFGENERAL = {admin$lev_OFFGENERAL[OFFGEN]}")
    
  } else if (toupper(OFFGEN) == "ALL"){
    
    plotdf <- dfR_rate %>% 
      filter(RACE %in% admin$lev_RACE[1:4], !is.na(RATE))
    title <- glue("Rate per 100 by Report Year (2015-2019) and RACE for any OFFGENERAL")
    
  }
  
  
plotdf %>% 
  ggplot(aes(x = RPTYEAR, y = RATE*100, color = RACE)) + 
  geom_line(size = 0.65) + 
  facet_geo(~ABB, grid = "us_state_grid2", scales = "free") + 
  scale_color_manual(values = gcolors[c(1, 2, 3, 4)])+ 
  scale_x_continuous(breaks = NULL, labels = ~substr(., 3, 4)) +
  labs(
      title = title
    , x = NULL
    , y = NULL
  ) + 
  theme_minimal() + 
  theme(
    legend.position = "top"
    , panel.grid.major.x = element_blank()
    , panel.grid.minor.x = element_blank()
    , panel.grid.minor.y = element_blank()
  )
  
}

RATE_statefacet("all")
RATE_statefacet(1)
RATE_statefacet(2)
RATE_statefacet(3)
RATE_statefacet(4)

```


#### `RATE > 1`

All includes all rows (includes `RACE` of `r paste(admin$lev_RACE[-c(2:4)])` and `OFFGENERAL` of `r paste(admin$lev_OFFGENERAL[-c(1:4)])`).  

There are multiple instances where the RATE is greater than one because the revocation count is greater than the population estimate.  The majority of the instances occurs when `RACE` is missing, which indicates that the NCRP data has higher amount of missing race information compared to the APS `UNKRACE`.  

```{r}
#| label: APS-RATE-RATEGREAT1
dfOR_g1      <- dfOR %>% filter(RATE > 1)
dfOR_rate_g1 <- dfOR_rate %>% filter(RATE > 1)

n    <- nrow(dfOR)
n_NA <- nrow(filter(dfOR, is.na(RRI)))
n_g1 <- nrow(dfOR_g1)


n_g1_cl10  <- dfOR_g1 %>% filter(REVCNT <  10) %>% nrow()
n_g1_cl25  <- dfOR_g1 %>% filter(REVCNT <  25) %>% nrow()
n_g1_cl50  <- dfOR_g1 %>% filter(REVCNT <  50) %>% nrow()
n_g1_cl100 <- dfOR_g1 %>% filter(REVCNT < 100) %>% nrow()
n_g1_pl.05 <- dfOR_g1 %>% filter(PROP_OF_TOT_REVCNT <  0.05) %>% nrow()
n_g1_pl.01 <- dfOR_g1 %>% filter(PROP_OF_TOT_REVCNT <  0.01) %>% nrow()
n_g1_r2    <- dfOR_g1 %>% filter(RACE == admin$lev_RACE[2]) %>% nrow()
n_g1_r3    <- dfOR_g1 %>% filter(RACE == admin$lev_RACE[3]) %>% nrow()
n_g1_r4    <- dfOR_g1 %>% filter(RACE == admin$lev_RACE[4]) %>% nrow()
n_g1_r5    <- dfOR_g1 %>% filter(RACE == admin$lev_RACE[5]) %>% nrow()
n_g1_o1    <- dfOR_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[1]) %>% nrow()
n_g1_o2    <- dfOR_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[2]) %>% nrow()
n_g1_o3    <- dfOR_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[3]) %>% nrow()
n_g1_o4    <- dfOR_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[4]) %>% nrow()
n_g1_o5    <- dfOR_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[5]) %>% nrow()
n_g1_o6    <- dfOR_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[6]) %>% nrow()


fn    <- nrow(dfOR_rate)
fn_NA <- nrow(filter(dfOR_rate, is.na(RATE)))
fn_g1 <- nrow(dfOR_rate_g1)


fn_g1_cl10  <- dfOR_rate_g1 %>% filter(REVCNT <  10) %>% nrow()
fn_g1_cl25  <- dfOR_rate_g1 %>% filter(REVCNT <  25) %>% nrow()
fn_g1_cl50  <- dfOR_rate_g1 %>% filter(REVCNT <  50) %>% nrow()
fn_g1_cl100 <- dfOR_rate_g1 %>% filter(REVCNT < 100) %>% nrow()
fn_g1_pl.05 <- dfOR_rate_g1 %>% filter(PROP_OF_TOT_REVCNT <  0.05) %>% nrow()
fn_g1_pl.01 <- dfOR_rate_g1 %>% filter(PROP_OF_TOT_REVCNT <  0.01) %>% nrow()
fn_g1_r2    <- dfOR_rate_g1 %>% filter(RACE == admin$lev_RACE[2]) %>% nrow()
fn_g1_r3    <- dfOR_rate_g1 %>% filter(RACE == admin$lev_RACE[3]) %>% nrow()
fn_g1_r4    <- dfOR_rate_g1 %>% filter(RACE == admin$lev_RACE[4]) %>% nrow()
fn_g1_o1    <- dfOR_rate_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[1]) %>% nrow()
fn_g1_o2    <- dfOR_rate_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[2]) %>% nrow()
fn_g1_o3    <- dfOR_rate_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[3]) %>% nrow()
fn_g1_o4    <- dfOR_rate_g1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[4]) %>% nrow()
```

::: {style="line-height: 1em;"}

| Description                       | All<br>Count| <br>Percent       | Filtered<br>Count | <br> Percent      |
|:-----------------------              |-------:     |:----              |-------:           |:----              |
| **Overall:**                       |             |                   |                   |                   |
| &emsp;Count              | `r n`       |                   | `r fn`            |                   |
| &emsp;Count where RATE = NA  | `r n_NA`    |`r percent(n_NA/n)`| `r fn_NA`         |`r percent(fn_NA/fn)`|
| &emsp;Count where RATE > 1| `r n_g1`    |`r percent(n_g1/n)`| `r fn_g1`         |`r percent(fn_g1/fn)`|
|
| **When RATE > 1:**         |             |                   |                   |                   |
| &emsp;Count where REVCNT < 10 |`r n_g1_cl10` | `r percent(n_g1_cl10/n_g1)`|`r fn_g1_cl10`|  `r percent(fn_g1_cl10/fn_g1)`|
| &emsp;Count where REVCNT < 100|`r n_g1_cl100`|`r percent(n_g1_cl100/n_g1)`|`r fn_g1_cl100`|`r percent(fn_g1_cl100/fn_g1)`|
| &emsp;Count where REVCNT/TOTAL_REVCNT < 1%|`r n_g1_pl.01`|`r percent(n_g1_pl.01/n_g1)`|`r fn_g1_pl.01`|`r percent(fn_g1_pl.01/fn_g1)`|
| &emsp;Count where REVCNT/TOTAL_REVCNT < 5%    |`r n_g1_pl.05`|`r percent(n_g1_pl.05/n_g1)`|`r fn_g1_pl.05`|`r percent(fn_g1_pl.05/fn_g1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[2]` |`r n_g1_r2`|`r percent(n_g1_r2/n_g1)`|`r fn_g1_r2`|`r percent(fn_g1_r2/fn_g1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[3]` |`r n_g1_r3`|`r percent(n_g1_r3/n_g1)`|`r fn_g1_r3`|`r percent(fn_g1_r3/fn_g1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[4]` |`r n_g1_r4`|`r percent(n_g1_r4/n_g1)`|`r fn_g1_r4`|`r percent(fn_g1_r4/fn_g1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[5]` |`r n_g1_r5`|`r percent(n_g1_r5/n_g1)`| | |
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[1]` |`r n_g1_o1`|`r percent(n_g1_o1/n_g1)`|`r fn_g1_o1`|`r percent(fn_g1_o1/fn_g1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[2]` |`r n_g1_o2`|`r percent(n_g1_o2/n_g1)`|`r fn_g1_o2`|`r percent(fn_g1_o2/fn_g1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[3]` |`r n_g1_o3`|`r percent(n_g1_o3/n_g1)`|`r fn_g1_o3`|`r percent(fn_g1_o3/fn_g1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[4]` |`r n_g1_o4`|`r percent(n_g1_o4/n_g1)`|`r fn_g1_o4`|`r percent(fn_g1_o4/fn_g1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[5]` |`r n_g1_o5`|`r percent(n_g1_o5/n_g1)`| | |
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[6]` |`r n_g1_o6`|`r percent(n_g1_o6/n_g1)`| | |

:::
<!-- end STYLE FOR TABLE -->


```{r}
#| label: APS-RATE-RATEGREAT1-rm
rm(n, fn)
rm(list = ls(pattern = "^fn_"))
rm(list = ls(pattern = "^n_"))
```


#### `RATE > 0.5`


```{r}
dfOR_rate %>% 
  filter(RATE >= 0.5) %>% 
  select(ABB, RPTYEAR, OFFGENERAL, RACE, REVCNT, POPEST, RATE, TOTAL_REVCNT, PROP_OF_TOT_REVCNT) %>% 
  arrange(desc(REVCNT)) %>% 
  kable()
```



:::
<!-- end {.panel-tabset} APS-RATE-->


### RRI

Filtered data used:  

- `RACE` equal to `r paste(admin$lev_RACE[2:3], collapse = ", ")`  
- `OFFGENERAL` equal to `r paste(admin$lev_OFFGENERAL[1:4], collapse = ", ")`

```{r}
#| label: APS-RRI
dfOR_rri    <- dfOR     %>% filter(RACE %in% admin$lev_RACE[2:3], OFFGENERAL %in% admin$lev_OFFGENERAL[1:4])
dfR_rri     <- dfR      %>% filter(RACE %in% admin$lev_RACE[2:3])
dfOR_rri_1l <- dfOR_rri %>% filter(RRI < 1)
dfOR_l1     <- dfOR     %>% filter(RRI < 1)
```


<!-- start {.panel-tabset} APS-RRI -->
::: {.panel-tabset} 


#### Overview 

```{r}
#| label: APS-RRI-OVERVIEW-table 
dfOR_rri %>% 
  select(RRI, OFFGENERAL, RACE) %>% 
  group_by(OFFGENERAL, RACE) %>% 
  skimr::skim_without_charts()
```

```{r}
#| label: APS-RRI-OVERVIEW-boxplot
#| fig.width: 12
#| fig.height: 4
dfOR_rri %>% 
  filter(!is.na(RRI)) %>% 
  ggplot(aes(y = OFFGENERAL, x = RRI)) + 
  geom_vline(xintercept = 1, alpha = 0.5, color = "red") + 
  geom_boxplot(alpha = 0.8, fill = "grey35", color = "grey35") + 
  facet_wrap(~RACE, ncol = 1) + 
  scale_x_continuous(limits = c(0, NA), expand = c(0.01, 0)) + 
  scale_y_discrete(limits = rev) + 
  theme_bw()
```


#### State Facet


```{r}
#| label: APS-RRI-STATEFACET
#| fig.width: 12
#| fig.height: 7.5
RRI_statefacet <- function(OFFGEN){
  
  if (OFFGEN %in% c(1:4)){
    
    plotdf <- dfOR_rri %>% 
        filter(OFFGENERAL == admin$lev_OFFGENERAL[OFFGEN], !is.na(RRI))
    wrg_o <- expand.grid(ABB = unique(plotdf$ABB), RPTYEAR = c(2015:2019)) %>% 
      mutate(RACE = "White", RRI = 1)
    title <- glue("RRI by Report Year (2015-2019) and RACE where OFFGENERAL = {admin$lev_OFFGENERAL[OFFGEN]}")
    
    
  } else if (toupper(OFFGEN) == "ALL"){
    
    plotdf <- dfR_rri %>% 
      filter(RACE %in% admin$lev_RACE[2:3], !is.na(RRI))
    wrg_o <- expand.grid(ABB = unique(plotdf$ABB), RPTYEAR = c(2015:2019)) %>% 
      mutate(RACE = "White", RRI = 1)
    title <- glue("RRI by Report Year (2015-2019) and RACE for any OFFGENERAL")
    
  }


plotdf %>% 
  full_join(., wrg_o, by = c("ABB", "RPTYEAR", "RACE", "RRI")) %>% 
  ggplot(aes(x = RPTYEAR, y = RRI, fill = RACE, alpha = RACE)) + 
  #geom_col(width = 1, alpha = 0.8, color = "white", position = "identity") + 
  geom_area(color = "white", position = "identity", size = 0.25) + 
  facet_geo(~ABB, grid = "us_state_grid2", scales = "free") + 
  scale_fill_manual(values = gcolors[c(2, 3, 7)])+ 
  scale_alpha_manual(values = c(0.8, 0.9, 0.5)) + 
  scale_x_continuous(breaks = NULL, labels = ~substr(., 3, 4)) +
  labs(
      title = title
    , x = NULL
    , y = NULL
  ) + 
  theme_minimal() + 
  theme(
    legend.position = "top"
    , panel.grid.major.x = element_blank()
    , panel.grid.minor.x = element_blank()
    , panel.grid.minor.y = element_blank()
  )
  
}

RRI_statefacet("all")
RRI_statefacet(1)
RRI_statefacet(2)
RRI_statefacet(3)
RRI_statefacet(4)

```


#### `RRI < 1`

All includes all rows (includes `RACE` of `r paste(admin$lev_RACE[-c(2:3)])` and `OFFGENERAL` of `r paste(admin$lev_OFFGENERAL[-c(1:4)])`)

```{r}
#| label: APS-RRI-RRILESS1-tablevals 
n    <- nrow(dfOR)
n_NA <- nrow(filter(dfOR, is.na(RRI)))
n_l1 <- nrow(dfOR_l1)
n_l1_cl10  <- dfOR_l1 %>% filter(REVCNT <  10) %>% nrow()
n_l1_cl25  <- dfOR_l1 %>% filter(REVCNT <  25) %>% nrow()
n_l1_cl50  <- dfOR_l1 %>% filter(REVCNT <  50) %>% nrow()
n_l1_cl100 <- dfOR_l1 %>% filter(REVCNT < 100) %>% nrow()
n_l1_pl.05 <- dfOR_l1 %>% filter(PROP_OF_TOT_REVCNT <  0.05) %>% nrow()
n_l1_pl.01 <- dfOR_l1 %>% filter(PROP_OF_TOT_REVCNT <  0.01) %>% nrow()
n_l1_r2    <- dfOR_l1 %>% filter(RACE == admin$lev_RACE[2]) %>% nrow()
n_l1_r3    <- dfOR_l1 %>% filter(RACE == admin$lev_RACE[3]) %>% nrow()
n_l1_r4    <- dfOR_l1 %>% filter(RACE == admin$lev_RACE[4]) %>% nrow()
n_l1_o1    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[1]) %>% nrow()
n_l1_o2    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[2]) %>% nrow()
n_l1_o3    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[3]) %>% nrow()
n_l1_o4    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[4]) %>% nrow()
n_l1_o5    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[5]) %>% nrow()
n_l1_o6    <- dfOR_l1 %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[6]) %>% nrow()


fn    <- nrow(dfOR_rri)
fn_NA <- nrow(filter(dfOR_rri, is.na(RRI)))
fn_l1 <- nrow(dfOR_rri_1l)
fn_l1_cl10  <- dfOR_rri_1l %>% filter(REVCNT <  10) %>% nrow()
fn_l1_cl25  <- dfOR_rri_1l %>% filter(REVCNT <  25) %>% nrow()
fn_l1_cl50  <- dfOR_rri_1l %>% filter(REVCNT <  50) %>% nrow()
fn_l1_cl100 <- dfOR_rri_1l %>% filter(REVCNT < 100) %>% nrow()
fn_l1_pl.05 <- dfOR_rri_1l %>% filter(PROP_OF_TOT_REVCNT <  0.05) %>% nrow()
fn_l1_pl.01 <- dfOR_rri_1l %>% filter(PROP_OF_TOT_REVCNT <  0.01) %>% nrow()
fn_l1_r2    <- dfOR_rri_1l %>% filter(RACE == admin$lev_RACE[2]) %>% nrow()
fn_l1_r3    <- dfOR_rri_1l %>% filter(RACE == admin$lev_RACE[3]) %>% nrow()
fn_l1_o1    <- dfOR_rri_1l %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[1]) %>% nrow()
fn_l1_o2    <- dfOR_rri_1l %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[2]) %>% nrow()
fn_l1_o3    <- dfOR_rri_1l %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[3]) %>% nrow()
fn_l1_o4    <- dfOR_rri_1l %>% filter(OFFGENERAL == admin$lev_OFFGENERAL[4]) %>% nrow()

```

::: {style="line-height: 1em;"}

| Description                       | All<br>Count| <br>Percent       | Filtered<br>Count | <br> Percent      |
|:-----------------------              |-------:     |:----              |-------:           |:----              |
| **Overall:**                       |             |                   |                   |                   |
| &emsp;Count              | `r n`       |                   | `r fn`            |                   |
| &emsp;Count where RRI = NA  | `r n_NA`    |`r percent(n_NA/n)`| `r fn_NA`         |`r percent(fn_NA/fn)`|
| &emsp;Count where RRI < 1| `r n_l1`    |`r percent(n_l1/n)`| `r fn_l1`         |`r percent(fn_l1/fn)`|
|
| **When RRI < 1:**         |             |                   |                   |                   |
| &emsp;Count where REVCNT < 10|`r n_l1_cl10`|`r percent(n_l1_cl10/n_l1)`|`r fn_l1_cl10`|`r percent(fn_l1_cl10/fn_l1)`|
| &emsp;Count where REVCNT < 25|`r n_l1_cl25`|`r percent(n_l1_cl25/n_l1)`|`r fn_l1_cl25`|`r percent(fn_l1_cl25/fn_l1)`|
| &emsp;Count where REVCNT < 50|`r n_l1_cl50`|`r percent(n_l1_cl50/n_l1)`|`r fn_l1_cl50`|`r percent(fn_l1_cl50/fn_l1)`|
| &emsp;Count where REVCNT < 100|`r n_l1_cl100`|`r percent(n_l1_cl100/n_l1)`|`r fn_l1_cl100`|`r percent(fn_l1_cl100/fn_l1)`|
| &emsp;Count where REVCNT/TOTAL_REVCNT < 1%  |`r n_l1_pl.01`|`r percent(n_l1_pl.01/n_l1)`|`r fn_l1_pl.01`|`r percent(fn_l1_pl.01/fn_l1)`|
| &emsp;Count where REVCNT/TOTAL_REVCNT < 5% |`r n_l1_pl.05`|`r percent(n_l1_pl.05/n_l1)`|`r fn_l1_pl.05`|`r percent(fn_l1_pl.05/fn_l1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[2]` |`r n_l1_r2`|`r percent(n_l1_r2/n_l1)`|`r fn_l1_r2`|`r percent(fn_l1_r2/fn_l1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[3]` |`r n_l1_r3`|`r percent(n_l1_r3/n_l1)`|`r fn_l1_r3`|`r percent(fn_l1_r3/fn_l1)`|
| &emsp;Count where RACE = `r admin$lev_RACE[4]` |`r n_l1_r4`|`r percent(n_l1_r4/n_l1)`| | |
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[1]` |`r n_l1_o1`|`r percent(n_l1_o1/n_l1)`|`r fn_l1_o1`|`r percent(fn_l1_o1/fn_l1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[2]` |`r n_l1_o2`|`r percent(n_l1_o2/n_l1)`|`r fn_l1_o2`|`r percent(fn_l1_o2/fn_l1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[3]` |`r n_l1_o3`|`r percent(n_l1_o3/n_l1)`|`r fn_l1_o3`|`r percent(fn_l1_o3/fn_l1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[4]` |`r n_l1_o4`|`r percent(n_l1_o4/n_l1)`|`r fn_l1_o4`|`r percent(fn_l1_o4/fn_l1)`|
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[5]` |`r n_l1_o5`|`r percent(n_l1_o5/n_l1)`| | |
| &emsp;Count where OFFGENERAL = `r admin$lev_OFFGENERAL[6]` |`r n_l1_o6`|`r percent(n_l1_o6/n_l1)`| | |

:::
<!-- end STYLE FOR TABLE -->

```{r}
#| label: APS-RRI-RRILESS1-rm 
rm(n, fn)
rm(list = ls(pattern = "^fn_"))
rm(list = ls(pattern = "^n_"))
```


```{r}
#| label: APS-RRI-RRILESS1-histogram
#| fig.height: 3
#| fig.width: 10
dfOR_rri %>% 
  drop_na(RRI) %>% 
  ggplot(aes(x = RRI)) + 
  geom_histogram(bins = 100, fill = "grey80", color = "grey35") + 
  geom_vline(xintercept = 1, color = "red", alpha = 0.5) + 
  labs(
      title = "Histogram of RRI values for Filtered Data"
    , subtitle = "Vertical red line indicates RRI = 1"
  ) + 
  theme_bw() + 
  theme(plot.subtitle = element_text(color = "red"))
```

```{r}
#| label: APS-RRI-RRILESS1-histogramcrosssection
#| fig.height: 6
#| fig.width: 10
dfOR_rri %>% 
  drop_na(RRI) %>% 
  ggplot(aes(x = RRI)) + 
  geom_histogram(bins = 50, fill = "grey80", color = "grey35") + 
  geom_vline(xintercept = 1, color = "red", alpha = 0.5) + 
  facet_wrap(RACE~OFFGENERAL, scales = "free", nrow = 2) + 
  labs(
      title = "Histogram of RRI values by RACE/OFFGENERAL for Filtered Data"
    , subtitle = "Vertical red line indicates RRI = 1"
  ) + 
  theme_bw() + 
  theme(plot.subtitle = element_text(color = "red"))
```


```{r}
#| label: APS-RRI-RRILESS1-scatterplota
#| fig.height: 7
#| fig.width: 12
dfOR_rri %>% 
  drop_na(RRI) %>% 
  mutate(REVCNT_less_10 = ifelse(REVCNT < 10, TRUE, FALSE)) %>% 
  ggplot(aes(x = RRI, y = PROP_OF_TOT_REVCNT, color = REVCNT_less_10)) + 
  geom_vline(xintercept = 1, linetype = "dashed") + 
  scale_y_continuous(name = "REVCNT/TOTAL_REVCNT\n(Cross-Section Count / Total Count for State/Year)", labels = scales::percent) + 
  geom_point(alpha = 0.5) + 
  facet_wrap(RACE~OFFGENERAL, scales = "free", nrow = 2) + 
  labs(
    title = "Scatter Plot of PROP_OF_TOT_REVCNT by RRI, by cross-section for Filtered Data"
    , subtitle = "Vertical dashed line indicates RRI = 1"
  ) + 
  theme_bw() + 
  theme(legend.position = "top")
```

```{r}
#| label: APS-RRI-RRILESS1-scatterplotb
#| fig.height: 7
#| fig.width: 12
dfOR_rri %>% 
  filter(RRI < 1) %>% 
  mutate(REVCNT_less_10 = ifelse(REVCNT < 10, TRUE, FALSE)) %>% 
  ggplot(aes(x = RRI, y = PROP_OF_TOT_REVCNT, color = REVCNT_less_10)) + 
  geom_vline(xintercept = 1, linetype = "dashed") + 
  scale_y_continuous(name = "REVCNT/TOTAL_REVCNT\n(Cross-Section Count / Total Count for State/Year)", labels = scales::percent) + 
  geom_point(alpha = 0.5) + 
  facet_wrap(RACE~OFFGENERAL, scales = "free", nrow = 2) + 
  labs(
    title = "Scatter Plot of PROP_OF_TOT_REVCNT by RRI, by cross-section for Filtered Data where RRI < 1"
    , subtitle = "Vertical dashed line indicates RRI = 1"
  ) + 
  theme_bw() + 
  theme(legend.position = "top")
```


:::
<!-- start {.panel-tabset} APS-RRI -->

:::
<!-- end {.panel-tabset} APS-->

:::
<!-- end {.panel-tabset} ALLLLLL-->
