---
title: "RRI - Suppression"
format: 
  html: 
    embed-resources: true 
editor: source
editor_options: 
  chunk_output_type: console
execute: 
  echo: false 
  eval: TRUE
---

```{r}
#| include: false 

library(tidyverse)
```


```{r}
#| eval: false 

NCRP_A_REV_BJS <- readRDS("C:/Users/meichlersmith/The Council of State Governments/JC Research - Documents/50 State Revocations Project/MCLC Shiny App/data/analysis/NCRP_A_REV_BJS.RDS")


REV_BJS$OR |> filter(
  RACE == "White", 
  SUPPRESS == 1, 
  OFFGENERAL != "Other",
  OFFGENERAL != "missing", 
  ABB != "DC"
  )


REV_BJS$OR |> 
  filter(ABB == "ID", RPTYEAR == 2015, OFFGENERAL == "Drugs")

# non-white NOT suppressed, white is suppressed 

REV_BJS$OR |> 
  filter(
    !is.na(REVCNT), 
    SUPPRESS != 1, 
    WHITERATE != S_WHITERATE, 
    !OFFGENERAL %in% c("Other", "missing"), 
    ABB != "DC", 
    !RACE %in% c("Other", "missing")
)


# non-white is suppressed, white is suppressed 

REV_BJS$OR |> 
  filter(
    !is.na(REVCNT), 
    SUPPRESS == 1, 
    WHITERATE != S_WHITERATE, 
    !OFFGENERAL %in% c("Other", "missing"), 
    ABB != "DC", 
    !RACE %in% c("Other", "missing")
)


# non-white is suppressed, white is NOT suppressed 

REV_BJS$OR |> 
  filter(
    !is.na(REVCNT), 
    SUPPRESS == 1, 
    WHITERATE == S_WHITERATE, 
    !OFFGENERAL %in% c("Other", "missing"), 
    ABB != "DC", 
    !RACE %in% c("Other", "missing")
)

```

## Text for Infographics

```{r}
#| message: false 

box::use(../prep/box/infograph)
tables <- readRDS("../app/data/NCRP_RRI_tables.RDS")
```


| # | Options | Meaning | 
|:--|:------|:--------------------------------|
| 1 | - Admissions<br>- Population | NCRP data source (prison admissions or prison population) | 
| 2 | <br>- gt1<br>- lt1<br>- eq1 | rounded RRI is:<br>- greater than 1<br>- less than 1<br>- equal to 1 | 
| 3 | <br>- 0<br>- 1 | RRI is using suppression<br>- FALSE<br>- TRUE (one of the groups has a count <5) | 
| 4 | <br>- BJS<br>- CEN | denominator for RRI<br>- parole population, BJS data (disparities attributed to parole revocation)<br>- state population, census data (cumulative disparities across system) |  

```{r}
opts <- tidyr::crossing(whichNCRP = c("Admissions", "Population"), whichPOP = c("BJS", "CEN"))

 
pull_rri_tables <- function(whichNCRP, whichPOP){
  map(state.name, function(x){
    if (tables[[whichNCRP]][[whichPOP]][[x]]$INFOGRAPH$DATAAVAIL == 0){
      tibble()
    } else {
      tables[[whichNCRP]][[whichPOP]][[x]]$INFOGRAPH$DF
    }
  }
) |> bind_rows() |> 
  mutate(
    NCRP = whichNCRP, 
    POP  = whichPOP
  )
}


params_for_loop <- tidyr::expand_grid(
      NCRP = names(tables)[1:2]
    , STATE = state.name
    , POP = c("BJS", "CEN")
  ) |> 
  mutate(row = row_number())

rri_table <- map2(opts$whichNCRP, opts$whichPOP, pull_rri_tables) |>
  bind_rows() |>
  mutate(rS_RRI = ifelse(S_RRI != 0 & round(S_RRI, 1) == 0, 0.1, round(S_RRI, 1))) |> 
  rowwise() |> 
  mutate(titleTextType = infograph$title_text_type(NCRP, rS_RRI, SUPPRESS, POP)) |>
  ungroup() |> 
  left_join(params_for_loop, by = join_by("STATE", "NCRP", "POP")) |> 
  select(STATE, NCRP, POP, RACE, rS_RRI, titleTextType, row)



order_type <- crossing(
  x1 = c("Admissions", "Population"), 
  x2 = c("1gt1", "2lt1", "3eq1"), 
  x3 = c(0, 1), 
  x4 = c("BJS", "CEN")
) |> arrange(x1, x4, x2, x3) |> 
  rowwise() |> 
  mutate(type = paste(c(x1, str_sub(x2, 2, -1), x3, x4), collapse = "_")) |> 
  ungroup() |> 
  pull(type) 


rri_table |> 
  mutate(titleTextType = factor(titleTextType, order_type)) |> 
  count(titleTextType)


# titleTextType <- "Population_lt1_1_BJS"
# rri_table |> filter(titleTextType == !!titleTextType)  |> count(row) |> filter(n== 2)
# rri_table |> filter(titleTextType == !!titleTextType)  |> count(RACE)
# rri_table |> filter(titleTextType == !!titleTextType, rS_RRI >= 10)  
# rri_table |> filter(titleTextType == !!titleTextType) |> print(n=20)
  

print("Loop #'s to get at least 1 of all opts available: ")
 
c(6, 46, 8, 86, 106, 110, 108, 116, 38, 96, 168, 196, 48, 148, 9, 19, 5, 7, 105, 133, 185, 95, 23, 195, 147) |> 
  sort() |> unique() |> paste(collapse = ", ") |> 
 str_wrap(width = 90) |> 
  cat(sep = "\n")


```



