---
title: "SVII Demographic Calculations - `r params$state`"
editor: source
self-contained: true 
format: 
  html:
    page-layout: full
    echo: false 
params: 
  state: "New Jersey" 
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false 
state <- params$state
```


```{r}
#| message: false
#| warning: false 
library(tidyverse)
library(DT)
library(scales)
```


RRI's are calculated by looking at the rate for a given group (Black, AIAN, Hispanic) divided by the rate for a comparison group.

For race and ethnicity the comparison group is White.  For sex and gender, the comparison group is Female.  

$$
\texttt{rri}_{\text{metric, group}} = \frac{\texttt{rate}_{\text{metric, group}}}{\texttt{rate}_{\text{metric, White/Female}}} 
$$
Rates are calculated by taking the average value from 2022 and 2023 for a given group and dividing it by the comparison population.  

The comparison population for total prison admissions and total prison population is U.S. Census data for `r state`.  
The comparison population for probation and parole metrics is the BJS Probation and Parole in the United States report, which details probation and parole populations broken out by demographics for `r state`.  

**RRI Text in Bullet Points** 

- If `rri` > 1 then text is: `rri`X more likely ...   
- If `rri` < 1 then text is: ((1-`rri`)*100)% less likely ...   
- If `rri` = 1 then text is: as likely ... 

```{r}
svii_demo <- readRDS("./svii_demo.rds") |> 
  filter(state_name == state)
```


## Counts and Percent Values  

- `n` = `2022` + `2023` (combined value of 2022 and 2023 values) 
- `perc` = percent of `n` divided by the aggregate value for a given metric, rounded to the nearest percent; values from 0-100; **these values are displayed in the tables** 
  * Example for Total Prison Admissions 
  * Total Prison Admissions, Female, `n`: `r pull(filter(svii_demo, metric_abbr == "a total", group == "Female")[,"2022"], 1)` (Female, 2022) + `r pull(filter(svii_demo, metric_abbr == "a total", group == "Female")[,"2023"], 1)` (Female, 2023) = `r pull(filter(svii_demo, metric_abbr == "a total", group == "Female"), n)`  
  * Total Prison Admissions, Male, `n`: `r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Male")[,"2022"], 1))` (Male, 2022) + `r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Male")[,"2023"], 1))` (Male, 2023) = `r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Male"), n))`    
  * Total Prison Admissions, Female, `perc`: (`r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Female"), n))`/(`r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Female"), n))`+`r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Male"), n))`))*100 -> round to nearest integer = `r pull(filter(svii_demo, metric_abbr == "a total", group == "Female"), perc)`
- `cp` refers to the comparison population that is displayed in the table, values are Census, PPUS_Parole, and PPUS_Probation
  * for total admissions and total prison population, the comparison population is `r state` population data which comes from the [U.S. Census Population Estimate Project (PEP)](https://www.census.gov/programs-surveys/popest.html) 
  * for parole and probation metrics, the comparison population is the `r state`'s parole and probation population data which comes from the BJS report [Probation and Parole in the United States, 2023](https://www.ojp.gov/library/publications/probation-and-parole-united-states-2023) (Probation population data from Appendix Table 10, Parole population data from Appendix Table 13)
- `n_cp` is the count value for the comparison population for a given group (i.e. Probation Population, `r state`, Black People)  
- `perc_cp` = percent of `n_cp` divided by the aggregate value for a given comparison population; **these values are displayed in the top row of the tables**
  * Example for Census data
  * `r state` Population, Female, `n_cp`: `r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Female"), ncomp))`  
  * `r state` Population , Male, `n_cp`: `r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Male"), ncomp))`  
  * `r state` Population Female, `perc_cp`: (`r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Female"), ncomp))`/(`r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Female"), ncomp))`+`r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "Male"), ncomp))`))*100 -> round to nearest integer = `r pull(filter(svii_demo, metric_abbr == "a total", group == "Female"), compperc)`
  * values that round to 0 are displayed as "<1%" on the web tool 
- `perc_cp_unk` is the percent of the comparison population that is unknown for a given demographic breakdown; this is only listed in the BJS PPUS report.  If a given group category has a percent unknown of greater than 15%, RRI's are not calculated.  

## Rate and RRI Calculations 

$$
\texttt{rate}_{\text{metric, group}} = \frac{\texttt{n}_{\text{metric, group}}/2}{\texttt{n\_cp}_{\text{metric, group}}} \times 100,000
$$

- `rate` = rate per 100,000 when comparing the the average value to the comparison population; `n` is divided by 2 to get the average value for `2022` and `2023`
  * Example for Total Prison Admissions, AIAN 
  * Total Prison Admissions, AIAN, `n` = `r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "AIAN"), n))`  
  * AIAN population in `r state`, `n_cp` = `r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "AIAN"), ncomp))` 
  * Rate of AIAN Total Prison Admissions per 100,000, `rate`: ([`r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "AIAN"), n))`/2]/`r comma(pull(filter(svii_demo, metric_abbr == "a total", group == "AIAN"), ncomp))`) * 100,000 = `r round(pull(filter(svii_demo, metric_abbr == "a total", group == "AIAN"), rate), 0)`

$$
\texttt{rri}_{\text{metric, group}} = \frac{\texttt{rate}_{\text{metric, group}}}{\texttt{rate}_{\text{metric, White/Female}}} 
$$
  
- `rri` = divide the `rate` for a given group by the `rate` for the comparison group (for race and ethnicity, the comparison group is White and the sex or gender the comparison group is Female)
  * Example for Total Prison Admissions, AIAN 
  * AIAN, `rate` = `r round(pull(filter(svii_demo, metric_abbr == "a total", group == "AIAN"), rate), 0)`
  * Comparison group rate, `rate_cg`= `r round(pull(filter(svii_demo, metric_abbr == "a total", group == "White"), rate), 0)`
  * `rri` = `r round(pull(filter(svii_demo, metric_abbr == "a total", group == "AIAN"), rate), 0)`/`r round(pull(filter(svii_demo, metric_abbr == "a total", group == "White"), rate), 0)` --> rounded to 1 decimal = `r round(pull(filter(svii_demo, metric_abbr == "a total", group == "AIAN"), rri), 1)`
  
**RRI Text in Bullet Points** 

- If `rri` > 1 then text is: `rri`X more likely ...   
- If `rri` < 1 then text is: ((1-`rri`)*100)% less likely ...   
- If `rri` = 1 then text is: as likely ... 

## Table 

The table below shows all of the values.  Please note that the `rate` and `rate_cg` are shown rounded to the nearest decimal to make viewing easier.  Additionally, the `perc` and `perc_cp` values are rounded to the nearest percent, some of the the values are small enough to round to 0 - in these cases, the values shown on the web tool will be "<1%".  

AIAN: American Indian  
NHPI: Pacific Islander  

```{r}


svii_rri <- svii_demo |> 
  group_by(state_name, metric_abbr) |> 
  mutate(
    rate_compgroup = case_when(
      group_cat == "race_ethnicity" ~ rate[group == "White"], 
      group_cat == "sex_gender" ~ rate[group == "Female"]
    ), 
    .after = rate
  ) |> 
  ungroup() |> 
  select(
    metric = data, 
    group, 
    group_cat, 
    `2022`, 
    `2023`, 
    n, 
    perc, 
    cp = comparison_source, 
    n_cp = ncomp, 
    perc_cp = compperc, 
    perc_cp_unk = compunk, 
    rate, 
    rate_cg = rate_compgroup, 
    rri
  ) |> 
  filter(
    !is.na(n), 
    !group %in% c("Other", "Diverse", "Unknown r/e", "Unknown s/g")
  ) |> 
  arrange(metric)

# https://stackoverflow.com/questions/58526047/customizing-how-datatables-displays-missing-values-in-shiny
rowCallback <- c(
    "function(row, data){",
    "  for(var i=0; i<data.length; i++){",
    "    if(data[i] === null){",
    "      $('td:eq('+i+')', row).html('NA')",
    "        .css({'color': 'rgb(151,151,151)', 'font-style': 'italic'});",
    "    }",
    "  }",
    "}"  
  )

svii_rri |> 
  DT::datatable(
    rownames = FALSE, 
    options = list(
      initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'font-size': '80%'});",
        "}"
      ), 
      rowCallback = JS(rowCallback)
    )
  ) |> 
  DT::formatStyle(columns = c(1:ncol(svii_rri)), fontSize = '80%') |> 
  DT::formatRound(columns = c("rate", "rate_cg"), digits = 0) |> 
  DT::formatRound(columns = c("rri"), digits = 1) |> 
  DT::formatRound(columns = c("n", "2022", "2023", "n_cp"), digits = 0)



```

