---
title: "General Documentation: MCLC NCRP Revocations 2015-2019" 
description: "Last User: `r stringr::str_sub(getwd(), 10, stringr::str_locate(stringr::str_sub(getwd(), 10, -1), '/')[1]+10-2)`"
date: last-modified
date-format: "YYYY-MM-DD HH:mm:ss"
published-title: Last Modified
doi: "`r Sys.time()`"
doi-title: Last Ran
params: 
  NCRPLET: "N"
format: 
  html:
    page-layout: full
    fontsize: 1em
editor: source
self-contained: true
---

```{r, include=FALSE}
box::use(
    box/admin
  , box/calc
  , box/clean_SC
)
```



::: panel-tabset

## Data Sources

::: panel-tabset

### NCRP (Revocation Counts)


+:--------------+:--------------------------------------------------------------------------------------------------------+
| **Usage**     | Revocation Counts by state/year/race/offense general 
+---------------+---------------+
| **Source**    | [National Corrections Reporting Program 1991-2019 ICPSR 38048](https://www.icpsr.umich.edu/web/ICPSR/studies/38048) 
+---------------+---------------+
| **SharePoint**| [JC Research - Documents/CC/data/raw/NCRP](https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2FCC%2Fdata%2Fraw%2FNCRP&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98) |
+---------------+---------------+


- 2 options for data used: 
    * A: Admission individual records, `DS0002/38048-0002-Data.rda`
    * N: Year-end individual records, `DS0004/38048-0004-Data.rda`
- filter to only include `ADMTYPE` == "(2) Parole return/revocation" and `RPTYEAR` >= 2015
- recode `RACE` variable to shorter names 
- Count based on different cross sections 

### Census (Community Population)

::: {.panel-tabset}


#### ACS - PUMMS 


```{r}
#| echo: false 
link <- "https://www.census.gov/programs-surveys/acs/microdata/documentation.html"
```


+:--------------+:-------------------------------------------------------------------------+
| **Usage**     | Population Estimates by state/year/race, denominator to calculate rates  |
+---------------+--------------------------------------------------------------------------+
| **Source**    | [Census American Community Survey Public Use Microdata Sample](`r link`)  |
+---------------+--------------------------------------------------------------------------+
| **SharePoint**|  NA                                                                      |
+---------------+--------------------------------------------------------------------------+

```{r}
#| echo: false 
rm(link)
```


Public Use Microdata Sample (PUMS).  Data is pulled from PUMS API using the `{tidycensus}` package.  The data is pulled and saved on SharePoint.  



##### PUMMS --> NCRP 

-   filter data to be 18+
-   re-code Race/Ethnicity categories to match RACE NCRP categories
-   sum across categories
-   add state ids
-   use population estimates for 2015-2019 (population estimate for a specific year is used for calculating rates for that NCRP rates for that year)



##### Race/Ethnicity Re-code 

SC has `ORIGIN`(Ethnicity) and `RACE` that need to be fit into the NCRP `RACE` categories.


| PUMS variables | `RACE` Re-code | Description | 
|:---------------|:----------|:--------------|
| ` HISP %in% c("1", "01") & RAC1P  == "1"` | `r admin$lev_RACE[1]` | Not Hispanic and White alone | 
| `!HISP %in% c("1", "01") & RACBLK == "0"` | `r admin$lev_RACE[3]` | Hispanic, not Black  | 
| `RACBLK == 1`                             | `r admin$lev_RACE[2]` | Black alone, or in combination with any ethnicity | 
| Everything else                           | `r admin$lev_RACE[4]` | All others | 


#### ACS - B01001

```{r}
#| echo: false 
link <- "https://data.census.gov/cedsci/table?q=B01001%3A%20SEX%20BY%20AGE&tid=ACSDT5Y2020.B01001"
```


+:--------------+:-------------------------------------------------------------------------+
| **Usage**     | Population Estimates by state/year/race, denominator to calculate rates  |
+---------------+--------------------------------------------------------------------------+
| **Source**    | [American Community Survey - B01001 SEX BY AGE Tables](`r link`)         |
+---------------+--------------------------------------------------------------------------+
| **SharePoint**|  NA                                                                      |
+---------------+--------------------------------------------------------------------------+

```{r}
#| echo: false 
rm(link)
```


|Name | Table | Title | Source | 
|:---|:----- |:------------|:-----|
|Total   |B01001 |SEX BY AGE                                       | [data.census.gov](https://data.census.gov/cedsci/table?q=B01001&g=0100000US%240400000)  | 
|White   |B01001H|SEX BY AGE (WHITE ALONE, NOT HISPANIC OR LATINO) | [data.census.gov](https://data.census.gov/cedsci/table?q=B01001h&g=0100000US%240400000) | 
|Black_H |B01001B|SEX BY AGE (BLACK OR AFRICAN AMERICAN ALONE)     | [data.census.gov](https://data.census.gov/cedsci/table?q=B01001b&g=0100000US%240400000) | 
|Hispanic|B01001I|SEX BY AGE (HISPANIC OR LATINO)                  | [data.census.gov](https://data.census.gov/cedsci/table?q=B01001i&g=0100000US%240400000) | 


- different race breakdowns than NCRP 
- age groups for ACS include a group for 18-19, so can create value of 18+ by suming the 18-19 category with all higher age categories 


##### Race/Ethnicity 

ACS does NOT provide the B01001 table for Black, NOT Hispanic or Latino.  
This might not be the best data to use in calculating rates because:  

(1) the Black population will be over-counted in comparison to the population from NCRP,  the NCRP Black population is Black only, not Hispanic/Latino and the ACS population is Black, including people who are Hispanic/Latino
(2) Unable to calculate an accurate 'Other' category: 
$$
\begin{aligned}
H & = \text{included Hispanic/Latino} \\
\text{Total} & = \text{White} + \text{Black} + \text{Hispanic} + \text{Other} &\implies \text{Other} &= \text{Total} - \text{White} - \text{Black} - \text{Hispanic} \\
\text{Total} & \neq \text{White} + \text{Black}_H+ \text{Hispanic} + \text{Other} &\implies \text{Other} &\neq \text{Total} - \text{White} - \text{Black}_H - \text{Hispanic} \\
\end{aligned} 
$$


Using this data will: 

- Black: over-count population estimate --> rates/RRI lower 
- Other: under-count population estimate --> rates/RRI higher 
  * theoretically, Other could be 0 or negative number if Black_H is significantly higher than Black (large portion of Black_H includes people who would also be in Hispanic)



#### SC 

+:--------------+:--------------------------------------------------------------------------------------------------------+
| **Usage**     | Population Estimates by state/year/race, denominator to calculate rates  
+---------------+---------------+
| **Source**    | [Census State Population by Characteristics](https://www.census.gov/programs-surveys/popest/technical-documentation/research/evaluation-estimates/2020-evaluation-estimates/2010s-state-detail.html) 
+---------------+---------------+
| **SharePoint**| [JC Research - Documents/CC/data/raw/SC_EST](https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2FCC%2Fdata%2Fraw%2FSC%2DEST&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98) |
+---------------+---------------+


##### SC --> NCRP 

-   filter data to be 18+, combine sex, and combine ORIGIN
-   re-code RACE/ORIGIN categories to match RACE NCRP categories
-   sum across categories
-   add state ids
-   use population estimates for 2015-2019 (population estimate for a specific year is used for calculating rates for that NCRP rates for that year)

##### Race/Ethnicity Re-code 

SC has `ORIGIN`(Ethnicity) and `RACE` that need to be fit into the NCRP `RACE` categories.

| SC `ORIGIN`      | SC `RACE`                                            | NCRP `RACE` Original       | `RACE` Re-code | 
|:--------------   |:-----------------------                              |:-----------------          |:--------------|
| 1 (Not Hispanic) | 1 (White Alone)                                      | `r admin$NCRPlev_RACE()[1]`| `r admin$lev_RACE[1]` |
| 1 (Not Hispanic) | 2 (Black or African American Alone)                  | `r admin$NCRPlev_RACE()[2]`| `r admin$lev_RACE[2]` |
| 1 (Not Hispanic) | 3 (American Indian or Alaska Native Alone)           | `r admin$NCRPlev_RACE()[4]`| `r admin$lev_RACE[4]` |
| 1 (Not Hispanic) | 4 (Asian Alone)                                      | `r admin$NCRPlev_RACE()[4]`| `r admin$lev_RACE[4]` |
| 1 (Not Hispanic) | 5 (Native Hawaiian and Other Pacific Islander Alone) | `r admin$NCRPlev_RACE()[4]`| `r admin$lev_RACE[4]` |
| 1 (Not Hispanic) | 6 (Two or more races)                                | `r admin$NCRPlev_RACE()[4]`| `r admin$lev_RACE[4]` |
| 2 (Hispanic)     | 1 (White Alone)                                      | `r admin$NCRPlev_RACE()[3]`| `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 2 (Black or African American Alone)                  | `r admin$NCRPlev_RACE()[3]`| `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 3 (American Indian or Alaska Native Alone)           | `r admin$NCRPlev_RACE()[3]`| `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 4 (Asian Alone)                                      | `r admin$NCRPlev_RACE()[3]`| `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 5 (Native Hawaiian and Other Pacific Islander Alone) | `r admin$NCRPlev_RACE()[3]`| `r admin$lev_RACE[3]` |
| 2 (Hispanic)     | 6 (Two or more races)                                | `r admin$NCRPlev_RACE()[3]`| `r admin$lev_RACE[3]` |




:::
<!-- end census -->

### BJS (Parole Population)

::: {.panel-tabset}

#### BJS - APS


```{r}
#| echo: false 
bjslink     <- "https://bjs.ojp.gov/data-collection/annual-probation-survey-and-annual-parole-survey#documentation-0"
splink_par  <- "https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2FCC%2Fdata%2Fraw%2FBJS%2FAParS&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98"
splink_prob <- "https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2FCC%2Fdata%2Fraw%2FBJS%2FAProbS&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98"
```


+:--------------+:----------------------------------------------------------------------------------------------------------------+
| **Usage**     | Projection of population on parole or probation                                                                 |
+---------------+-----------------------------------------------------------------------------------------------------------------+
| **Source**    | - [BJS Annual Probation Survey and Annual Parole Survey -> Documentation -> Codebooks and datasets](`r bjslink`) 
|               | - Parole: [Annual Parole Survey series](https://www.icpsr.umich.edu/web/NACJD/series/328)                       
|               | - Probation: [Annual Probation Survey series](https://www.icpsr.umich.edu/web/NACJD/series/327)                  
+---------------+-----------------------------------------------------------------------------------------------------------------+
| **SharePoint**| - Parole: [JC Research - Documents/CC/data/raw/BJS/AParS](`r splink_par`)                                       |
|               | - Probation: [JC Research - Documents/CC/data/raw/BJS/AProbS](`r splink_prob`)                                  | 
+---------------+-----------------------------------------------------------------------------------------------------------------+


- only available to 2018
- released on a report year basis, have to combine
- **only use parole data** (because that's what matches the NCRP data) 
- use the following variables from APS
  * `STATE`: state abbreviation, can be used to create other state id columns 
  * Race variables: 
    * `WHITE`
    * `BLACK` 
    * `HISP` 
    * `UNKRACE` 
    * `TOTRACE` 
  * Note that `TOTRACE` == `TOTEND` (total at year end) in all instances for Parole/Probation 2013-2018
  * `RPTYEAR` year of survey (added variable during import)

##### Variables 

::: {.grid style="font-size: 0.9em;"} 

::: {.g-col-8}

| Variable | Description | 
|:--|:-------------------|
|`STATEID` | mix of usage, i.e. `1`, `(1) Alabama`, `(01) Alabama` |
|`TOTEN`   |total entries to parole/probation | 
|`ESTOTEN` | `TOTEN` value type, whether based on estimated/actual data by reporting agencies | 
|`TOTEX`   | total exits (discharges) from parole/probation |
|`ESTTOEX` | `TOTEX` value type, whether based on estimated/actual data by reporting agencies | 
|`TOTEND`  | parole/probation population end of year |
|`ESTOTEND`| `TOTEND` value type, whether based on estimated/actual data by reporting agencies | 

:Variables Directly from APS
  
::: 
<!-- end {.g-col-8} --> 

::: {.g-col-4}

| Variable | Description | 
|:--|:-------------------|
|`FIPS`   | created from `STATEID`, **use this variable to id state, consistent format**  |
|`RPTYEAR`| year of survey  | 
|`SOURCE` | rda file where data came from | 


:Variables Created at Import 
  
::: 
<!-- end {.g-col-4} --> 


::: 
<!-- end {.grid} --> 
  



##### Value Types (Estimation - `ES####`) Categories 

- \(1\) Estimated 
- \(2\) Actual 
- \(3\) Both estimate and actual from reporting entities 
- \(4\) BJC imputed data 

  
##### Race/Ethnicity Re-code (not used in projection! )


The parole/probation surveys are count based data (each row is a count, not an individual person).  Therefore there are multiple race **variables** that indicate counts, instead of a single race variable that has different values indicating the race/ethnicity of a person.  


| APS Variable| Description                                                | NCRP `RACE` Original      | `RACE` Re-code | 
|:-------     |:-----------------------------                              |:-----------------         |:--------------|
| `WHITE`     | 10a. White (not of Hispanic origin)                        |`r admin$NCRPlev_RACE()[1]`|`r admin$lev_RACE[1]`|
| `BLACK`     | 10b. Black or African American (not of Hispanic origin)    |`r admin$NCRPlev_RACE()[2]`|`r admin$lev_RACE[2]`|
| `HISP`      | 10c. Hispanic or Latino                                    |`r admin$NCRPlev_RACE()[3]`|`r admin$lev_RACE[3]`|
| `AMINALK`   | 10d. American Indian/Alaska Native (not of Hispanic origin)|`r admin$NCRPlev_RACE()[4]`|`r admin$lev_RACE[4]`|
| `ASIAN`     | 10e. Asian (not of Hispanic origin)                        |`r admin$NCRPlev_RACE()[4]`|`r admin$lev_RACE[4]`|
| `HAWPAC`    | 10f. Hawaiian/Pacific Islander (not of Hispanic origin)    |`r admin$NCRPlev_RACE()[4]`|`r admin$lev_RACE[4]`|
| `TWORACE`   | 10g. Two or more races (not of Hispanic origin)            |`r admin$NCRPlev_RACE()[4]`|`r admin$lev_RACE[4]`|
| `ADDRACE`   | 10h. Additional categories in your information system      |`r admin$NCRPlev_RACE()[4]`|`r admin$lev_RACE[4]`|
| `UNKRACE`   | 10i. Not known                                             | NA                        |`r admin$lev_RACE[5]`|
| `TOTRACE`   | Total (Sum of items 10a through 10i should equal item 4)   | NA                        | NA |

The re-code `r admin$lev_RACE[4]` category is calculated by subtracting certain categories from the total:  
`r admin$lev_RACE[4]` = `TOTRACE` - `WHITE` - `BLACK` - `HISP` - `UNKRACE` 

```{r}
#| echo: false 
rm(bjslink, splink_par, splink_prob)
```


#### BJS - PPUS 


```{r}
#| echo: false 
bjslink     <- "https://bjs.ojp.gov/library/publications/list?series_filter=Probation%20and%20Parole%20Populations"
splink_ppus <- "https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2FCC%2Fdata%2Fraw%2FBJS%2FPPUS&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98"
```


+:--------------+:----------------------------------------------------------------------------------------------------------------+
| **Usage**     | Projection of population on parole or probation                                                                 |
+---------------+-----------------------------------------------------------------------------------------------------------------+
| **Source**    | - [BJS: Probation and Parole Populations series](`r bjslink`)                                                   
|               | - [2020](https://bjs.ojp.gov/library/publications/probation-and-parole-united-states-2020)                      
|               | - [2019](https://bjs.ojp.gov/library/publications/probation-and-parole-united-states-2019)                      
|               | - [2017-2018](https://bjs.ojp.gov/library/publications/probation-and-parole-united-states-2017-2018)            
+---------------+-----------------------------------------------------------------------------------------------------------------+
| **SharePoint**| [JC Research - Documents/CC/data/raw/BJS/PPUS](`r splink_ppus`)                                                 |
+---------------+-----------------------------------------------------------------------------------------------------------------+


- for a specific year, go to Downloads > Data tables 
- report pdf and folder with tables (in csv form) are downloaded
- special import instructions for each year and probation/parole table in `ppus_table.csv` specify which table and columns to use for specific variables 
- THIS DOES NOT HAVE VALUES BROKEN OUT BY RACE --> CANNOT BE USED TO CALCULATE RATES (AND THUS CANNOT BE USED TO CALCULATED RRI)


##### Variables 

::: {.grid style="font-size: 0.9em;"} 

::: {.g-col-4}

| Variable | Description | 
|:--|:-------------------|
|`STATEID` | state name, includes footnote tags |
|`TOTEN`   | total entries to parole/probation | 
|`TOTEX`   | total exits (discharges) from parole/probation |
|`TOTEND`  | parole/probation population end of year |

:Variables Directly from PPUS Table
  
::: 
<!-- end {.g-col-4} --> 

::: {.g-col-8}

| Variable | Description | 
|:--|:-------------------|
|`FIPS`   | created from `STATEID`, **use this variable to id state, consistent format** |
|`RPTYEAR`| year of survey  | 
|`SOURCE` | table csv file where data came from | 
|`ESTOTEN` | `TOTEN` value type, whether based on estimated/actual data by reporting agencies  | 
|`ESTOTEX` | `TOTEX` value type, whether based on estimated/actual data by reporting agencies | 


:Variables Created at Import 
  
::: 
<!-- end {.g-col-8} --> 


::: 
<!-- end {.grid} --> 


##### Creating `ES###` Columns 

Tables are set up with 2 side by side columns, one for Reported and one for Estimated.  

**When reported is not missing:** use the value from the reported column and assign `(2) Actual` for the `ES####` variable  
**When reported is missing (`NA`):** use the value form the estimated column and assign `(1) Estimated` for the `ES####` variable 

*NOTE:* `ESTOTEND` is not created because within the tables available, there is only one column with data (it is not split into reported/estimated like the entries and exits) 
  


```{r}
#| echo: false 
rm(bjslink, splink_ppus)
```



::: 
<!--end {panel.tabset} BJS --> 


::: 
<!--end panel.tabset DATA SOURCES --> 


## Analytical File

`calc$combine_and_calcrates()` imports data, cleans, combines and calculates metrics.  Output is a list of 4 data sets: 


- `OR`:  Cross Section by STATE, RPTYEAR, OFFGENERAL, RACE (offense and race) 
- `O`: Cross Section by STATE, RPTYEAR, OFFGENERAL (offense) 
- `R`: Cross Section by STATE, RPTYEAR, RACE (race) 
- `t`: Cross Section by STATE, RPTYEAR (total)  


::: {style="line-height: 1em;"}

| Variable   |`OR`    |`O`     |`R`     |`t`     | Type  |  Description | 
|:-----      |:---    |:---    |:---    |:---    |:---   |:--------------------------|
|`STATE`     |&#10003;|&#10003;|&#10003;|&#10003;|factor | State name |
|`FIPS`      |&#10003;|&#10003;|&#10003;|&#10003;|factor | 2-character FIPS code | 
|`ABB`       |&#10003;|&#10003;|&#10003;|&#10003;|factor | 2-character USPS abbreviation | 
|`RPTYEAR`   |&#10003;|&#10003;|&#10003;|&#10003;|numeric| year data was reported, 2015-2019 | 
|`OFFGENERAL`|&#10003;|&#10003;|        |        |factor | Categorization of most serious sentenced offense, shorten names to: `r paste(admin$lev_OFFGENERAL, collapse = ", ")` | 
|`RACE`      |&#10003;|        |&#10003;|        |factor | Race/Ethnicity of inmate, shorten names to: `r paste(admin$lev_RACE, collapse = ", ")` | 
|`REVCNT`    |&#10003;|&#10003;|&#10003;|&#10003;|numeric| Count of revocations | 
|`POPEST`    |&#10003;|&#10003;|&#10003;|&#10003;|numeric| Population (estimate) based on `pop_denom` input | 
|`POPTYPE`   |&#10003;|&#10003;|&#10003;|&#10003;|character| Source of population data | 
|`RATE`      |&#10003;|&#10003;|&#10003;|&#10003;|numeric| Rate of revocation count per population, `REVCNT`/`POPEST` <br>for a specific `RACE`, `STATE`, `RPTYEAR`, `OFFGENERAL` cross section |
|`WHITERATE` |&#10003;|        |&#10003;|        |numeric| `REVCNT`/`POPEST` where `RACE` = white <br>for a specific `STATE`, `RPTYEAR`, `OFFGENERAL` cross section | 
| `RRI`      |&#10003;|        |&#10003;|        |numeric| Relative Rate Index, `RATE`/`WHITERATE`<br> for a specific `STATE`, `RPTYEAR`, `OFFGENERAL` cross section | 
|`RECENT_YR` |&#10003;|&#10003;|&#10003;|&#10003;|numeric| Most recent year where `POPEST` is available  | 


: Variable Included in Output Data and Variable Descriptions
::: 
<!--end STYLE for table --> 




## Metrics

::: grid
::: g-col-6
Values:\
$n$ revocation count\
$N$ population estimate\
$R$ rate\
$I$ Relative rate index
:::

<!--end {.g-col-6} -->

::: g-col-6
Sub-text:\
$s$ State\
$o$ offense general category\
$r$ race/ethnicity\
$y$ year
:::

<!--end {.g-col-6} -->
:::

<!-- end {.grid}-->

::: panel-tabset
### Revocation Counts, $n$

Count the individual level data from NCRP by specific metrics.

| DF      | Equation for `REVCNT`      | Meaning                                                                 |
|:---------------|:-----------------|:-------------------------------------|
| `cs_OR` | $n^{sy}_{or}$ | Revocation count by STATE, RPTYEAR, OFFGENERAL, RACE (offense and race) |
| `cs_O`  | $n^{sy}_{o}$  | Revocation count by STATE, RPTYEAR, OFFGENERAL (offense)                |
| `cs_R`  | $n^{sy}_{r}$  | Revocation count by STATE, RPTYEAR, RACE (race)                         |
| `cs_t`  | $n^{sy}$      | Revocation count by STATE, RPTYEAR (total)                              |

### Rate, $R$

Revocation counts for a specific cross section divided by the population estimate for that specific cross section. Population is available by state, year, and race/ethnicity.

| DF      | Equation for `RATE` | Meaning                                                     |
|:---------------|:-----------------|:-------------------------------------|
| `cs_OR` | $R^{sy}_{or} = \frac{n^{sy}_{or} }{N^{sy}_{r} }$ | Rate by STATE, RPTYEAR, OFFGENERAL, RACE (offense and race) |
| `cs_O`  | $R^{sy}_{o} = \frac{n^{sy}_{o} }{N^{sy} }$       | Rate by STATE, RPTYEAR, OFFGENERAL (offense)                |
| `cs_R`  | $R^{sy}_{r} = \frac{n^{sy}_{r} }{N^{sy}_{r} }$   | Rate by STATE, RPTYEAR, RACE (race)                         |
| `cs_t`  | $R^{sy} = \frac{n^{sy} }{N^{sy} }$               | Rate by STATE, RPTYEAR (total)                              |




### Relative Rate Index (RRI), $I$

Relative Rate Index is compare the $r = 1$ (White) to the other race/ethnicity groups.

*Note:* The RRI is calculated for all four race groups but will only be shown for $r = 2$ (Black) and $r = 3$ (Hispanic). When $r = 1$ (White) $\implies I = 1$. The last category, $r = 4$ (Other) is removed due to small counts and difficultly gather meaning from 'Other' category.

| DF      | Equation for `RRI` | Meaning                                                    |
|:---------------|:-----------------|:-------------------------------------|
| `cs_OR` | $I^{sy}_{or} = \frac{R^{sy}_{or} }{R^{sy}_{o1} }$ | RRI by STATE, RPTYEAR, OFFGENERAL, RACE (offense and race) |
| `cs_O`  | N/A                                               | N/A                                                        |
| `cs_R`  | $I^{sy}_{r} = \frac{R^{sy}_{r} }{R^{sy}_{1} }$    | RRI by STATE, RPTYEAR, RACE (race)                         |
| `cs_t`  | N/A                                               | N/A                                                        |
:::

<!-- end {.panel-tabset} METRICS-->

## Data Steps 

::: {.panel-tabset} 

### Box Modules 

|            |     |            |     |            |
|:----------:|:-:|:----------:|:-:|:----------:|
| admin.R<br>import.R| --> | calc_APS.R<br>clean_NCRP.R<br>clean_SC.R | --> | calc.R | 


### Community Population  

```{r}
params$NCRPLET
calc$combine_and_calcrates(pop_denom = "PUMS", NCRPLET = params$NCRPLET)
```


### Parole Population 

```{r}
params$NCRPLET
calc$combine_and_calcrates(pop_denom = "BJS", NCRPLET = params$NCRPLET)
```



:::
<!-- end {.panel-tabset} DATA STEPS -->

:::
<!-- end {.panel-tabset} -->
