---
title: "NCRP Mock-Up: Revocations 2015-2019" 
date: "Last updated/ran: `r Sys.time()`"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r, include = FALSE}
box::use(
    box/calc
  , box/admin
)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 10)

library(tidyverse)
library(highcharter)
```



```{r}
CNTRTDF <- calc$combine_and_calcrates()
```
```{r}
#copy over from Mari's code, make some edits for these plots 

###app/dataframes.R
default_fonts <- c("Graphik")

#gcolors <- c("#D25E2D", "#EDB799", "#C7E8F5", "#236ca7", "#D6C246", "#dcdcdc")

gcolors <- c("#666666", "#D25E2D", "#236ca7", "#D6C246", "#EDB799", "#C7E8F5")

### app/functions.R
# custom highcharts theme for plots
hc_theme_jc2 <- hc_theme(
    #colors = c("#D25E2D", "#EDB799", "#C7E8F5", "#236ca7", "#D6C246", "#dcdcdc")
    chart = list(style = list(fontFamily = default_fonts, color = "#666666"))
  , title = list(align = "left", style = list(fontFamily = default_fonts, fontSize = "24px")) 
  , subtitle = list(align = "left", style = list(fontFamily = default_fonts, fontSize = "16px"))
  , legend = list(align = "left", verticalAlign = "top")
  , xAxis = list(
        gridLineColor = "transparent"
      , lineColor = "transparent"
      , minorGridLineColor = "transparent"
      , tickColor = "transparent"
    )
  # , yAxis = list(
  #       labels = list(enabled = FALSE)
  #     , gridLineColor = "transparent"
  #     , lineColor = "transparent"
  #     , minorGridLineColor = "transparent"
  #     , tickColor = "transparent"
  #     )
  , plotOptions = list(
         line = list(marker = list(enabled = FALSE), lineWidth = 3)
      # , spline = list(marker = list(enabled = FALSE))
      #  area = list(marker = list(enabled = FALSE))
      # , areaspline = list(marker = list(enabled = FALSE))
      # , arearange = list(marker = list(enabled = FALSE))
       , bubble = list(maxSize = "10%")
      )
)


rri_wline_dark <-  list(list(
      value  = 1
    , color  = "#666666"
    , width  = 2
    , zIndex = 4
    , dashStyle = "Dash" #https://api.highcharts.com/class-reference/Highcharts#.DashStyleValue
    , label = list(
        text = "White (ref. group)"
      , rotation = 0
      , style = list(
          color = "#666666"
        , fontWeight = "bold"
        ) #end style list
    ) #end label list
  )) #end doublelist


rri_wline_lite <-  list(list(
      value  = 1
    , color  = "#666666"
    , width  = 2
    , zIndex = 4
    , dashStyle = "Dash" #https://api.highcharts.com/class-reference/Highcharts#.DashStyleValue
    , label = list(
        text = "White (ref. group)"
      , rotation = 0
      , style = list(
          color = "#666666"
        , fontWeight = "bold"
        ) #end style list
    ) #end label list
  )) #end doublelist



refgroup <- function(hc, col = "dark", dash = "Dash", width = 2, type = "line", lineColor = NA){
  
  thisColor <- case_when(
      col == "dark"  ~ "#666666"
    , col == "light" ~ "#dcdcdc"
    , TRUE           ~ col
  )
  
  #https://api.highcharts.com/class-reference/Highcharts#.DashStyleValue
  if (is.na(dash) | !dash %in% c('Dash', 'DashDot',  'Dot',  'LongDash',  'LongDashDot',  'LongDashDotDot',  'ShortDash',  'ShortDashDot',  'ShortDashDotDot', 'ShortDot',  'Solid')){
    thisDash <- "Dash"
    warning("Dash Style not available")
  } else {
    thisDash <- dash 
  }
  
  
  hc_add_series(
    hc
        , data = data.frame(x = 2015:2019, y = 1)
        , type = type
        , color = thisColor
        , dashStyle = thisDash  
        , name = "White (ref. group)"
        , marker = FALSE
        , lineWidth = width
        , lineColor = ifelse(is.na(lineColor), thisColor, lineColor)
)
}

```

# {.tabset} 

All examples are shown with CA.  

**UPDATES**

- General
  * make line widths larger (size = 3)
  * reference lines are kept same size as before (size = 2) 
  * remove markers 
- Rate by Population 
  * remove charts for rate per 1000 and rate per 1mil, just keep rate per 100k 
  * add text to point label: {val} per 100,000
- Relative Rate Index 
  * add 'x' to axis labels 
  * add text to point label: {RACE} is {val}x as likely as White 
  * update reference line label from "White (reference group) to "White (ref. group)"
  * Area 
    - add small (size = 1) white line on top of area charts to separate groups 
    - change reference line to reference area 

```{r}
ABB <- "CA"
VAR <- "REVCNT"
```

```{r}
fnc_highchart_ROline <- function(ABB, VAR){
  
  ptfmt <- case_when(
      VAR == "REVCNT"    ~ "{point.VAR:,.0f}" #0 decimal places 
    , VAR == "RATE_1K"   ~ "{point.VAR:,.2f} per 1,000" #2 decimal places 
    , VAR == "RATE_100K" ~ "{point.VAR:,.1f} per 100,000" #1 decimal place
    , VAR == "RATE_1MIL" ~ "{point.VAR:,.1f} per 1,000,000" #1 decimal place
    , VAR == "RRI"       ~ "{point.RACE} is {point.VAR:,.1f}x as likely as White" #1 decimal place
    )
  
  if (substr(VAR, 1, 3) == "RRI"){
    theseRE   <- admin$lev_RACE[1:3] #only include black and hispanic 
    theseCols <- gcolors[1:3]
  } else {
    theseRE <- admin$lev_RACE[1:4] #White, Black, Hispanic, Other 
    theseCols <- gcolors[1:4]
  }
  
  plotdata <-  CNTRTDF$OR %>% 
    filter(ABB == !!ABB) %>% 
    rename("VAR" = !!VAR) %>% 
    filter(RACE %in% theseRE) %>% 
    filter(!OFFGENERAL %in% admin$lev_OFFGENERAL[-c(1:4)])#REMOVE OTHER/MISSING OFFGENERAL 
    
  map(admin$lev_OFFGENERAL[1:4], function(OG){
    
    plotdata %>% 
      filter(OFFGENERAL == OG) %>% 
      hchart("line"
        , hcaes(x = RPTYEAR, y = VAR, group = RACE)
        , color = theseCols
        , tooltip = list(pointFormat = ptfmt)
      ) %>% 
      hc_title(text = OG) %>% 
      hc_yAxis(min = 0, max = max(plotdata$VAR, na.rm = TRUE), title = list(text = "")) %>% 
      hc_xAxis(title = list(text = "")) %>% 
      hc_add_theme(hc_theme_jc2)
  }) %>% 
  hw_grid(rowheight = 350, ncol = 4) %>% 
    htmltools::browsable()
  
}
```
## Revocation Counts 

```{r}
fnc_highchart_ROline("CA", "REVCNT")
```

#### Stats 

```{r}
CNTRTDF$OR$REVCNT |> summary()
CNTRTDF$OR |> ggplot(aes(x = REVCNT)) + 
  geom_histogram(color = "grey50", fill = "grey80", bins = 50) + 
  ggtitle("Histogram") + 
  theme_minimal()
```


## Rate by Population {.tabset} 



```{r}
fnc_highchart_ROline("CA", "RATE_100K")
```


$$
\begin{aligned}
&\text{Rate per } 100,000 = \frac{\text{Count}_i}{\text{Population}_i} \cdot 100,000 \\
&i  = \text{Race/Ethnicity Group}
\end{aligned}
$$

#### Stats

I think rate per 100,000 makes the most sense because the majority of the values are above 1 but the largest values aren't 'too' large.  

```{r}
CNTRTDF$OR$RATE_100K |> summary()
CNTRTDF$OR |> ggplot(aes(x = RATE_100K)) + 
  geom_histogram(color = "grey50", fill = "grey80", bins = 50) + 
  ggtitle("Histogram") + 
  theme_minimal()
CNTRTDF$OR |> ggplot(aes(x = RATE_100K)) + 
  stat_ecdf(geom = "step") + 
  ggtitle("Empirical Cumulative Distribution") + 
  geom_vline(xintercept = 1, color = "red", linetype = "dotted") + 
  annotate("text", x = 1, y = 1, label = "RATE = 1", hjust = -0.1, color = "red") +
  theme_minimal() 
```


## Relative Rate Index {.tabset}

Only includes `Black` and `Hispanic` categories 


### Line Chart 


```{r}
VAR <- "RRI"

  ptfmt <- "{point.RACE} is {point.VAR:,.1f}x as likely as White" #1 decimal place
  theseRE   <- admin$lev_RACE[2:3] #only include black and hispanic 
  theseCols <- gcolors[2:3]

  
  plotdata <-  CNTRTDF$OR %>% 
    filter(ABB == !!ABB) %>% 
    rename("VAR" = !!VAR) %>% 
    # filter(RACE %in% theseRE) %>% 
    filter(!OFFGENERAL %in% admin$lev_OFFGENERAL[-c(1:4)])#REMOVE OTHER/MISSING OFFGENERAL 
    
  map(admin$lev_OFFGENERAL[1:4], function(OG){
    
    bh <- plotdata %>% filter(OFFGENERAL == OG, RACE %in% theseRE)
    #should all == 1,, instead of just putting as 1, leave as is (will help check calcs are done right)
    w  <- plotdata %>% filter(OFFGENERAL == OG, RACE == admin$lev_RACE[1]) %>% select(x = RPTYEAR, y = VAR)
    
    hchart(bh, "line"
        , hcaes(x = RPTYEAR, y = VAR, group = RACE)
        , color = theseCols
        , tooltip = list(pointFormat = ptfmt)
      ) %>% 
      refgroup(col = "dark") %>% 
      hc_title(text = OG) %>% 
      hc_yAxis(
          min = 0
        , max = max(plotdata$VAR, na.rm = TRUE)
        , title = list(text = "")
        , labels  = list(format = "{text}x")
        ) %>% 
      hc_xAxis(title = list(text = "")) %>% 
      hc_add_theme(hc_theme_jc2)
  }) %>% 
  hw_grid(rowheight = 350, ncol = 4) %>% 
    htmltools::browsable()
  
  

```


 

### Area 


```{r}
VAR <- "RRI"

  ptfmt <- "{point.RACE} is {point.VAR:,.1f}x as likely as White" #1 decimal place
  theseRE   <- admin$lev_RACE[2:3] #only include black and hispanic 
  theseCols <- gcolors[2:3]

  
  plotdata <-  CNTRTDF$OR %>% 
    filter(ABB == !!ABB) %>% 
    rename("VAR" = !!VAR) %>% 
    filter(!OFFGENERAL %in% admin$lev_OFFGENERAL[-c(1:4)])#REMOVE OTHER/MISSING OFFGENERAL 
    
  map(admin$lev_OFFGENERAL[1:4], function(OG){
    
    bh <- plotdata %>% filter(OFFGENERAL == OG, RACE %in% theseRE)
    #should all == 1,, instead of just putting as 1, leave as is (will help check calcs are done right)
    w  <- plotdata %>% filter(OFFGENERAL == OG, RACE == admin$lev_RACE[1]) %>% select(x = RPTYEAR, y = VAR)
    
    hchart(bh, "area"
        , hcaes(x = RPTYEAR, y = VAR, group = RACE)
        , color = theseCols
        , tooltip = list(pointFormat = ptfmt)
        , marker = FALSE
        , lineColor = "white"
        , lineWidth = 1
      ) %>% 
      refgroup(col = "light", dash = "Solid", width = 1, type = "area", lineColor = "white") %>% 
      hc_title(text = OG) %>% 
      hc_yAxis(min = 0
               , max = max(plotdata$VAR, na.rm = TRUE)
               , title = list(text = "")
               , labels  = list(format = "{text}x")
      ) %>% 
      hc_xAxis(title = list(text = "")) %>% 
      hc_add_theme(hc_theme_jc2)
  }) %>% 
  hw_grid(rowheight = 350, ncol = 4) %>% 
    htmltools::browsable()
```


### Contrast Values 


Contrast values, found using [WebAIM Contrast Checker](https://webaim.org/resources/contrastchecker/).  


| Foreground/Background |Orange #D25E2D| Blue #236CA7| Light Orange #EDB799 | Light Blue #C7E8F5|   
|:----------            |---------:|-------:|---------:|---------:|
| #FFFFFF (white)       | 3.90     | 5.56   |  1.77    |  1.28    | 
| #DCDCDC (light grey)  | 2.84     | 4.05   |  1.29    |  1.06    | 
| #666666 (dark grey)   | 1.47     | 1.03   |  3.23    |  4.45    | 
| #000000 (black)       | 5.56     | 3.77   | 11.83    | 16.28    | 


| Level | Passing Contrast | 
|:---------------------------------|:----|
|WCAG Level AA Large text   | 3   |
|WCAG Level AA Graphical Objects/UI Components | 3   | 
|WCAG Level AA Normal text  | 4.5 | 
|WCAG Level AAA Large text  | 4.5 | 
|WCAG Level AAA Normal text | 7   | 


### Stats 

```{r}
CNTRTDF$OR |> filter(RACE %in% c("Black", "Hispanic")) |> 
  pull(RRI) |> summary()
CNTRTDF$OR |> filter(RACE %in% c("Black", "Hispanic")) |> 
  ggplot(aes(x = RRI)) + 
  geom_histogram(color = "grey50", fill = "grey80", bins = 50) + 
  ggtitle("Histogram") + 
  theme_minimal()
```
