---
title: "RRI Comparison BJS vs SC" 
description: "Last User: `r stringr::str_sub(getwd(), 10, stringr::str_locate(stringr::str_sub(getwd(), 10, -1), '/')[1]+10-2)`"
date: last-modified
date-format: "YYYY-MM-DD HH:mm:ss"
published-title: Last Modified
doi: "`r Sys.time()`"
doi-title: Last Ran
execute:
  echo: true
format: 
  html:
    page-layout: full
    fontsize: 0.9em
    fig-width: 12
    fig-height: 7
    code-fold: true 
editor: source
self-contained: true
editor_options: 
  chunk_output_type: console
---


<style>

.txt_h {
  text-align: center;
}


</style>

```{r}
#| label: setup
#| include: false  

library(tidyverse)
library(knitr)
library(kableExtra)

#https://stackoverflow.com/questions/66974669/collapse-rows-is-not-collapsed-and-updating-packages-does-not-fix
#devtools::install_github(repo="haozhu233/kableExtra", ref="a6af5c0") #to get collapse rows to work 

box::use(
    box/admin
)
```


## Notes 

The prefix `S_` indicates that the variables values has been suppressed if the `REVCNT` <5.  The `S_` version of a variable (e.g. `S_RRI`) will equal the original variable (`RRI`) when suppression did not occur.  The variable `SUPPRESS` is used as a flag, with 1 = suppression occurred and `S_REVCNT` = 5 instead of the original value.  

## Math Stuffs 


TLDR: The data with the largest proportion of White population to the Black or Hispanic population will have the larger RRI.  

::: grid
::: g-col-6
Values:  
$n$ revocation count  
$N$ population estimate  
$R$ rate  
$I$ Relative rate index
:::

<!--end {.g-col-6} -->

::: g-col-6
Sub-text:\
$r$ race/ethnicity  
$r = W$ white  
$BJS$ BJS data  
$SC$ SC data
:::

<!--end {.g-col-6} -->
:::

<!-- end {.grid}-->



$$
\begin{aligned}
I & = \frac{ R_r }{ R_W } = \frac{n_r / N_r }{n_W /N_W} = \frac{ n_r \cdot N_W}{N_r \cdot n_w} = \frac{n_r}{n_W} \cdot \frac{N_W}{N_r} \\[1em]
I^{BJS} & = \frac{n_r}{n_W} \cdot \frac{N^{BJS}_W}{N^{BJS}_r} \\[1em]
I^{SC} & = \frac{n_r}{n_W} \cdot \frac{N^{SC}_W}{N^{SC}_r} \\[1em] 
\end{aligned}
$$

$$
\begin{aligned}
I^{BJS} & > I^{SC} \\[1em]
\frac{n_r}{n_W} \cdot \frac{N^{BJS}_W}{N^{BJS}_r} & > \frac{n_r}{n_W} \cdot \frac{N^{SC}_W}{N^{SC}_r}  \\[1em]
 \frac{N^{BJS}_W}{N^{BJS}_r} & > \frac{N^{SC}_W}{N^{SC}_r} 
\end{aligned}
$$


$$
\begin{aligned}
p &= \frac{N_W}{N_r} \\[1em]
p^{BJS} &> p^{SC} \implies I^{BJS} > I^{SC}
\end{aligned}
$$




```{r}
REV_BJS <- readRDS(file.path(admin$sp_data, "NCRP_REV_APS.RDS"))
REV_SC  <- readRDS(file.path(admin$sp_data, "NCRP_REV_SC.RDS"))


part1 <- full_join(
    REV_BJS$R
  , REV_SC$R
  , by = c(admin$varcs("R", TRUE), "REVCNT", "SUPPRESS", "S_REVCNT")
  , suffix = c(".BJS", ".SC")
  ) %>% 
  select(STATE, RPTYEAR, RACE, REVCNT, SUPPRESS, S_REVCNT, contains("POPEST"), contains("S_RATE"), contains("S_RRI")) %>% 
  select(STATE, RPTYEAR, RACE, REVCNT, SUPPRESS, S_REVCNT, contains(".BJS"), contains(".SC")) %>% 
 mutate(BJS_gt_SC = ifelse(S_RRI.BJS > S_RRI.SC, 1, 0)) %>% 
  filter(RACE %in% admin$lev_RACE[1:3]) #%>% 

part2 <- part1 %>% 
  filter(RACE == "White") %>% 
  select(STATE, RPTYEAR, WPOPEST.BJS = POPEST.BJS, WPOPEST.SC = POPEST.SC)


S_comp_R <- full_join(part1, part2, by = c("STATE", "RPTYEAR")) %>% 
  group_by(STATE, RPTYEAR) %>% 
  mutate(p.BJS = WPOPEST.BJS/POPEST.BJS, .after = POPEST.BJS) %>% 
  mutate(p.SC  = WPOPEST.SC /POPEST.SC,  .after = POPEST.SC) %>% 
  ungroup() %>% 
  mutate(
      RRI_diff  =   S_RRI.SC -   S_RRI.BJS
    , p_diff = p.SC - p.BJS
  )
rm(part1, part2)


part1 <- full_join(
    REV_BJS$OR
  , REV_SC$OR
  , by = c(admin$varcs("OR", TRUE), "REVCNT", "SUPPRESS", "S_REVCNT")
  , suffix = c(".BJS", ".SC")
  ) %>% 
  select(STATE, RPTYEAR, OFFGENERAL, RACE, REVCNT, SUPPRESS, S_REVCNT, contains("POPEST"), contains("S_RATE"), contains("S_RRI")) %>% 
  select(STATE, RPTYEAR, OFFGENERAL, RACE, REVCNT, SUPPRESS, S_REVCNT, contains(".BJS"), contains(".SC")) %>% 
 mutate(BJS_gt_SC = ifelse(S_RRI.BJS > S_RRI.SC, 1, 0)) %>% 
  filter(RACE %in% admin$lev_RACE[1:3]) 

part2 <- part1 %>% 
  filter(RACE == "White") %>% 
  select(STATE, RPTYEAR, OFFGENERAL, WPOPEST.BJS = POPEST.BJS, WPOPEST.SC = POPEST.SC)


S_comp_OR <- full_join(part1, part2, by = c("STATE", "RPTYEAR", "OFFGENERAL")) %>% 
  group_by(STATE, RPTYEAR, OFFGENERAL) %>% 
  mutate(p.BJS = WPOPEST.BJS/POPEST.BJS, .after = POPEST.BJS) %>% 
  mutate(p.SC  = WPOPEST.SC /POPEST.SC,  .after = POPEST.SC) %>% 
  ungroup() %>% 
  mutate(
      RRI_diff  =   S_RRI.SC -  S_RRI.BJS
    , p_diff = p.SC - p.BJS
  )
rm(part1, part2)


```


## All OFFGENEARL Categories 

```{r}

S_comp_R %>% 
  filter(RACE != "White") %>% 
  drop_na(RRI_diff, p_diff) %>% 
  ggplot() + 
  annotate("rect"
           , xmin = min(S_comp_R$RRI_diff, na.rm = T)
           , xmax = 0
           , ymin = min(S_comp_R$p_diff, na.rm = T)
           , ymax = 0
           , fill = "grey80"
           , alpha = 0.5
          ) + 
  geom_point(aes(x = RRI_diff, y = p_diff, shape = RACE, color = as.character(BJS_gt_SC)), alpha = 0.5) +
  labs(
    title = "Comparing Differences in S_RRI and pPOP for Black/Hispanic (Any OFFGENEARL category) - INFOGRAPHICS"
    , subtitle = "pPOPEST = WPOPEST (White Population) / POPEST (White, Black, or Hispanic)\nWhite is removed from Plot since S_RRI = 1 so all S_RRI difference = 0\n Grey box indicates where BJS RRI is larger and BJS p is larger"
    , x = "S_RRI difference (S_RRI.SC - S_RRI.BJS)"
    , y = "pPOPESTP Difference (pPOPESTP.SC - pPOPESTP.BJS)"
  ) + 
  scale_color_discrete(name = "S_RRI.BJS > S_RRI.SC") + 
  theme_minimal()
```


```{r}
DT::datatable(S_comp_R)
```


## OFFGENEARL Breakout 


```{r}
S_comp_OR %>% 
  filter(RACE != "White") %>% 
  drop_na(RRI_diff, p_diff) %>% 
  ggplot() + 
  annotate("rect"
           , xmin = min(S_comp_OR$RRI_diff, na.rm = T)
           , xmax = 0
           , ymin = min(S_comp_OR$p_diff, na.rm = T)
           , ymax = 0
           , fill = "grey80"
           , alpha = 0.5
          ) + 
  geom_point(aes(x = RRI_diff, y = p_diff, shape = RACE, color = as.character(BJS_gt_SC)), alpha = 0.5) +
  labs(
    title = "Comparing Differences in S_RRI and p for Black/Hispanic (OFFGENEARL Breakout)"
    , subtitle = "p = WPOPEST (White Population) / POPEST (White, Black, or Hispanic)\nWhite is removed from Plot since S_RRI = 1 so all S_RRI difference = 0\n Grey box indicates where BJS RRI is larger and BJS p is larger"
    , x = "S_RRI difference (S_RRI.SC - S_RRI.BJS)"
    , y = "p Difference (p.SC - p.BJS)"
  ) + 
  scale_color_discrete(name = "S_RRI.BJS > S_RRI.SC") + 
  theme_minimal()
```

```{r}
DT::datatable(S_comp_OR)
```


## Example: Arkansas, 2015, Any OFFGENEARL category 

```{r}
S_comp_R %>% filter(STATE == "Arkansas", RPTYEAR == 2015) %>% 
  DT::datatable()
```

$$
\begin{aligned}
n_W & = 3442 \\
n_H & = 15 \\[1em]
N^{BJS}_W & = 13377\\
N^{BJS}_H & = 874 \\
p^{BJS} & = N^{BJS}_H / N^{BJS}_H = 13377/874 = 15.3 \\[1em]
N^{SC}_W & = 1726866\\
N^{SC}_H & = 130073 \\
p^{SC} & = N^{SC}_H / N^{SC}_H = 1726866/130073 = 13.3 \\[1em]
I^{BJS}_H & = 0.067 \\
I^{SC}_H & = 0.05796049
\end{aligned}
$$


