---
title: "RRI Overview" 
description: "Last User: `r stringr::str_sub(getwd(), 10, stringr::str_locate(stringr::str_sub(getwd(), 10, -1), '/')[1]+10-2)`"
date: last-modified
date-format: "YYYY-MM-DD HH:mm:ss"
published-title: Last Modified
doi: "`r Sys.time()`"
doi-title: Last Ran
execute:
  echo: true
format: 
  html:
    page-layout: full
    fontsize: 0.9em
    fig-width: 12
    fig-height: 7
    code-fold: true 
editor: source
self-contained: true
editor_options: 
  chunk_output_type: console
---


```{r}
#| label: setup
#| include: false  

library(tidyverse)
library(knitr)
library(kableExtra)

#https://stackoverflow.com/questions/66974669/collapse-rows-is-not-collapsed-and-updating-packages-does-not-fix
#devtools::install_github(repo="haozhu233/kableExtra", ref="a6af5c0") #to get collapse rows to work 

#https://github.com/quarto-dev/quarto-cli/issues/5702
# need to use knitr 1.42
# otherwise get error when trying to use DT::datatable

box::use(
    box/admin
  , box/assignflags
)
```


::: {.panel-tabset} 

## Notes 

The prefix `S_` indicates that the variables values has been suppressed if the `REVCNT` <5.  The `S_` version of a variable (e.g. `S_RRI`) will equal the original variable (`RRI`) when suppression did not occur.  The variable `SUPPRESS` is used as a flag, with 1 = suppression occurred and `S_REVCNT` = 5 instead of the original value.  



```{r}
N_BJS  <- readRDS(file.path(admin$sp_data, "NCRP_N_REV_BJS.RDS"))
A_BJS  <- readRDS(file.path(admin$sp_data, "NCRP_A_REV_BJS.RDS"))

N_PUMS <- readRDS(file.path(admin$sp_data, "NCRP_N_REV_PUMS.RDS"))
A_PUMS <- readRDS(file.path(admin$sp_data, "NCRP_A_REV_PUMS.RDS"))
```




```{r}

longdf <- map2(
    list(N_BJS,  N_PUMS,   A_BJS,   A_PUMS)
  ,   c("N_BJS","N_PUMS", "A_BJS", "A_PUMS")
  , ~bind_rows(
      .x$R %>% mutate(OFFGENERAL = admin$lev_OFFGENERAL2[1])
    , .x$OR
    ) %>% 
    mutate(
        OFFGENERAL = factor(OFFGENERAL, levels = admin$lev_OFFGENERAL2)
      , DATA = .y
    ) 
) %>% 
  bind_rows() %>% 
  mutate(
      DATANCRP = str_sub(DATA, 1, 1)
    , DATAPOP  = str_sub(DATA, 3, -1)
  )



```

## Infographic RRI's

Most recent year for all offense categories, looking at Hispanic and Black only. 

```{r}

allOG_2r_rectyr <- longdf %>% 
  filter(OFFGENERAL == admin$lev_OFFGENERAL2[1]) %>% 
  filter(RPTYEAR == RECENT_YR, RACE %in% c("Black", "Hispanic"), STATE != "District of Columbia") 


allOG_2r_rectyr %>%
  filter(!is.na(S_RRI), S_RRI != Inf) %>% 
  ggplot(aes(x = S_RRI, y = RACE)) + 
  geom_vline(xintercept = 1, color = "grey35", linetype = "dashed") + 
  geom_boxplot(aes(color = RACE), alpha = 0) + 
  facet_wrap(~RACE, scales = "free", nrow = 2)+ 
  scale_shape_manual(values = c(17, 16)) + 
  facet_wrap(DATAPOP~DATANCRP, scales = "free") + 
  labs(title = "RRI values for Most Recent Year") + 
  theme_bw() +
  theme(
      axis.text.y = element_blank()
    , axis.ticks.y = element_blank()
  ) 


# allOG_2r_rectyr %>%
#   filter(!is.na(S_RRI), S_RRI != Inf) %>% 
#   ggplot(aes(x = S_RRI)) + 
#   geom_vline(xintercept = 1, color = "grey35", linetype = "dashed") + 
#   geom_boxplot(aes(color = DATAPOP, fill = DATANCRP), alpha = 0.5) + 
#   facet_wrap(~RACE, scales = "free", nrow = 2)+ 
#   scale_fill_manual(values = c("white", "grey85")) + 
#   labs(title = "RRI values for Most Recent Year") + 
#   theme_bw() +
#   theme(
#       axis.text.y = element_blank()
#     , axis.ticks.y = element_blank()
#   ) 


allOG_2r_rectyr %>% 
  group_by(RACE, DATAPOP, DATANCRP) %>% 
  filter(!is.na(S_RRI), S_RRI != Inf) %>% 
  summarize(
      q000 = quantile(S_RRI, probs = 0)
    , q025 = quantile(S_RRI, probs = 0.25)
    , q050 = quantile(S_RRI, probs = 0.50)
    , q075 = quantile(S_RRI, probs = 0.75)
    , q100 = quantile(S_RRI, probs = 1)
    , mean = mean(S_RRI)
    , .groups = "keep"
  ) %>% 
  ungroup() %>% 
  add_row(
      RACE = "Black/Hispanic"
    , DATAPOP = "BJS/PUMS"
    , DATANCRP = "A/N"
    , q000 = quantile(filter(allOG_2r_rectyr, !is.na(S_RRI), S_RRI != Inf)$S_RRI, probs = 0)
    , q025 = quantile(filter(allOG_2r_rectyr, !is.na(S_RRI), S_RRI != Inf)$S_RRI, probs = 0.25)
    , q050 = quantile(filter(allOG_2r_rectyr, !is.na(S_RRI), S_RRI != Inf)$S_RRI, probs = 0.50)
    , q075 = quantile(filter(allOG_2r_rectyr, !is.na(S_RRI), S_RRI != Inf)$S_RRI, probs = 0.75)
    , q100 = quantile(filter(allOG_2r_rectyr, !is.na(S_RRI), S_RRI != Inf)$S_RRI, probs = 1)
    , mean = mean(filter(allOG_2r_rectyr, !is.na(S_RRI), S_RRI != Inf)$S_RRI)
  ) %>% 
  kable() %>% 
  kable_styling() %>% 
  row_spec(9, bold = TRUE) %>% 
  collapse_rows(1:2, valign = "top")



allOG_2r_rectyr %>% 
  select(ABB, RPTYEAR, RACE, DATANCRP, DATAPOP, S_REVCNT, POPEST, S_RRI) %>% 
  mutate_at(vars(S_RRI), ~round(., digits = 2)) %>% 
  mutate_at(vars(ABB, RPTYEAR, RACE, DATANCRP, DATAPOP), as.factor) %>% 
  DT::datatable(
    filter = c("top") 
  )
```


## Flags 


```{r}
#| fig-height: 4
FLAGS_A_BJS <- read_csv(file.path(admin$sp_data, "FLAGS_A_BJS.csv"), show_col_types = FALSE) %>% 
  select(-c(ncrp, data, note_RATE)) %>% 
  pivot_longer(cols = -STATE) %>% 
  rename(A_BJS = value)
FLAGS_N_BJS <- read_csv(file.path(admin$sp_data, "FLAGS_N_BJS.csv"), show_col_types = FALSE) %>% 
  select(-c(ncrp, data, note_RATE)) %>% 
  pivot_longer(cols = -STATE) %>% 
  rename(N_BJS = value)

FLAGS_A_CEN <- read_csv(file.path(admin$sp_data, "FLAGS_A_CEN.csv"), show_col_types = FALSE) %>% 
  select(-c(ncrp, data, note_RATE)) %>% 
  mutate_all(as.character)%>% 
  pivot_longer(cols = -STATE) %>% 
  rename(A_CEN = value)
FLAGS_N_CEN <- read_csv(file.path(admin$sp_data, "FLAGS_N_CEN.csv"), show_col_types = FALSE) %>% 
  select(-c(ncrp, data, note_RATE)) %>% 
  mutate_all(as.character)%>% 
  pivot_longer(cols = -STATE) %>% 
  rename(N_CEN = value)

ALL_FLAGS <- Reduce(function(x, y) full_join(x, y, by = c("STATE", "name"))
       , list(FLAGS_A_BJS, FLAGS_N_BJS, FLAGS_A_CEN, FLAGS_N_CEN)
      ) %>% 
  pivot_longer(cols = -c("STATE", "name"), names_to = "DATA", values_to = "FLAG") %>% 
    mutate(
      DATANCRP = str_sub(DATA, 1, 1)
    , DATAPOP  = str_sub(DATA, 3, -1)
  ) %>% 
  mutate(flag_meaning = assignflags$flag_meaning(FLAG)) 


for (thisname in unique(ALL_FLAGS$name)){
  
  p <- ALL_FLAGS %>% 
    filter(name == thisname) %>% 
    group_by(DATANCRP, DATAPOP) %>% 
    count(FLAG, flag_meaning) %>% 
    mutate(prop = n/sum(n)) %>% 
  ggplot(aes(x = FLAG, y = prop)) + 
    geom_col(color = "grey50", alpha = 0.5)+ 
    geom_text(
        aes(label = scales::percent(prop, accuracy = 1))
      , vjust = -0.5
    ) + 
    scale_y_continuous(expand = c(0.08, 0)) + 
    facet_wrap(DATAPOP~DATANCRP, nrow = 1) +
    labs(title = thisname, x = NULL, y = NULL) + 
    theme_bw() + 
    theme(
        axis.text.y = element_blank()
      , axis.ticks.y = element_blank()
    ) 
  
  print(p)
}




ALL_FLAGS %>% 
  mutate_all(as.factor) %>% 
  DT::datatable(
    filter = c("top") 
  )

```



## Infographic Notes Check


```{r}

notes <- read_csv(file.path(admin$sp_data_raw, "notes/revcnt_notes.csv"), show_col_types = FALSE)

noinfog_notes <- notes %>% 
  select(STATE, DATANCRP = ncrp, DATAPOP = popdenom) %>% 
  mutate(in_notes = TRUE)

noinfog_flags <- ALL_FLAGS %>% 
  filter(name == "flag_INFOGRAPH", FLAG %in% c("1M", "1MS", "2")) %>% 
  select(STATE, DATANCRP, FLAG, DATAPOP) %>% 
  mutate(in_flags = TRUE) 

diffdf <- full_join(noinfog_flags, noinfog_notes, by = c("STATE", "DATANCRP", "DATAPOP")) %>% 
  filter(is.na(in_flags) | is.na(in_notes))


if (nrow(diffdf) > 0){ 
  warning("Notes for no infograph and infographic flags = 2 are NOT consistent!!\nCHECK AND UPDATED AS NEEDED")
  diffdf
} else {
  message("Notes for no infograph and infographic flags = 2 have the same set of states and data")
}



DT::datatable(notes, filter = c("top"))
```


::: 
<!-- end {.panel-tabset} ALLL --> 