---
title: "SVII Shiny Documentation" 
date: now
date-format: "YYYY-MM-DD HH:mm:ss z"
published-title: "Last run"
editor: source
execute: 
  echo: false 
self-contained: true 
format: 
  html:
    page-layout: full
    fig-width: 12
    toc: true
    toc-depth: 4
    toc-location: left
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false 
library(tidyverse)
library(csgjcr)


svii_agg  <- readRDS("../prep/svii_agg.rds")
svii_demo <- readRDS("../prep/svii_demo.rds")
```


# Input Data 

- source file:  [50 State Revocations Project/50 State Survey (2024)/Data/raw/combined/svii_main.rds](https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2F50%20State%20Survey%20%282024%29%2FData%2Fraw%2Fcombined%2Fsvii%5Fmain%2Erds&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98&parent=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2F50%20State%20Survey%20%282024%29%2FData%2Fraw%2Fcombined) 
- documentation on creation of `svii_main.rds` file: [50 State Revocations Project/50 State Survey (2024)/Data/raw/survey_documentation.html](https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2F50%20State%20Survey%20%282024%29%2FData%2Fraw%2Fsurvey%5Fdocumentation%2Ehtml&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98&parent=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2F50%20State%20Survey%20%282024%29%2FData%2Fraw)
- repo that creates `svii_main.rds`: [50_state_revocations](https://github.com/CSGJusticeCenter/50_state_revocations)
- Data from the current survey is added to the data from previous surveys, the output files in the [combined](https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2F50%20State%20Survey%20%282024%29%2FData%2Fraw%2Fcombined&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98) folder include data available from 2018-2023 
- The previous survey data is pulled from [50 State Revocations Project/MCLC Shiny App/data/raw/mclc/mclc_data_2022_v9.xlsx](https://csgorg.sharepoint.com/:x:/r/sites/Team-JC-Research/_layouts/15/Doc.aspx?sourcedoc=%7B286F1BA7-7E51-42F5-893F-9ABCE4D04451%7D&file=mclc_data_2022_v9.xlsx&action=default&mobileredirect=true). This is the [file imported](https://github.com/CSGJusticeCenter/MCLCShiny/blob/323a8670ca2dac362bc7cc30f48697b9c4eb35de/import.R#L41) in the [v2.0.00 (Apr 2024)](https://github.com/CSGJusticeCenter/MCLCShiny/releases/tag/v2.0.00) of the app. 

# Data Pathway Flow Chart


![Flow chart of Data Pathway](`r csg_sp_path("50 State Revocations Project/50 State Survey (2024)/Data/raw/graphics/MCLCShiny_prep_0_shiny_prep.png")`)


*Need to edit this flow chart? drawio files are located here: [50 State Revocations Project/50 State Survey (2024)/Data/raw/graphics](https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2F50%20State%20Survey%20%282024%29%2FData%2Fraw%2Fgraphics&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98&ct=1652815580832&or=Teams%2DHL&ga=1). Download software from [drawio.com](https://www.drawio.com/).* 


# Data Management 

## True Zeros 

A true value of zero means:  

1. the metric exits (i.e. the state has parole) 
2. the metric can be measured (i.e. the state's data system allows for pulling parole data) 
3. the value is 0 

## Values of 0's and NA's 

In v2.0.00 (Apr 2024) of the app, [all 0 values were converted to NA's](https://github.com/CSGJusticeCenter/MCLCShiny/blob/323a8670ca2dac362bc7cc30f48697b9c4eb35de/import.R#L253-L254). This was done for two main reasons: 

1. Make tables/charts easier to read without an excess of 0 values 
2. Assuming most, if not all, 0 values were not 'true' 0 values 


### MCLC Data (2018-2021) - zero values 

In the MCLC era of data collection, data was collected via a google spreadsheet ([template spreadsheet for example](https://docs.google.com/spreadsheets/d/1JgiuQTz-ZLF5xByb3Wftq4GaTNCajsZ-gL79VDDmkPU/edit?gid=2093233864#gid=2093233864)).  States, in a desire to complete the submission, would put a value of '0' into the cell when the data metric was unavailabe (either because it didn't exists, like parole was abolished, or that metric could not be accessed from the data system).  


```{r}
#| label: import-mclc-2022-data
## code taken from 2024_survey/survey/admin.R file in the 50_state_revocations repo 
## https://github.com/CSGJusticeCenter/50_state_revocations/blob/cc36061888e519af02beb84fc90f736a99d9709f/2024_survey/survey/admin.R

box::use(
  readxl[read_excel]
)

## https://github.com/CSGJusticeCenter/50_state_revocations/blob/cc36061888e519af02beb84fc90f736a99d9709f/2024_survey/survey/admin.R#L19-L23
pathway_data_raw <- csg_sp_path(
  "50 State Revocations Project", "50 State Survey (2024)", 
  "Data", "raw")

## https://github.com/CSGJusticeCenter/50_state_revocations/blob/cc36061888e519af02beb84fc90f736a99d9709f/2024_survey/survey/admin.R#L26-L30
info_file <- file.path(pathway_data_raw, "survey_metrics_and_categories.xlsx")

main_metrics <- read_excel(info_file, sheet = "main") |> 
  mutate(sum_of_abbr = ifelse(sum_of_abbr == "NA", NA, str_split(sum_of_abbr, ", ")))

## https://github.com/CSGJusticeCenter/50_state_revocations/blob/cc36061888e519af02beb84fc90f736a99d9709f/2024_survey/survey/admin.R#L78
main_metric_fct_order <- main_metrics$metric

## https://github.com/CSGJusticeCenter/50_state_revocations/blob/cc36061888e519af02beb84fc90f736a99d9709f/2024_survey/survey/admin.R#L82-L107
## rm code about converting zeros so can review which values are 0 
mclc_2022_survey <- read_excel(
  csg_sp_path("50 State Revocations Project", "MCLC Shiny App", "data", "raw", "mclc", "mclc_data_2022_v9.xlsx"), 
) |> 
  pivot_longer(-c(states, year), names_to = "rawmetric", values_to = "n") |> 
  mutate(
    metric = str_to_title(str_replace_all(rawmetric, "_", " ")), 
    metric_short = word(metric, 1, -2), 
    type = word(metric, -1), 
    year = as.numeric(year), 
    n = as.numeric(n) 
  ) |> 
  full_join(filter(main_metrics, optional_metric == FALSE), by = c("metric", "metric_short", "type")) |> 
  mutate(group = "aggregate", group_cat = "aggregate") |> 
  mutate(
    metric = factor(metric, main_metric_fct_order), 
    metric_abbr = factor(metric_abbr, main_metrics$metric_abbr)
  ) |> 
  arrange(desc(year), metric) |> 
  select(state = states, year, metric_abbr, type, group_cat, group, n, metric, metric_short)
```


```{r}
zero_22_instances <- mclc_2022_survey |> 
  filter(n == 0) |> 
  count(state, type, metric_abbr)

zero_22_states <- unique(zero_22_instances$state)

## table data for state 
# mclc_2022_survey |> filter(state == zero_22_states[7]) |>
#   select(state, year, metric_abbr, n) |>
#   arrange(year) |>
#   pivot_wider(names_from = year, values_from = n) |>
#   arrange(metric_abbr)
# 
# 
# svii_agg |> filter(state_name == zero_22_states[7]) |>
#   mutate(metric_abbr = factor(metric_abbr, levels = levels(mclc_2022_survey$metric_abbr))) |> 
#   select(state_name, year, metric_abbr, n) |>
#   arrange(year) |>
#   pivot_wider(names_from = year, values_from = n) |>
#   arrange(metric_abbr)
```

There were `r length(zero_22_states)` states that had 0 values: `r paste(zero_22_states, collapse = ", ")`


- **Alabama**
  * provided 0's for population new offense violation metrics for 2018-2021 (`p new`, `p new par`, `p new prob`)
  * AL population data includes only the subset of individuals for technical violations (not new violations) 
  * ***UPDATE: in 2022-2023, AL provided population new offense violation metrics***
- **Illinois**
  * provided 0's for all probation metrics for 2018-2021
  * IL probation is run by a separate organization (Administrative Office of the Illinois Courts) - DOC is unable to provide probation data 
  * *Metrics that were 0's in 2018-2021 were not submitted in 2022-2023 --> NA's for 2018-2023*
- **Maine**
  * provided 0's for admissions parole data for 2018-2020 (`a par`, `a tech par`, `a new par`)
  * ME provide NA's for metrics in 2021; ME does not have parole (abolished in 1976)
  * *Metrics that were 0's in 2018-2021 were not submitted in 2022-2023 --> NA's for 2018-2023*
- **Michigan**
  * provided 0's for population probation metrics and population new offense metrics (`p new`, `p prob`, `p tech prob`, `p new prob`, `p new par`)
  * MI can't provide probation data or new offense data on population - MI only tracks people with technical parole violations in prison populations 
  * *Metrics that were 0's in 2018-2021 were not submitted in 2022-2023 --> NA's for 2018-2023*
- **Minnesota**
  * provided 0's for `p new prob`, provided NA values for `a new prob`
  * MN can't provide probation breakdown 
  * *Metrics that were 0's in 2018-2021 were not submitted in 2022-2023 --> NA's for 2018-2023*
- **Washington**
  * provided 0's for all probation metrics
  * All "community custody" supervision trends reported in the post-release/parole sections
  * ***UPDATED: in 2022-2023 WA provided all probation metrics***
- **West Virginia**
  * provided 0's for population parole data (`p par`, `p tech par`, `p new par`)
  * prison population does not identify people who were previously on parole 
  * *WV resubmitted 2018-2021 values as a part of their 2022-2023, structure is consistent population parole metrics are not submitted --> NA's for 2018-2023*


### SVII Data (2022-2023) - zero values 


In the most recent data collection (survey conducted in 2024, collecting data for 2022-2023), states were asked to submit data in whatever format they desired.  This lead to a lot fewer of not true 0's - if a state didn't have our couldn't measure a certain metric, it simply wasn't included in the submission.  

```{r}
# prep/2a_import_surve.R files 
svii_raw <- readRDS(csg_sp_path("50 State Revocations Project/50 State Survey (2024)/Data/raw/combined/svii_main.rds")) 

svii_raw |> 
  filter(group == "aggregate") |> 
  filter(n == 0) |> 
  select(state_name, metric_abbr, year, n) |> 
  print(n = 17)
```

when looking at **aggregate** data there are only 17 instances of a 0 value.  

- 12 instances are for unknown parole/probation violations
  * new metric for states who know that an observation is a parole or probation violation, but cannot determine if the observation is a new offense or technical violations 
  * the unknown metrics are used to help create the 'upper' metrics (i.e. prob = new prob + tech prob + unk prob) and to check sums (see an [individual data summary html](https://csgorg.sharepoint.com/sites/Team-JC-Research/Shared%20Documents/Forms/AllItems.aspx?ct=1652815580832&or=Teams%2DHL&ga=1&id=%2Fsites%2FTeam%2DJC%2DResearch%2FShared%20Documents%2F50%20State%20Revocations%20Project%2F50%20State%20Survey%20%282024%29%2FData%2Fraw%2Fstate%5Fsurvey&viewid=134e5f2c%2Df80c%2D46ef%2D8491%2D1eac7193eb98), and review the Data Check section )
  * the unk par/prob metrics are NOT shown in the app, thus these instances of zero can be ignored (they are filtered out of the display data frame)
  * States: Colorado and Mississippi 
- 5 instances: Indiana and Massachusetts 
  * admission data only 
  * believe these are 'true' zeros because non-zero values were provided in other years or in population table submitted 
  * These 0 values should be retained 
  
**The code that replaced 0's with NA's in the shiny prep has been removed.**  

Originally, code that replaced 0's with NA was a part of the data prep for the shiny app (`2a_import_survey.R`).  This code has been removed because it's not longer needed: (1) converting the necessary 0's to NA's in the old MCLC 2018-2021 data is already completed in [50_state_revocations/2024_survey/survey/admin.R](https://github.com/CSGJusticeCenter/50_state_revocations/blob/cc36061888e519af02beb84fc90f736a99d9709f/2024_survey/survey/admin.R#L82-L107) and (2) values of 0 that will go into the aggregate version of the app have alrady been check (text above).  


### Links 

[MCLC Overview](https://csgorg.sharepoint.com/:x:/r/sites/Team-JC-Research/_layouts/15/Doc.aspx?sourcedoc=%7BF426FDAC-51FA-4DC3-BD33-6867446FD73B%7D&file=MCLC%20Overview.xlsx&action=default&mobileredirect=true) spreadsheet - Missingness 2022 tab: talked about missingness and 0 values for each state.  


Slack messages from Mari Roberts (original author of code) on July 19, 2024: 

> Here are the reasons I believe I made this choice [to convert 0's to NA]  
> Zero values can clutter the chart and make it less readable.  
> I don't think any states actually had any true "0"s?  
> Except for the ones that have abolished parole, perhaps.  

[Slack Link 1](https://csgjc.slack.com/archives/D03GCM55S3A/p1721399582244449) 
[Slack Link 2](https://csgjc.slack.com/archives/D03GCM55S3A/p1721399594922169) 
[Slack Link 3](https://csgjc.slack.com/archives/D03GCM55S3A/p1721399610265279)
[Slack Link 4](https://csgjc.slack.com/archives/D03GCM55S3A/p1721399634778509)


## Subtitles (State Dashboards) 

Subtitles are placed within in the values boxes and the area/bar charts on the overview tab when there is only probation, only parole, or partial data available.   

### Conditions for Subtitles 

There are 4 values boxes on the state dashboard that represent: 

1. Overall admissions/population in 2023 
2. Supervision violation admissions/population  in 2023 (supervision)
3. Technical violation admissions/population in 2023 (tech)
4. New offense violation admissions/population in 2023 (new)

Only supervision, tech, and new have the option for a subtitle.  The subtitle for the value boxes check on a **yearly** basis.  Check probation/parole breakout for each metric to determine if only probation/only parole data is available for that metric in that year.  

```{r}
# prep/2a_import_surve.R files -- part of svii_agg creation, above svii_subtitle_vb 
subtext_no_par <- "(No Parole Data Available)"
subtext_no_prob <- "(No Probation Data Available)"
subtext_nodata <- "no data" 
subtext_gen_partial <- "(Partial Data Available)"


subtext_no_probpar <- str_replace(subtext_no_par, "Parole", "[Probation/Parole]")
```


::: {style="font-size:0.8em;"}
| Supervision | Technical | New Offense |  *Subtitle for Value Boxes*| 
|:-----:|:-----:|:-----:|:-----:| 
| `!is.na(prob) & !is.na(par)` | `!is.na(tech_prob) & !is.na(tech_par)` | `!is.na(new_prob) & !is.na(new_par)` | `NA` |  
| `is.na(prob) & is.na(par)`   | ` is.na(tech_prob) & is.na(tech_par)`  | `is.na(new_prob) & is.na(new_par)`   | `r subtext_nodata` |  
| `!is.na(prob) &  is.na(par)`<br>`& supervision == prob` | `!is.na(tech_prob) &  is.na(tech_par)`<br>`& tech == tech_prob` | `!is.na(new_prob) &  is.na(new_par)`<br>`& new == new_prob` | `r subtext_no_par` | 
| `is.na(prob)  & !is.na(par)`<br>`& supervision ==  par` | `is.na(tech_prob)  & !is.na(tech_par)`<br>`& tech ==  tech_par` | `is.na(new_prob)  & !is.na(new_par)`<br>`& new ==  new_par` | `r subtext_no_prob`|
| else | else | else | OTHER | 
: Conditions for Determining Subtitles for Value Boxes for a Specific Year 
:::

'OTHER' indicates some sort of special instance that requires individualized attention: 

- IA: supervision = par + prob (but then prob is removed b/c prob == tech_prob); txt_supervision --> `r subtext_gen_partial`
- IA: tech > tech_par but tech_prob == NA; rm subtitle 
- KY: supervision value for previous years provided; prob is removed b/c prob = tech_prob; rm subtitle
- MN: supervision value is provided; prob is removed b/c only have tech_prob; rm subtitle 

<br> 
After the subtitles are completed for the value boxes on a yearly basis, we need to determine the subtitles on a grouped basis (for 2018-2023 instead of for a single year). In order to determine the grouped subtitle, we look at the subtitle for each year of a given group (there should be 6 cells for each group, 1 for each year from 2018-2023).  

::: {style="font-size:0.8em;"}
| Conditions (same conditions for supervision, tech, and new) |  *grouped text*| 
|:-------------|:-------|
| All cells are equal, each cell is `NA` | `NA` |
| All cells are equal, each cell is "`r subtext_no_probpar`" | `r subtext_no_probpar`|
| All cells are equal, each cell is "`r subtext_nodata`` | `r subtext_nodata` | 
| Mix of NA's and text, all cells with text equal to "`r subtext_no_probpar`" | `r str_replace(subtext_no_probpar, 'No', 'Partial')` | 
| Mix of NA's and text, all cells with text equal to "`r subtext_nodata`" | `r subtext_gen_partial` | 
| All other situations (mix of different kinds of text) | `r subtext_gen_partial` | 
: Conditions for Determining Grouped Text (combining years)  
:::

<br>
After this step, you now I have a specific grouped text value for each of the 3 metrics in the value boxes (`supervision`, `new`, `tech`).  The final step is using these 3 pieces of text to determine the subtitle for the area and bar chart on the overview tab of the state dashboard.  


::: {style="font-size:0.8em;"}
| Conditions (same conditions for supervision, tech, and new) |  *grouped text*| 
|:-------------|:-------|
| `all(is.na(c(supervision, tech, new)))` | `NA` | 
| `supervision == tech & tech == new`; all three values are the same text | `supervision` | 
| `any(c(supervision, tech, new) == subtext_nodata)`; at least one is equal to "`r subtext_nodata`" | `r subtext_gen_partial` | 
| `any(c(supervision, tech, new) == subtext_gen_partial)`; at least one is equal to "`r subtext_gen_partial`" | `r subtext_gen_partial` | 
| else, any other combination | `r subtext_gen_partial` | 
: Conditions for Determining Area/Bar Chart Subtitles 
:::



The final step is converting "`r subtext_nodata`" to `NA`.  When determining the subtitles, it's required to differentiate between instances where states have data and when they don't.  In the steps above, a state is flagged as not having data using "`r subtext_nodata`".  However, within the actually app we do not want to show a subtitle if a state doesn't have data (instead there will be other text available to indicate this).  

### States with Subtitles 

```{r}
states_with_subtitles <- svii_agg |> 
  filter(year == 2023) |> 
  distinct(state_name, type, metric_abbr, subtitle_vb, subtitle_areabar) |> 
  filter( !(is.na(subtitle_vb) & is.na(subtitle_areabar)) )
```


There are `r length(unique(states_with_subtitles$state_name))` that have a subtitle for the value boxes and/or a subtitle for the charts.  

Reminder: `subtitle_vb`  is based on 2023 data only; `subtitle_areabar` is based on all years

::: {style="font-size:0.8em;"}
```{r}
states_with_subtitles |> 
  DT::datatable(
    rownames = FALSE, 
    options = list(
      lengthMenu = list(c(10, 25, -1), c('10', '25', 'All'))
    )
  )
```
:::


# Demographic Tab 


## SVII Demographics 


- combine two years of data and then calculate proportion for each metric
- instead of showing most recent year (2023) -- use BOTH years of data 
- add 2 years together and then calculate proportions 
- 2 years is not enough to establish trends so makes most sense to combine data 
- since only displaying percentages, and using 2 years -- don't need to suppress data 
- display total prison adm/pop, probation violations & breakdowns, and parole violations & breakdowns -- exclude any combination of parole + probation (supervision violations, new offense violations, technical violations) 
  
  
SVII calculation example: 

| Group | 2022 n | 2023 n | 2022+2023 n | perc (shown on tool) | 
|:---|----:|----:|----:|----:|
| A | 5 | 8 | 5+8 = 13 | 13/48 = 27%| 
| B | 8 | 9 | 8+9 = 17 | 17/48 = 35%| 
| C | 7 | 11| 7+11 = 18 | 18/48 = 38% | 
| Aggregate | 20 |  28| 20+28 = 48 | | 


### `svii_demo` 

`svii_demo` is a data frame that is created from the general `svii` data frame.  Then, from the `svii_demo` object, the `svii_demo_tabel_prep` is created which is the actual values to be displayed in the app.  

Total rows: 9100 = 50 states * 13 groups * 14 metrics 

- 13 groups 
  * 9 R/E (AIAN, Asian, Black, Hispanic, NHPI, Other, Two, Unknown r/e)
  * 4 S/G (Diverse, Female, Male, Unknown s/g) 
- 14 metrics: for R/E only showing total, probation metrics, and parole metrics (skipping total supervision, new, tech, unknowns, and non-supervision)


Newly created columns: 

- `2022` and `2023` - the integer values (or NA) for a given state and group for the specific year 
- `n` = `2022` + `2023` (combined value) 
- `flag` - flag, see [SVII Demo Flags](#svii-demo-flags) section for more information 
- `prop` = `n`/(aggregate value for given group/state/year); if prop == 0 then convert prop to NA 
- `perc` = percentage value of prop (prop*100); rounded to the nearest percent (i.e. prop = 0.397, perc = 40) 
- `comparison_source` = which data set should be used to compare the SVII metric 
  * `a total`/`p total` = Census data 
  * parole data = PPUS_Parole 
  * probation data = PPUS_Probation 
- `comp` = comparison proportion value 
- `compperc` = percentage value of comp (comp*100); runded to the nearest percent 
- `compunk` = percentage value of comp for unknown race/ethnicity or sex/gender 
  * used for PPUS comparison (there are no 'unknown' in census data) 
  * used to determine if a comparison is plausable 
  * **if unknown group is greater than 15% --> don't calc RRI, don't highlight cells**
- `rri` = 
  * group %in% c("Other", "Unknown r/e", "Unknown s/g", "Diverse") ~ NA_real_  
  * compperc == 0 ~ NA_real_; if value is 0 --> CAN'T CALC RRI B/C CAN'T DIVIDE BY ZERO 
  * compunk > 15 ~ NA_real_; if the unknown perc of comparison group is greater than 15% --> don't calc or highlight 
  * !is.na(perc) & !is.na(compperc) ~ perc/compperc, 




### SVII Demo Flags  


```{r}
svii_demo |> 
  count(flag) |> 
  mutate(
    desc = c("both years have a value", "only 2022 is available", "only 2023 is available", "both years are NA"), 
    `2022` = c("$\\mathbb{Z}$", "$\\mathbb{Z}$", "NA", "NA"), 
    `2023` = c("$\\mathbb{Z}$", "NA", "$\\mathbb{Z}$", "NA"), 
    .before = n
  ) |> 
  rename(obs = n) |> 
  mutate(perc = scales::percent(obs/sum(obs), accuracy = 0.1)) |> 
  knitr::kable()

```

\*Note: $\mathbb{Z}$ = integers  

<br> 
- Concerned if states have a mix of 2,3 with 1 and 4 
- If a state is only 1 & 4 --> mirror data availability for 2022 and 2023.  
- If a state has a mix, concern that some rows are using 2 years of data and others are using 1 year of data.  
- Check manually for each state that has at least one row (metric x group) that has a flag of 2 or 3   

```{r}
states_with_mix_flags <- svii_demo |> 
  group_by(state_name) |> 
  count(flag) |> 
  ungroup() |> 
  pivot_wider(names_from = flag, values_from = n) |> 
  select(state_name, `1`, `2`, `3`, `4`) |> 
  filter(!is.na(`2`) | !is.na(`3`)) |> 
  pull(state_name)
```

There are `r length(states_with_mix_flags)` states with flags of 2 and/or 3: `r paste(states_with_mix_flags, collapse = ", ")`

```{r}
# svii_demo |> 
#   filter(state_name == states_with_mix_flags[8]) |> 
#   filter(!flag %in% c(1, 4))
```


::: {style='font-size:0.8em;'}
::: {.grid}

::: {.g-col-6}

- 1 **Florida** - ok, leave as is
  * no prob/par population data for Asian in 2022; have values of 0/1 in 2023
  * data submission only included the category of Asian in 2023 population data
  * assume, due to low counts in 2023, that there were no observations in 2022 
- 2 **Georgia** - ok, leave as is
  * no p_total data for NHPI IN 2022; value of 2 in 2023
  * NHPI is a category that was listed in 2023 and not listed in 2022
  * assume, due to low counts in 2023, that there were no observations in 2022
- 3 **Hawaii** - ok, leave as is
  * no a_tech_par/a_new_par data for AIAN in 2022, values of 0/3 in 2023
  * data submission include AIAN in 2023 table but not in 2022 table 
  * assume, due to low counts in 2023, that there were no observations in 2022 
  * leave as is 
- 4 **Illinois** - ok, leave as is
  * no a_new_par data for AIAN in 2022, value of 3 in 2023
  * no a_new_par/p_new_par data for Unknown r/e in 2022, values of 4/2 in 2023
  * IL data is pulled from public data set that includes all observations 
  * assume that there were no observations in 2022
- 5 **Iowa** - ok, leave as is
  * no data for Unknown s/g in 2022, values of 0/2/4 in 2023
  * Iowa submission included a column for unknown' gender in 2023, but excluded column in 2022
  * assume that there were no observations in 2022
- 6 **Kansas** - ok, leave as is
  * no data for Unknown r/e in 2023, values of 0/1/2/4 in 2022
  * Kansas submission included a column for 'unknown r/e in 2022, but excluded the column in 2023
  * assume that there were no observations in 2022
- 7 **Kentucky** - ok, leave as is
  * did not respond to survey, data comes from BJS NPS data; BJS NPS data only available for 2022
- 8 **<span style='background:yellow;'>Louisiana -- low counts in supervision metrics, don't show up in total</span>**
  * no data for a_total for NHPI/Two in 2022, values in 2023 are 0 
  * in data submission, LA had columns for NHPI and Two 
  * for a_total in 2022, left those cells blank instead of putting in value
  * 2022 admissions: 
    - NHPI has 0's in all other admissions cells 
    - Two has a value of 3 under a breakout of new offense parole, so would expect to see a value in the top left (a_total) category
    - however the current breakout of R/E (with NA's in NHPI and Two) = sum of S/G values 
    - the count of 3 would be ~0.02% of the total admissions 
  * ***concerning that the value for Two is not placed in the a_total cell, but since it represents such a small proportion of admissions, leave as is*** 

:::

```{r}
# svii_demo |>
#   filter(state_name == states_with_mix_flags[17]) |>
#   filter(!flag %in% c(1, 4))
```

::: {.g-col-6}

- 9 **Massachusetts** - ok, leave as is 
  * no a_par/a_tech_par for Asian in 2023; values of 2/3 in 2022 
  * column of 'Asian/Pacific Islander' is in the MA submission, but the a_tech_par cell in 2023 is blank 
  * assume that a_par is removed because one of the submetrics is NA 
  * all other cells that are not blank (except for a_total) are values of 0
  * assume there were no observations in 2023
- 10 **Nebraska** - ok, leave as is 
  * no data for a_par/a_tech_par/a_new_par for NHPI in 2023; values of 0/1 in 2022
  * NE submission included 'Pacific Islander' column in 2022 but not in 2023
  * assume there were no observations in 2023 
- 11 **<span style='background:yellow;'>North Carolina -- ONLY USE 2023 DATA FOR MALE/FEMALE A_TOTAL</span>**
  * Male/Female, NHPI, Asian have missing values in 2022; Male/Female have high counts (00s and 000s) in 2023
  * **NC did not provide Male/Female breakdown for a_total in 2022 but did in 2023; ONLY USE 2023 COUNTS TO CALC PROP/PERC FOR A_TOTAL MALE/FEMALE**
  * ~~can calc Male/Female a_supervision, a_tech, a_new, a_prob, a_par from data provided~~; completed in [50_state_revocations](https://github.com/CSGJusticeCenter/50_state_revocations/commit/06b8fe704bda40da2c99303d585cbde4ec2f8ba4) repo 
  * missing data in one year for NHPI/Asian for prob/tech_prob/new_par; values are 0/1; assume low counts in NA year 
- 12 **Ohio** - ok, leave as is
  * did not respond to survey, data comes from BJS NPS data; BJS NPS data only available for 2022
- 13 **Oregon** - ok, leave as is 
  * mix of 2022/2023 with one year being NA and the other being 1/2/3
  * Oregon provided count data on a year x supervision x revocation type x sex x race
  * if there weren't any values for a given cell, assume there were no observations 
- 14 **Rhode Island** - ok, leave as is 
  * mix of 2022/2023 with one year being NA and the other being 0/1 for Asian/AIAN/Other
  * row with race category was either include/excluded in tables 
  * assume that if category is excluded, due to no obseravtions that year 
- 15 **South Carolina** - ok, leave as is 
  * missing data in 2022 for a_total/a_prob/p_total for NHPI/Other; 2023 values are 1/2 
  * SC provided tables by admission type x supervision x race x ethnicity x sex x age 
  * if there weren't any values for a given cell (i.e. a_total NHPI), assume there were no observations 
- 16 **Tennessee** - ok, leave as is 
  * 2022 values for Unknown r/e for admissions prob/par values are NA; all values for 2023 are 0
  * unknown category was included in admissions 2023 and population; always had values of 0
  * assume no observations in 2022
- 17 **Washington** - ok, leave as is 
  * NA in 2022 Other a_new_par; value of 0 in 2023 
  * cell was left blank in 2022; all other supervision metric cells are 0 or 2
  * assume no observations in 2022
:::

::: 

:::
  
## Census (State) Population  

- use 2023 data, pull data and categorize to match BJS categories 
- using **total** counts 
- do we want to use adult counts?? 
- use to compare to total prison adm/pop only 

Why  re-import data instead of just using the cenus_pep_state.rds data already available in the jr_data_library/analysis folder?  
Because need to seperate Asian and Pacific Islander; in the jr_data_library/analysis version these two categories are combined.  


### raw data files 

- jr_data_library/data/raw/census/pep/sc-est2009-alldata6-all.csv
- jr_data_library/data/raw/census/pep/sc-est2019-alldata6.csv
- jr_data_library/data/raw/census/pep/sc-est2023-alldata6.csv

### Links 

Link to [jr_data_library clean_pep (census data)](https://github.com/CSGJusticeCenter/jr_data_library/blob/develop/R/pull_clean/census/pep/clean_pep.R); [permalink](https://github.com/CSGJusticeCenter/jr_data_library/blob/f1f42e52476fb303ac521dbff14ed7689fd3a3c1/R/pull_clean/census/pep/clean_pep.R#L1)

Download data sets from census: [census.gov/programs-surveys/popest/datasets/2020-2023/state/asrh/](https://www2.census.gov/programs-surveys/popest/datasets/2020-2023/state/asrh/)
  

## Parole/Probation Populations 

- use 2023 data
- only have 'White', 'Black', 'Hispanic', and 'Other' race categories 
- PPUS survey collect more categories for race/ethnicity but report only provides these 4 categories when breaking out values by jurisdiction (by state) 
- Parole population compared to parole violations & breakdowns 
- Probation population compared to probation violations & breakdowns 

### raw data files 

- jr_data_library/data/raw/bjs/ppus/ppus23/ppus23t10.csv (Appendix Table 10: Selected characteristics of adults on probation, by jurisdiction, 2023)
- jr_data_library/data/raw/bjs/ppus/ppus23/ppus23t13.csv (Appendix Table 13: Selected characteristics of adults on parole, by jurisdiction, 2023)

::: {.callout-note}
## Unknown/Not Reported + Not Asked
In the 2023 PPUS report, a new column was added to the **Selected characteristics of adults on probation** table.  
The parole table (and previous versions of the probation table) only had a single Unknown column (called "Unknown/not reported").  The 2023 reported add a column to the probation table called "Not asked".  

In order to make the data consistent for both parole and probation; the probation table take the "Unkown/not reported" and combines it with the "Not asked" to get a single Unknown value for demographic breakouts.  

:::

### Links 

Link to [Probation and Parole in the United States, 2023](https://www.ojp.gov/library/publications/probation-and-parole-united-states-2023) report on BJS's website.  


## Highlight Cells - Compare to Population Percentage 

In the table, we want to highlight some of the SVII survey data when: 

- the SVII percentage is greater than comparison population percentage for a given group 
- this calculated/determined by: 
  (1) rounding the percentages to the nearest 1% (so don't highlight 8.1% > 8.0% when both are rounded and displayed as 8%) 
  (2) calculated `comp_to_pop_perc` (metric_perc/comparison_population_perc) 
  (3) if `comp_to_pop_perc` > 1 --> highlight cell  
- exclude highlighting if the unknown category of the comparison population is > 15% (too much unknown to make a meaningful comparison) 


| | Group A | Group B | Group C | Unknown Group | 
|:---|----:|----:|----:|----:|
| Comparison Population | 30% | 35% | 25% | 10% | 
| SVII Metric | <span style='font-weight: bold; color: #7b3014;'>32%</span> | 34% | <span style='font-weight: bold; color: #7b3014;'>34%</span>  | - | 
: Bold/Highlight cells where the metric percentage is greater than the comparison population for a given group
<br>

| | Group A | Group B | Group C | Unknown Group | 
|:---|----:|----:|----:|----:|
| Comparison Population | 25% | 30% | 25% | 20% | 
| SVII Metric | 32% | 34% | 34% | - | 
: Do not highlight cells if comparison population unknown group is greater than 15% 


## RRI - Comparison Population   

Relative Rate Index with Comparison Group


1. Calculate rate: group_metric_n / group_comp_population_n 
2. Calculate RRI: rate/rate[group == White/Female]


Put text above each of the tables: 


<span style='font-weight: bold; font-size: 1.5em;'>[GROUP_TEXT] are [VAL] likely to be [TYPE_TEXT] [METRIC_TEXT] than [COMP_GROUP]</span> 

Only do for the r/e and s/g categories listed below (don't do for Other r/e category or Unknown categories)

If no RRI's can be calculated:  

***[STATE] did not have sufficent demographic data to determine any relative rates.*** 


::: {.grid} 

::: {.g-col-4}

| `group` | [GROUP_TEXT] | 
|:---|:----|
|`White` | White people | 
|`Black`  | Black people |  
|`Hispanic` | Hispanic people| 
|`AIAN` | American Indian people| 
|`Asian` |Asian people|
|`NHPI` | Pacific Islander people|
|`Male` | Males| 
|`Female` | females\* | 

\*Note: females are not capitalized, the word 'Males' is capitalized because it's at the front of the sentence 

:::

::: {.g-col-4}

| `group_cat` | [COMP_GROUP] | 
|:--------|:----------|
| race_ethnicity | White people | 
| sex_gender | females | 
  
  
| `rri` | [VAL] | 
|:--------|:------|
| `rri > 1` | `rri`: "#.# times more" |
| `rri < 1` | `1-rri`: "#% less" | 
  
  
| `data_type` | [TYPE_TEXT] 
|:-----|:-------------|
| Admissions | admitted | 
| Population | incarcerated | 

:::

::: {.g-col-4}

| `metric_abbr` | [METRIC_TEXT] 
|:-----|:-------------|
| total    |  "" |  
| par      | " for a parole violation" 
| tech par | " for a technical offense parole violation" | 
| new par  | " for a new offense parole violation" | 
| prob     | " for a probation violation" | 
| tech prob| " for a technical offense probation violation" | 
| new prob | " for a new offense probation violation" | 


:::


:::


For Parole and Probation sections 

- default is to shown par/prob RRI's 
- if par/prob is NOT available but tech_par/tech_prob is available --> show tech_par/tech_prob RRI's 
- if par/prob AND tech_par/tech_prob is NOT available but new_par/new_prob is available --> show new_par/new_prob



